### 2023-03-24 ieee_main.tex
Init commit.

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{natbib}

\newcommand{\PeakNet}{PeakNet}
\newcommand{\peaknet}{PeakNet}
\newcommand{\psocake}{Psocake}

\begin{document}

\title{\peaknet{}: Bragg peak finding in X-ray crystallography experiments with
U-Net}

\author{\IEEEauthorblockN{Cong Wang}
\IEEEauthorblockA{\textit{Linac Coherent Light Source} \\
\textit{SLAC National Accelerator Laboratory}\\
%% 2575 Sand Hill Road, Menlo Park, CA 94025, USA \\
cwang31@slac.stanford.edu}
\and
\IEEEauthorblockN{Po-nan Li*\thanks{* Performed this work in
a previous role at SLAC National Accelerator Laboratory}}
%% City, Country \\
\and
\IEEEauthorblockN{Jana Thayer}
\IEEEauthorblockA{\textit{Linac Coherent Light Source} \\
\textit{SLAC National Accelerator Laboratory}\\
%% 2575 Sand Hill Road, Menlo Park, CA 94025, USA \\
jana@slac.stanford.edu}
\and
\IEEEauthorblockN{Chun Hong Yoon}
\IEEEauthorblockA{\textit{Linac Coherent Light Source} \\
\textit{SLAC National Accelerator Laboratory}\\
%% 2575 Sand Hill Road, Menlo Park, CA 94025, USA \\
yoon82@slac.stanford.edu}
}

\maketitle

\begin{abstract}
Serial crystallography at X-ray free electron laser (XFEL) sources has
experienced tremendous progresses in achieving high data rate in recent times.
While this development offers potential to enable novel scientific
investigations, such as imaging faster molecular events, it also poses
challenges in regards to real-time data analysis, which may have to involve some
degree of data reduction to only save those containing actionable information on
disks.  If data reduction is not effective, it could directly result in a
substantial increase in facility budgetary requirements, or even hinder the
utilization of ultra-high repetition imaging techqniues.  Furthermore, an
additional challenge involves providing real-time feedback to users derived from
real-time data analysis.  Under the framework of serial crystallography, the
initial and critical step in real-time data analysis is finding X-ray Bragg
peaks from diffraction images.  To tackle this challenge, we present \peaknet{},
a Bragg peak finder that utilizes neural networks and runs about four times
faster than \psocake{} peak finder, while delivering significantly better
indexing rates and comparable number of indexed events.  We formulated the task
of peak finding into a semantic segmentation problem, which is then addressed by
using the classical U-Net architecture.  A key advantage of \peaknet{} is its
ability to scale linearly with respect to data volume, making it well-suited for
real-time serial crystallography data analysis at high data rates.  Additionally,
we identified a performance bottleneck that, if eliminated, would result in
scaling beyound linear capability on GPUs.
\end{abstract}

%% \begin{IEEEkeywords}
%% component, formatting, style, styling, insert
%% \end{IEEEkeywords}

\section{Introduction}

Serial crystallography with X-ray free electron lasers (XFEL) has enabled the
structural determination of three-dimensional macromolecules from radiation
damage-free samples at room temperature, an approach commonly known as
\textit{diffraction-before-destruction}
\citep{neutzePotentialBiomolecularImaging2000,
chapmanFemtosecondDiffractiveImaging2006,chapmanFemtosecondXrayProtein2011}.
Time-resolved serial crystallography at XFEL facilities, like the Linac Coherent
Light Source (LCLS), allows the investigation of biochemical reactions with
femtosecond-scale time resolutions.  This technique is typically referred to as
serial femtosecond crystallography (SFX), which has led to many signficiant
structural studies \citep{kupitzSerialTimeresolvedCrystallography2014,
nangoThreedimensionalMovieStructural2016,pandeFemtosecondStructuralDynamics2016a,
youngStructurePhotosystemII2016,sugaLightinducedStructuralChanges2017,
kernStructuresIntermediatesKok2018,ibrahimUntanglingSequenceEvents2020,
sugaTimeresolvedStudiesMetalloproteins2020} since the first published work at
LCLS \citep{aquilaTimeresolvedProteinNanocrystallography2012}.  In the meantime,
the data rate at XFEL facilities have also gradually increased from hundreds of
Hz to the MHz range, with the European X-ray Free Electron Laser (EuXFEL) being
the first MHz facility available to users and LCLS-II set to launch in 2023.

At the MHz data rate, novel real-time data analysis approaches are needed to
tackle two major challenges that arise in SFX experiments, namely data reduction
and real time feedback.  Firstly, data reduction aims to extract and compress
real-time actionable information by identifying important events, commonly
referred to as ``hits", and vetoing irrelevant ones from terabytes per second of
data streams.  One typical approach for SFX hit finding utilizes existing Bragg
peak finders, such as the Cheetah peak finder
\citep{bartyCheetahSoftwareHighthroughput2014}, the robust peak finder
\citep{hadian-jaziPeakfindingAlgorithmBased2017} or the \psocake{} peak finder
\citep{shinDataAnalysisUsing2018}.  Additionally, a neural networks-based SFX
hit finder was reported to achieved a processing rate of 1.3 kHz on a single GPU
\citep{keConvolutionalNeuralNetworkbased2018}.  Secondly, real-time feedback in
SFX experiments provides users with information on the experimental conditions
and allows them to make real-time decisions that can optimize the data
acquisition process.  For example, it's critical to fine-tune the hit rate to
maximize the usage of samples;  it's also important to know the current
diffraction limit, crystalline mosaicity, reciprocal space coverage, and other
revelant factors over time.  Therefore, hit finding alone is insufficient to
provide the necessary insights, making real-time Bragg peak finding crucial in
delivering fast and comprehensive feedbacks.  The previously mentioned peak
finder in \psocake{} runs at roughly 5 Hz on a data center CPU, which may result
in substantial costs when attempting to scale up the process.

In this work, we present \peaknet{} that addresses the problem of high data rate
peak finding by converting it into the task of peak segmentation using neural
networks.  To accomplish this goal, we propose to train a neural network model
to classify each individual pixel as either a peak pixel or not a peak pixel.
This is followed by recognizing a connected area of pixels as a single peak, a
task that can be readily accomplished through the connected component analysis
\citep{weaverCentrosymmetricCrossSymmetricMatrices1985}.  Subsequently, the peak
coordinates will be determined by computing the center of mass of all the pixels
that belong to the identified peak.  It's worth noting that the entire peak
finding process takes place on GPUs, offering a cost-effective option for
achieving scalability.  Concretely, our contributions can be summarized as
follows:

\begin{itemize}

    \item We introduce a deep neural network-based Bragg peak finder, named
    \peaknet{}, which can effectively and efficiently segment hundreds or even
    thousands of Bragg peaks with various peak profiles in detector images of
    any size.  Despite being trained on peaks labeled by an existing peak finder,
    we highlight that \peaknet{}'s capability is not limited by the peak finder
    used in labeling.

    \item We demonstrate the efficacy of \peaknet{} by evaluating its
    performance on large multi-panel ($1739 \times 1748$) and single-panel
    ($1920 \times 1920$) detector.  It significantly outperformed existing
    methods in terms of indexing rate, while delivering comparable number of
    indexed events.  We also finetuned the underlying U-Net architecture of
    \peaknet{} to strike an optimal balance between model efficacy and runtime
    performance, leading to a four times out-of-the-box processing speed than
    \psocake{} peak finder.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DIVIDER %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Related work}

Reliable and automatic peak finding algorithms have undergone multiple
iterations of development.  An early approach involved utilizing template
matching \citep{wilkinsonIntegrationSinglecrystalReflections1988a} based on
libraries of peak shapes, but this method was found to be slow and inefficient
in runtime, especially when dealing with peaks with low signal-to-noise ratios
(SNR).  The main obstacle lies in the localization of peaks and the tuning of
user parameters for pattern matching, compounded by the difficult task of
developing a comprehensive library of peak shapes.  Another influential approach
employed region-growing techniques
\citep{bolotovskySeedSkewnessMethodIntegration1995,
bartyCheetahSoftwareHighthroughput2014} to detect pixel areas with high
skewness.  In the context of serial crystallography with XFEL sources, the
efficacy of this method was diminished due to the lack of sufficient data to
provide reliable statistics, rendering it susceptible to outliers and less adept
in analyzing weak peaks at higher scattering angles, which are essential for
achieving atomic resolution in structure determination.

While template matching and region-growing tecnhiques require users to provide
priori information like threshold values, Robust Peak Finder (RPF)
\citep{hadian-jaziPeakfindingAlgorithmBased2017,
hadian-jaziDataReductionSerial2021} has demonstrated proficient peak finding
capabilities with minimal user inputs.  This techinuqe utilizes the Modified
Selective Statistical Estimator (MSSE) method to segment between background
pixels and actual peaks.  Furthermore, the RPF method can also parallelize the
processing of diffraction patterns, making it ideal for real-time data analysis.

\psocake{} is a software specifically designed to streamline high throughput
data reduction and analysis of XFEL experiments, and is routinely used at SLAC
National Accelerator laborator (SLAC) and Pohang Accelerator Laboratory (PAL).
The built-in peak-finding algorithm \citep{shinDataAnalysisUsing2018} includes
calibrating raw analog digital units (ADUs); applying optional background
correction and bad pixel masks; identifying possible peaks; calculating their
SNR; determining Bragg spot sizes; and selecting peaks based on size, total
intensity and SNR.

In recent years, neural network models have emerged as a promising avenue for
Bragg peak finding.  BraggNet \citep{sullivanBraggNetIntegratingBragg2019} is
the first method that demonstrates proficiency of neural network models,
specifically U-Net \citep{ronnebergerUNetConvolutionalNetworks2015}, in
accurately segmenting peak pixels, including weak peaks, from background pixels
in neutron crystallography data.  Specifically, BraggNet employed simulated
peaks to create training datasets, which underwent a number of preprocessing
steps, including centering and cropping to a specfic size and adding Poisson
noise.  It should be noted that BraggNet works on a single peak at a time within
a small 32 by 32 window, which deviates significantly from conventional Bragg
peak finding tasks that require extracting peak positions from images typically
with hundreds or thousands of pixels along one dimension.  Furthermore, another
neural network method for Bragg peak analysis was detailed in the work of
BraggNN \citep{liuBraggNNFastXray2021}, emphasizing the refinement of Bragg peak
positions without the need for explicit fitting of a profile function, such as
the pseudo-Voigt profile.  Likewise, BraggNN works on a single peak at a time
within a 11 by 11 window, performing regression to two variables representing
the peak position.  To the best of our knowledge, no existing neural network
based peak-finding models have demonstrated the ability to detect multiple peaks,
which is the primary goal we strive to achieve with \peaknet{}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DIVIDER %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Methods}

% Summarize the method
% Breakdown
% - u-net
% - loss function
% - post process
% - labeling
%   - stream files, peak found and indexed
%   - label refinement

\peaknet{} uses a U-Net architecture to perform peak segmantation on diffraction
images, generating a heatmap of probabilities of a given pixel belonging to a
true peak.  A probability threshold is subsequently employed to translate the
heatmap into a binary mask or segmentation map, with a value of one indicating a
peak pixel and zero otherwise.  A connected component analysis
\citep{weaverCentrosymmetricCrossSymmetricMatrices1985} is then applied to
extract peak positions in image coordinates.  The entire peak finding process is
summarized in Fig. \ref{fig : peak finding}.  In this section, we present the
details in model training, comprising the specific U-Net architecture, the loss
function and the data labeling process.

\begin{figure*}[htbp]
\centering
\includegraphics[width=0.9\textwidth,keepaspectratio]
{./figures/peaknet.method.pdf}
\caption{Peak finding process in \peaknet{}.}
\label{fig : peak finding}
\end{figure*}

\subsection{The segmentation model: U-Net}

Peak segmentaiton in \peaknet{} is achieved by the use of U-Net
\citep{ronnebergerUNetConvolutionalNetworks2015} with a reduced number of
feature channels applied in both the contracting and expanding paths, as
depicted in Fig. \ref{fig : unet}.  A single contracting layer contains two
stride-one and zero-padding $3 \times 3$ convlutional layers with a rectified
linear unit (ReLU) \citep{fukushimaCognitronSelforganizingMultilayered1975} and
an additional stride-two $2 \times 2$ max-pooling layer.  The number of feature
channels doubles with respect to its previous contracting layer.  Likewise, a
single expanding path contains a stride-two $2 \times 2$ transposed
convolutional layers concatenated with the corresponding feature map from the
contracting path.  This is followed by two stride-one $3 \times 3$ convolutional
layers connected to a ReLU activation function.  It is worth noting that the
feature map cropping may be necessary during the concatenation between feature
maps from two paths.  In the last layer, all 8 channels will be mapped to a
single channel through a $1 \times 1$ convolution.

\begin{figure*}[htbp]    % Insert the figure HERE and TOP
\centering
\includegraphics[width=0.9\textwidth,keepaspectratio]
{./figures/unet.pdf}
\caption{The U-Net architecture in \peaknet{}.}
\label{fig : unet}
\end{figure*}

\subsection{The loss function: focal loss}

A main technical issue in training U-Net for Bragg peak detection is the extreme
peak-background class imbalance (e.g., $> 10^3 : 1$), resulting in reduced
prediction accuracy.  This may not pose as a problem in previous peak finders
like BraggNet, which operates on a much smaller area of $32 \times 32$, whereas
\peaknet{} is trained on larger multiple panel detectors, such as the
Cornell-SLAC pixel array detector (CSPAD) \citep{hartCornellSLACPixelArray2012}
with a dimension of $194 \times 185$ for one of its panels.  Focal loss was
introduced to address the extreme class imbalance problem for object detectors
\citep{linFocalLossDense2018}.  It is defined as:

\begin{equation}
    \text{FL}(p_{\text{peak}}) = -\alpha \cdot p_{\text{background}}^\gamma
    \cdot \log{p_{\text{peak}}}
\end{equation}

Here, $p_{\text{peak}}$ and $p_{\text{background}}$ are the probabilities of a
pixel being a peak and a background, respectively, with $p_{\text{peak}} +
p_{\text{background}} = 1$.  $\gamma$ controls a modulating factor
$p_{\text{background}}$ and $\alpha$ is an additional modulating factor.  In
practice, numerical instability will often emerge in the calculation of
$p_\text{peak}(x) = e^{-\text{logit(x)}}$ given an output value $x$ from the
U-Net, where $\text{logit} (x) = \log{(1 + e^{-x})}$.  To bypass this issue,
logit needs to be rewritten as $\text{logit}(x) = a + \log{(e^{-a} + e^{-x-a})}$,
where $a = max(0, -x)$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DIVIDER %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experiments}

\subsection{\peaknet{} on multi-panel detectors: Trained on panels but
predicting on assembled images.}

We demonstrated the possibility of \peaknet{} making prediction on assembled
images from a multi-panel detectors despite being trained on individual panels.
To facilitate this investigation, we utilized a multi-panel detector CSPAD,
which is widely used in serial crystallography experiments at LCLS.
Specifically, we used crystallographic data from the LCLS experiment
\textit{cxic0415} at run \textit{101} in the Coherent X-ray Imaging (CXI)
instrument, where the CSPAD deployed consists of 32 panels.  An individual
diffraction image recorded on CSPAD are conventionally saved in a stack of 64
mini-panels (half of a physical CSPAD panel).  For data labeling, we randomly
selected 268 mini-panels, which were labeled using the \psocake{} peak finder
with the default settings.  We then split the labeled data into 60\% training
set and 20\% validation set.  The remaining 20\% data were initially set aside
for testing purposes, but were not used due to the lack of an effecitve metrics,
which will be discussed later in the evaluation of our model's efficacy.  Our
test set included the first 5000 events of the run, which facilitated a faster
feedback loop compared with going through all events in the run.  Notably, we
didn't apply any image preprocessing, and thus \peaknet{} directly takes in an
diffraction image of its original size and outputs a segmentation map.

\begin{figure*}[htbp]
\centering
\includegraphics[width=0.9\textwidth,keepaspectratio]
{./figures/label_to_predict_with_zoom.pdf}
\caption{(a) \peaknet{} input images and peak labels.  (b) \peaknet{} prediction
on an entire CSPAD image.  (c) A magnified view of a small region of the
detector.}
\label{fig : label and predict}
\end{figure*}

Fig. \ref{fig : label and predict} (a) displays labeled samples, with the input
mini-panel image on the left and pixel-wise labeled peaks on the right.  The
overall peak label is a binary mask that shares the same size as the input, with
a value of one indicating a peak pixel and zero otherwise.  Consequently, each
input consists of a $185 \times 194$ mini-panel from the CSPAD and a binary mask
of the same size.  Additionally, Fig.  \ref{fig : label and predict} (b) shows a
sample model prediction on an entire CSPAD image with a size of $1739 \times
1748$.

\subsection{Examining \peaknet{}'s generalizability beyound the peak finder used
in labeling}

The current strategy for data labeling involves using an existing peak finder,
and it is important to evaluate whether any limitations of the peak finder used
in data labeling will affect the peak finding capability of \peaknet{}. One
specific limitation to investigate is the size dependency of the peak finder.
Notably, the peak size range is a user-defined input requested by the \psocake{}
peak finder. This works well when diffraction spots have consistent sizes.
However, detectors such as Rayonix have a large point spread function, which may
result in large peaks being ignored by the \psocake{} peak finder.  Consequently,
there is a concern about whether \peaknet{} will inherit the same limitations
since it is trained on \psocake{} peak labels.

\begin{figure*}[htbp]
\centering
\includegraphics[width=0.9\textwidth,keepaspectratio]
{./figures/rayonix.pdf}
\caption{Peak finding on a Raynoix image using (c) \peaknet{} and (d) \psocake{}.  (a), (b), (c) and (d) are magnified views of some regions.}
\label{fig : rayonix}
\end{figure*}

Fig. \ref{fig : rayonix} presents a side-by-side comparison of peak detection on
a Rayonix image, with the \peaknet{} results displayed on the left and the
\psocake{} results on the right. Upon visual inspection of Fig. \ref{fig :
rayonix} (c) and (d), both \peaknet{} and \psocake{} were observed to detect a
considerable number of peaks, suggesting a potentially comparable performance
between the two methods.  However, upon closer inspection of the view near the
area slightly below the beamstop position, one obvious, reasonably sized Bragg
peak was observed but not detected by the \psocake{} peak finder, whereas
\peaknet{} successfully located this peak.  This finding provides direct
evidence that \peaknet{}'s peak finding capability is not strictly limited by
the peak finder used in the data labeling process.  In fact, \peaknet{} appears
to possess its own understanding of Bragg peaks, as evidenced by the exclusion
of a weak single Bragg peak-like spot near the upper edge of the image, as shown
in Fig. \ref{fig : rayonix} (a) and (b).  Therefore, it's important to note that
\peaknet{} is not merely a neural network replica of the \psocake{} peak finder
despite being trained on labels supplied by it.

\subsection{Model efficacy and runtime performance}

We consider model efficacy of a peak finder in two metrics: (1) indexing rate
and (2) the number of indexed events.  Table \ref{tb : perf} provides a
comparative analysis of two distinct datasets, CXI and MFX, showcasing the
outcomes obtained when processed using two peak finders, \psocake{} and
\peaknet{}.  The detectors employed for the respective datasets are CSPAD and
Rayonix.  The analyzed events for the CXI dataset span from 0 to 5000, whereas
the MFX dataset encompasses a range of 0 to 8998.  \psocake{} identified 2107
events in the CXI dataset and 465 in the MFX dataset, yielding indexing rates of
71.2\% and 84.5\% correspondingly.  In contrast, \peaknet{} discovered 1991
events in the CXI dataset and 430 in the MFX dataset, exhibiting superior
indexing rates of 78.6\% and 90.2\%, respectively.  Although both peak finders
exhibit varying levels of effectiveness, our evaluation has revealed that
\peaknet{} consistently achieves superior indexing rates across both datasets,
while also yielding comparable numbers of indexed events.  These results suggest
that \peaknet{} may represent a more reliable and efficient solution for the
analysis of such data, compared to the alternative peak finder.

To provide further context and justification for this efficacy measure, it is
important to note that conventional metrics like accuracy, precision and F-1
scores are not always well-defined in the context of peak finding, due to the
lack of actual ``ground truth".  This is because the peak labels used for
training and evaluation are derived from another peak finder, rather than being
uniquely determined in some fashion.  As a result, it is necessary to consider
alternative measures of model performance and reliability, such as the indexing
rate and the number of indexed events.  However, it is not surprising that
conventional metrics may remain a viable option when applied to synthetic data
generated by a simulator.

\begin{table}[htbp]
\caption{
    Peak finding and indexing results.
}
\label{tb : perf}
\centering
\begin{tabular}{ | l || c | c | }
    \hline
    Dataset           &  CXI   & MFX\\
    \hline
    Detector          & CSPAD  & Rayonix \\
    Events to analyze & 0-5000 & 0-8998 \\
    \hline
    \psocake{}: Found         &  2107   & 465  \\
    \psocake{}: Indexed       &  1501   & 393  \\
    \psocake{}: Indexing rate &  71.2\% & 84.5\% \\
    \hline
    \peaknet{}: Found         &  1991   & 430  \\
    \peaknet{}: Indexed       &  1565   & 388  \\
    \peaknet{}: Indexing rate &  78.6\% & 90.2\% \\
    \hline
\end{tabular}
\end{table}

Furthermore, while the runtime performance of \peaknet{} is excellent as
compared with other crystallography data analysis methods in Table \ref{tb :
runtime}, there is a caveat to consider.  Although \peaknet{} is designed as a
nearly end-to-end solution, with its neural networks returning a segmentation map
that represents the pixel-wise probability of being a peak from input
diffraction images, we must employ connected component analysis to convert the
segmentation maps into peak coordinates.  While the neural network runtime is
exceptionally fast, capable of processing 11 Rayonix images ($1920 \times 1920$)
in parallel on a 1080 Ti GPU in just 4ms (equivalent to 0.36 ms per image), the
additional time required for connected component analysis is considerably longer
and thus a significant runtime bottleneck in the current version of \peaknet{}.
In fact, this bottleneck processing time scales nearly linearly with respect to
the number of images, and it adds an additional 30ms of processing time for each
image despite running on the same GPU.  Practically speaking, the current
version of \peaknet{} runs at 49ms per Rayonix event on 1080 Ti, which is
actually 10 $\times$ faster than some diffraction image classification
algorithms.

\begin{table*}[htbp]
\caption{
    The runtime performance of diffraction image analysis algorithms measured on
    Rayonix images containing 3.7 megapixels.  We measured runtime performance
    of \psocake{} and \peaknet{} directly using Rayonix images.  For reference
    purposes, we also included another peak finding method RPF
    \citep{hadian-jaziPeakfindingAlgorithmBased2017,
    hadian-jaziDataReductionSerial2021} and two classification methods for X-ray
    diffraction data reduction. RPF runtime performance was originally measured
    on AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019}.  The two
    classification methods were evaluated on 0.5 megapixel images using the CNN
    hit finder method \citep{keConvolutionalNeuralNetworkbased2018}, which was
    also used as a point of comparison in the ORB+MLP method
    \citep{rahmaniDataReductionXray2023}. A $*$ notation was used to indicate a
    linearly extrapolated processing time, but the real performance may vary
    depending on the specific hardware and the complexity of the underlying
    algorithm.
}
\label{tb : runtime}
\centering
\begin{tabular}{  | l || l | l | c | c | }
    \hline
    Method      &  Task & Hardware & Image size           & Time (ms/event)  \\
    \hline
    RPF         &  Peak Finding & Intel E5-2698 & 1024 $\times$ 1024 & $\sim$120.0            \\
                &               &               & 1920 $\times$ 1920 &
                $\sim$421.8*            \\
    \hline
    \psocake{}  &  Peak Finding & Intel E5-2620 & 1920 $\times$ 1920 & 200.0             \\
    \hline
    \textbf{\peaknet{}}  &  Peak Finding & NVIDIA 1080 Ti & 1920 $\times$ 1920 &
    \textbf{49.0}            \\
    \hline
    CNN hit finder  & Classification & NVIDIA 1080 Ti &  720 $\times$ 720 & 0.8 \\
                                                     & &                & 1920
                                                      $\times$ 1920 & 5.6* \\
    \hline
    ORB+MLP  & Classification & Intel Core i5  & 720 $\times$ 720 & 50.0 \\
                                                     & &                & 1920
                                                      $\times$ 1920 & 355.6* \\
    \hline
\end{tabular}
\end{table*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DIVIDER %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusions}

In this paper, we introduced \peaknet{}, a deep learning-based peak finder that
efficiently tackles the Bragg peak finding problem as a semantic segmentation
task. The U-Net architecture of \peaknet{} has been optimized to achieve an
ideal balance between efficacy and runtime performance, resulting in a
processing speed four times faster than the \psocake{} peak finder while
maintaining superior indexing rates and a comparable number of indexed events. A
notable bottleneck in the current version of \peaknet{} is the connected
component analysis, which scales linearly with input data volume, whereas the
neural network portion scales beyond linear capability on GPUs, limited largely
by GPU memory. It is worth mentioning that the current data reduction concept
primarily focuses on processing single events as quickly as possible, centering
the design principle on CPUs. However, with neural networks, we propose a new
direction towards batch image processing on GPUs, exemplified by \peaknet{} in
the context of serial crystallography.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DIVIDER %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Acknowledgment}

The project was conceived by J.B.T and C.H.Y. Earlier versions of the U-Net
models were tested by P.L. under the supervision of C.H.Y.  The experiments were
designed by C.W with inputs from C.H.Y.  C.W prepared the datasets, labeled
experimental data, and trained and evaluated the refined neural network model.
The manuscript was written by C.W and C.H.Y with input from all authors.  This
material is based upon work supported by the U.S.  Department of Energy, Office
of Science, Office of Basic Energy Sciences under Award Number FWP-100643.  Use
of the Linac Coherent Light Source (LCLS), SLAC National Accelerator Laboratory,
is supported by the U.S. Department of Energy, Office of Science, Office of
Basic Energy Sciences under Contract No.  DE-AC02-76SF00515.

\bibliographystyle{plainnat}
\bibliography{bibliography.bib}

\end{document}

### 2023-03-24 ieee_main.tex
Merge changes from Chuck.  I have added additional changes too.

@@
 \and
-\IEEEauthorblockN{Po-nan Li*\thanks{* Performed this work in
-a previous role at SLAC National Accelerator Laboratory}}
+\IEEEauthorblockN{Po-Nan Li}%*\thanks{* Performed this work in
+%a previous role at SLAC National Accelerator Laboratory}}
 %% City, Country \\
+\IEEEauthorblockA{\textit{Department of Electrical Engineering} \\ 
+\textit{Stanford University}\\
+liponan@stanford.edu} %, Stanford, CA 94305, U.S.A
 \and
@@
 Serial crystallography at X-ray free electron laser (XFEL) sources has
-experienced tremendous progresses in achieving high data rate in recent times.
+experienced tremendous progress in achieving high data rate in recent times.
 While this development offers potential to enable novel scientific
-investigations, such as imaging faster molecular events, it also poses
-challenges in regards to real-time data analysis, which may have to involve some
-degree of data reduction to only save those containing actionable information on
+investigations, such as imaging molecular events at logarithmic timescales, it also poses
+challenges in regards to real-time data analysis, which involves some
+degree of data reduction to only save those features or images pertaining to the science on
 disks.  If data reduction is not effective, it could directly result in a
 substantial increase in facility budgetary requirements, or even hinder the
-utilization of ultra-high repetition imaging techqniues.  Furthermore, an
+utilization of ultra-high repetition imaging techniques making data analysis unwieldy.  Furthermore, an
 additional challenge involves providing real-time feedback to users derived from
-real-time data analysis.  Under the framework of serial crystallography, the
+real-time data analysis.  In the context of serial crystallography, the
 initial and critical step in real-time data analysis is finding X-ray Bragg
@@
 indexing rates and comparable number of indexed events.  We formulated the task
-of peak finding into a semantic segmentation problem, which is then addressed by
-using the classical U-Net architecture.  A key advantage of \peaknet{} is its
+of peak finding into a semantic segmentation problem, which is implemented as a classical U-Net architecture.  A key advantage of \peaknet{} is its
 ability to scale linearly with respect to data volume, making it well-suited for
-real-time serial crystallography data analysis at high data rates.  Additionally,
-we identified a performance bottleneck that, if eliminated, would result in
-scaling beyound linear capability on GPUs.
+real-time serial crystallography data analysis at high data rates.
 \end{abstract}
@@
 
-Serial crystallography with X-ray free electron lasers (XFEL) has enabled the
-structural determination of three-dimensional macromolecules from radiation
-damage-free samples at room temperature, an approach commonly known as
+Serial femtosecond crystallography (SFX) with X-ray free electron lasers (XFEL) has enabled structural determination of macromolecules by outrunning radiation
+damage at room temperature, an approach commonly known as
 \textit{diffraction-before-destruction}
@@
 chapmanFemtosecondDiffractiveImaging2006,chapmanFemtosecondXrayProtein2011}.
-Time-resolved serial crystallography at XFEL facilities, like the Linac Coherent
+Time-resolved serial femtosecond crystallography (TR-SFX) at XFEL facilities, like the Linac Coherent
 Light Source (LCLS), allows the investigation of biochemical reactions with
-femtosecond-scale time resolutions.  This technique is typically referred to as
-serial femtosecond crystallography (SFX), which has led to many signficiant
+picosecond time resolution which has led to many significant
 structural studies \citep{kupitzSerialTimeresolvedCrystallography2014,
@@
 tackle two major challenges that arise in SFX experiments, namely data reduction
-and real time feedback.  Firstly, data reduction aims to extract and compress
-real-time actionable information by identifying important events, commonly
-referred to as ``hits", and vetoing irrelevant ones from terabytes per second of
-data streams.  One typical approach for SFX hit finding utilizes existing Bragg
+and real time feedback.  Firstly, data reduction aims to veto, extract and compress scientific data by identifying important events, commonly
+referred to as ``hits", and vetoing irrelevant ones from terabyte per second data streams.  One typical approach for SFX hit finding utilizes existing Bragg
 peak finders, such as the Cheetah peak finder
 \citep{bartyCheetahSoftwareHighthroughput2014}, the robust peak finder
-\citep{hadian-jaziPeakfindingAlgorithmBased2017} or the \psocake{} peak finder
-\citep{shinDataAnalysisUsing2018}.  Additionally, a neural networks-based SFX
+\citep{hadian-jaziPeakfindingAlgorithmBased2017}, DIALS peak finder \citep{Winter2018} or the \psocake{} peak finder
+\citep{shinDataAnalysisUsing2018}.  Additionally, a neural network-based SFX
 hit finder was reported to achieved a processing rate of 1.3 kHz on a single GPU
-\citep{keConvolutionalNeuralNetworkbased2018}.  Secondly, real-time feedback in
+\citep{keConvolutionalNeuralNetworkbased2018}.
+ORB feature extractor combined with a multilayer perceptron (MLP) hit classifier showed promising results for SFX data \citep{rahmaniDataReductionXray2023}.
+Secondly, real-time feedback in
 SFX experiments provides users with information on the experimental conditions
 and allows them to make real-time decisions that can optimize the data
-acquisition process.  For example, it's critical to fine-tune the hit rate to
-maximize the usage of samples;  it's also important to know the current
+acquisition process.  For example, it is critical to fine-tune the hit rate to
+maximize the usage of collected data;  it is also important to know the current
 diffraction limit, crystalline mosaicity, reciprocal space coverage, and other
-revelant factors over time.  Therefore, hit finding alone is insufficient to
+relevant factors over time.  Therefore, hit finding alone is insufficient to
 provide the necessary insights, making real-time Bragg peak finding crucial in
-delivering fast and comprehensive feedbacks.  The previously mentioned peak
+delivering fast and comprehensive feedback.  The previously mentioned peak
 finder in \psocake{} runs at roughly 5 Hz on a data center CPU, which may result
-in substantial costs when attempting to scale up the process.
+in substantial cost when attempting to scale up the process.
 
@@
 networks.  To accomplish this goal, we propose to train a neural network model
-to classify each individual pixel as either a peak pixel or not a peak pixel.
-This is followed by recognizing a connected area of pixels as a single peak, a
-task that can be readily accomplished through the connected component analysis
+to classify each individual pixel as either belonging to a peak or not belonging to a peak.
+This is followed by converting a connected area of pixels as a single peak, a
+task that can be readily accomplished through connected component analysis
 \citep{weaverCentrosymmetricCrossSymmetricMatrices1985}.  Subsequently, the peak
 coordinates will be determined by computing the center of mass of all the pixels
-that belong to the identified peak.  It's worth noting that the entire peak
-finding process takes place on GPUs, offering a cost-effective option for
+that belong to the identified peak.  It is worth noting that the entire peak
+finding process takes place on GPUs, offering a fully parallelizable approach for
 achieving scalability.  Concretely, our contributions can be summarized as
@@
     thousands of Bragg peaks with various peak profiles in detector images of
-    any size.  Despite being trained on peaks labeled by an existing peak finder,
+    any dimension.  Despite being trained on peaks labeled by an existing peak finder,
     we highlight that \peaknet{}'s capability is not limited by the peak finder
@@
     performance on large multi-panel ($1739 \times 1748$) and single-panel
-    ($1920 \times 1920$) detector.  It significantly outperformed existing
+    ($1920 \times 1920$) detectors.  It significantly outperformed existing
     methods in terms of indexing rate, while delivering comparable number of
-    indexed events.  We also finetuned the underlying U-Net architecture of
+    indexed events.  We also fine-tuned the underlying U-Net architecture of
     \peaknet{} to strike an optimal balance between model efficacy and runtime
-    performance, leading to a four times out-of-the-box processing speed than
-    \psocake{} peak finder.
+    performance, leading to a four times out-of-the-box processing speed improvement over \psocake{} peak finder.
 
@@
 libraries of peak shapes, but this method was found to be slow and inefficient
-in runtime, especially when dealing with peaks with low signal-to-noise ratios
+during runtime, especially when dealing with peaks with low signal-to-noise ratios
 (SNR).  The main obstacle lies in the localization of peaks and the tuning of
@@
 
-While template matching and region-growing tecnhiques require users to provide
-priori information like threshold values, Robust Peak Finder (RPF)
+While template matching and region-growing techniques require users to provide
+prior information like threshold values, Robust Peak Finder (RPF)
 \citep{hadian-jaziPeakfindingAlgorithmBased2017,
 hadian-jaziDataReductionSerial2021} has demonstrated proficient peak finding
-capabilities with minimal user inputs.  This techinuqe utilizes the Modified
+capabilities with minimal user input.  This technique utilizes the Modified
 Selective Statistical Estimator (MSSE) method to segment between background
 pixels and actual peaks.  Furthermore, the RPF method can also parallelize the
-processing of diffraction patterns, making it ideal for real-time data analysis.
+processing of diffraction patterns, making it suitable for real-time data analysis.
 
@@
 data reduction and analysis of XFEL experiments, and is routinely used at SLAC
-National Accelerator laborator (SLAC) and Pohang Accelerator Laboratory (PAL).
+National Accelerator Laboratory (SLAC) and Pohang Accelerator Laboratory (PAL).
 The built-in peak-finding algorithm \citep{shinDataAnalysisUsing2018} includes
-calibrating raw analog digital units (ADUs); applying optional background
+calibrating raw analog-to-digital units (ADUs); applying optional background
 correction and bad pixel masks; identifying possible peaks; calculating their
@@
 peaks to create training datasets, which underwent a number of preprocessing
-steps, including centering and cropping to a specfic size and adding Poisson
+steps, including centering and cropping to a specific size and adding Poisson
 noise.  It should be noted that BraggNet works on a single peak at a time within
@@
 the peak position.  To the best of our knowledge, no existing neural network
-based peak-finding models have demonstrated the ability to detect multiple peaks,
+based peak-finding models have demonstrated the ability to detect multiple peaks with high precision without manual tuning of peak finding parameters,
 which is the primary goal we strive to achieve with \peaknet{}.
@@
 
-\peaknet{} uses a U-Net architecture to perform peak segmantation on diffraction
+\peaknet{} uses a U-Net architecture to perform peak segmentation on diffraction
 images, generating a heatmap of probabilities of a given pixel belonging to a
@@
 
-Peak segmentaiton in \peaknet{} is achieved by the use of U-Net
+Peak segmentation in \peaknet{} is achieved by the use of U-Net
 \citep{ronnebergerUNetConvolutionalNetworks2015} with a reduced number of
@@
 depicted in Fig. \ref{fig : unet}.  A single contracting layer contains two
-stride-one and zero-padding $3 \times 3$ convlutional layers with a rectified
+stride-one and zero-padding $3 \times 3$ convolutional layers with a rectified
 linear unit (ReLU) \citep{fukushimaCognitronSelforganizingMultilayered1975} and
@@
 like BraggNet, which operates on a much smaller area of $32 \times 32$, whereas
-\peaknet{} is trained on larger multiple panel detectors, such as the
+\peaknet{} is trained on larger multi-panel detectors, such as the
 Cornell-SLAC pixel array detector (CSPAD) \citep{hartCornellSLACPixelArray2012}
@@
 \begin{equation}
-    \text{FL}(p_{\text{peak}}) = -\alpha \cdot p_{\text{background}}^\gamma
-    \cdot \log{p_{\text{peak}}}
+    \text{FL}(p) = -\alpha \cdot (1-p)^\gamma \cdot \log{p}.
 \end{equation}
 
-Here, $p_{\text{peak}}$ and $p_{\text{background}}$ are the probabilities of a
-pixel being a peak and a background, respectively, with $p_{\text{peak}} +
-p_{\text{background}} = 1$.  $\gamma$ controls a modulating factor
-$p_{\text{background}}$ and $\alpha$ is an additional modulating factor.  In
+Here, $p$ is the probabilities of a
+pixel $x$ being a peak.  $\gamma$ controls a modulating factor
+$(1-p)$ and $\alpha$ is an additional modulating factor.  We used $\gamma = 2.0$ and $\alpha = 1.2$ in \peaknet{}.  In
 practice, numerical instability will often emerge in the calculation of
-$p_\text{peak}(x) = e^{-\text{logit(x)}}$ given an output value $x$ from the
-U-Net, where $\text{logit} (x) = \log{(1 + e^{-x})}$.  To bypass this issue,
-logit needs to be rewritten as $\text{logit}(x) = a + \log{(e^{-a} + e^{-x-a})}$,
-where $a = max(0, -x)$.
+$p = e^{-\text{logit}}$, where $\text{logit} = \log{(1 + e^{-x})}$.  To bypass this issue,
+logit needs to be rewritten as $\text{logit} = a + \log{(e^{-a} + e^{-x-a})}$,
+where $a = max(0, -x)$.  As a result, if we denote the label of a pixel $x$ as $y$, the focal loss becomes
+
+\begin{equation}
+    \text{FL}(p) = \alpha \cdot y \cdot (1-p)^\gamma + \text{logit} + (1 - y) \cdot p^\gamma \cdot x + p^\gamma \cdot (1 - y) \cdot \text{logit}
+\end{equation}
 
@@
 We demonstrated the possibility of \peaknet{} making prediction on assembled
-images from a multi-panel detectors despite being trained on individual panels.
+images from a multi-panel detector despite being trained on individual panels.
 To facilitate this investigation, we utilized a multi-panel detector CSPAD,
 which is widely used in serial crystallography experiments at LCLS.
-Specifically, we used crystallographic data from the LCLS experiment
-\textit{cxic0415} at run \textit{101} in the Coherent X-ray Imaging (CXI)
+Specifically, we used crystallographic data of streptavidin crystals from LCLS experiment
+\textit{cxic0415} run \textit{101} at the Coherent X-ray Imaging (CXI)
 instrument, where the CSPAD deployed consists of 32 panels.  An individual
@@
 set and 20\% validation set.  The remaining 20\% data were initially set aside
-for testing purposes, but were not used due to the lack of an effecitve metrics,
+for testing purposes, but were not used due to the lack of an effective metric,
 which will be discussed later in the evaluation of our model's efficacy.  Our
@@
 feedback loop compared with going through all events in the run.  Notably, we
-didn't apply any image preprocessing, and thus \peaknet{} directly takes in an
+did not apply any image preprocessing, and thus \peaknet{} directly takes in a
 diffraction image of its original size and outputs a segmentation map.
@@
 peak finder. This works well when diffraction spots have consistent sizes.
-However, detectors such as Rayonix have a large point spread function, which may
+However, detectors such as the Rayonix have a large point spread function for intense peaks, which may
 result in large peaks being ignored by the \psocake{} peak finder.  Consequently,
@@
 {./figures/rayonix.pdf}
-\caption{Peak finding on a Raynoix image using (c) \peaknet{} and (d) \psocake{}.  (a), (b), (c) and (d) are magnified views of some regions.}
+\caption{Peak finding on a Rayonix image using (c) \peaknet{} and (d) \psocake{}.  (a), (b), (c) and (d) are magnified views of some regions.}
 \label{fig : rayonix}
@@
 a Rayonix image, with the \peaknet{} results displayed on the left and the
-\psocake{} results on the right. Upon visual inspection of Fig. \ref{fig :
+\psocake{} results on the right.
+The diffraction data were collected from crystals of SARS-CoV-2 proteases using the Macromolecular Femtosecond Crystallography (MFX) instrument \citep{sierraMacromolecularFemtosecondCrystallography2019} at LCLS.
+Upon visual inspection of Fig.
+\ref{fig :
 rayonix} (c) and (d), both \peaknet{} and \psocake{} were observed to detect a
@@
 of a weak single Bragg peak-like spot near the upper edge of the image, as shown
-in Fig. \ref{fig : rayonix} (a) and (b).  Therefore, it's important to note that
-\peaknet{} is not merely a neural network replica of the \psocake{} peak finder
+in Fig. \ref{fig : rayonix} (a) and (b).  Therefore, it is important to note that
+\peaknet{} is not merely a neural network-based replica of the \psocake{} peak finder
 despite being trained on labels supplied by it.
@@
 events in the CXI dataset and 465 in the MFX dataset, yielding indexing rates of
-71.2\% and 84.5\% correspondingly.  In contrast, \peaknet{} discovered 1991
+71.2\% and 84.5\%, respectively.  In contrast, \peaknet{} discovered 1991
 events in the CXI dataset and 430 in the MFX dataset, exhibiting superior
@@
 exhibit varying levels of effectiveness, our evaluation has revealed that
-\peaknet{} consistently achieves superior indexing rates across both datasets,
+\peaknet{} achieves superior indexing rates across both datasets,
 while also yielding comparable numbers of indexed events.  These results suggest
 that \peaknet{} may represent a more reliable and efficient solution for the
-analysis of such data, compared to the alternative peak finder.
+analysis of such data.
 
@@
 alternative measures of model performance and reliability, such as the indexing
-rate and the number of indexed events.  However, it is not surprising that
+rate and the number of indexed events.  However, 
 conventional metrics may remain a viable option when applied to synthetic data
 generated by a simulator.
+For clarification purposes, we used the \textit{indexamajig} tool within the \textit{CrystFEL} data analysis software \citep{whiteCrystFELSoftwareSuite2012} to perform indexing.
+We employed multiple indexing methods, including \textit{mosflm}, \textit{xds} and \textit{xgandalf}, with an additional setting of \textit{-int-radius=4,5,6}.
 
@@
     \hline
-    \psocake{}: Found         &  2107   & 465  \\
+    \psocake{}: Hits found         &  2107   & 465  \\
     \psocake{}: Indexed       &  1501   & 393  \\
@@
     \hline
-    \peaknet{}: Found         &  1991   & 430  \\
+    \peaknet{}: Hits found         &  1991   & 430  \\
     \peaknet{}: Indexed       &  1565   & 388  \\
@@
 
-The project was conceived by J.B.T and C.H.Y. Earlier versions of the U-Net
-models were tested by P.L. under the supervision of C.H.Y.  The experiments were
-designed by C.W with inputs from C.H.Y.  C.W prepared the datasets, labeled
+Earlier versions of the U-Net
+models were built and tested by P.L under the supervision of C.H.Y.  The experiments were
+designed by C.W with inputs from J.B.T and C.H.Y.  C.W prepared the datasets, labeled
 experimental data, and trained and evaluated the refined neural network model.

### 2023-06-16 manuscript.tex
First commit.

%% \documentclass[a4paper,twocolumn]{article}
\documentclass[a4paper]{article}

\usepackage{style}      % Custom style
\usepackage{more}
\usepackage{constants}  % Load constants

% Author block
\renewcommand*{\Authfont}{\normalsize\normalfont}
\renewcommand*{\Affilfont}{\small\itshape}
\author[1]{Cong Wang}
\author[2]{Po-Nan Li}
\author[1]{Jana Thayer}
\author[1,*]{Chun Hong Yoon}
\affil[1]{Linac Coherent Light Source, SLAC National Accelerator Laboratory, Menlo Park, CA, USA.}
\affil[2]{Department of Electrical Engineering, Stanford University, Stanford, CA, USA.}
\affil[*]{Corresponding author: {\textnormal{\texttt{yoon82@slac.stanford.edu}}}}

\begin{document}

% Metadata
% Backward-compatible with latex2e
% Otherwise, it's okay to keep metadata ahead of begin{document}
\title{PeakNet: An Autonomous Bragg Peak Finder with Deep Neural Networks}

\maketitle

\begin{abstract}

Serial crystallography at X-ray free electron laser (XFEL) sources has
experienced tremendous progresses in achieving high data rate in recent times,
offering potential to enable novel scientific investigations, such as imaging
faster molecular events.  However, this approach also generates a significant
amount volume of data with sparsely distributed scientific signals, posing
challenges in data reduction and real-time feedback.  To address these concerns,
a rapid and efficient Bragg peak finding process serves as the pivotal initial
step, effectively addressing both data storage concerns and real-time feedback
requirements simultaneously.  Here, we present \peaknet{}, a autonomous Bragg
peak finder that utilizes deep neural networks, eliminating the need for manual
parameter tuning common in conventional peak finders and the laborious task of
manually masking pixels affected by artifact scattering, such as nozzle
scattering rings.  \peaknet{} also exhibits exceptional runtime efficiency,
processing a $1920 \times 1920$ image around 90 ms on an NVIDIA 1080 Ti GPU,
with the potential for further enhancements through parallelized analysis or GPU
stream processing.  With its ability to scale linearly with respect to data
volume, \peaknet{} is well-suited for real-time serial crystallography data
analysis at high data rates.

\end{abstract}

\section{Introduction}

Serial crystallography with X-ray free electron lasers (XFEL) has enabled the
structural determination of three-dimensional macromolecules from radiation
damage-free samples at room temperature, an approach commonly known as
\textit{diffraction-before-destruction}
\citep{neutzePotentialBiomolecularImaging2000,
chapmanFemtosecondDiffractiveImaging2006,chapmanFemtosecondXrayProtein2011}.
Time-resolved serial crystallography at XFEL facilities, like the Linac Coherent
Light Source (LCLS), allows the investigation of biochemical reactions with
femtosecond-scale time resolutions.  This technique is typically referred to as
serial femtosecond crystallography (SFX), which has led to many signficiant
structural studies \citep{kupitzSerialTimeresolvedCrystallography2014,
nangoThreedimensionalMovieStructural2016,pandeFemtosecondStructuralDynamics2016a,
youngStructurePhotosystemII2016,sugaLightinducedStructuralChanges2017,
kernStructuresIntermediatesKok2018,ibrahimUntanglingSequenceEvents2020,
sugaTimeresolvedStudiesMetalloproteins2020} since the first published work at
LCLS \citep{aquilaTimeresolvedProteinNanocrystallography2012}.  In the meantime,
the data rate at XFEL facilities have also gradually increased from hundreds of
Hz to the MHz range, with the European X-ray Free Electron Laser (EuXFEL) being
the first MHz facility available to users and LCLS-II set to launch in 2023.

At the MHz data rate, novel real-time data analysis approaches are needed to
tackle two major challenges that arise in SFX experiments, namely data reduction
and real time feedback.  One common approach for finding hits in serial
crystallography data is to utilize existing Bragg peak finders like the Cheetah
peak finder \citep{bartyCheetahSoftwareHighthroughput2014}, the Robust Peak
Finder (RPF) \citep{hadian-jaziPeakfindingAlgorithmBased2017}, or the \psocake{}
\citep{yoonPsocakeGUIMaking2020} peak finder.  Additionally, a deep neural
network-based hit finder for serial crystallography has been reported to achieve
a processing rate of 1.3 kHz by analyzing downsized 180 $\times$ 180 images
using a single GPU \citep{keConvolutionalNeuralNetworkbased2018}.  Secondly,
real-time feedback in serial crystallography experiments plays a crucial role by
providing users with important information about the experimental conditions.
This enables them to make timely decisions that optimize the data acquisition
process. For instance, it is essential to fine-tune the hit rate to maximize the
utilization of samples. Additionally, it is important to monitor factors such as
the current diffraction limit, crystalline mosaicity, reciprocal space coverage,
and other relevant parameters over time. Therefore, relying solely on hit
finding is insufficient to gain the necessary insights, making real-time Bragg
peak finding vital for delivering prompt and comprehensive feedback. However,
the peak finder mentioned earlier in \psocake{} operates at a rate of
approximately 5 Hz on a data center CPU, which could lead to significant costs
when scaling up the process.

In this work, we introduce \peaknet{}, a solution that effectively addresses the
challenge of autonomously and efficiently identifying Bragg peaks in high data
rate scenarios.  Our approach involves transforming the peak finding problem into
semantic segmentation tasks, where different regions within diffraction images
are classified and segmented using deep learning networks.  By leveraging this
process, \peaknet{} autonomously detects Bragg peaks while effectively
identifying strong artifact scattering, eliminating the need for human
intervention.  Subsequently, connected areas of pixels are examined and treated
as individual peaks, a task easily accomplished through connected component
analysis \citep{weaverCentrosymmetricCrossSymmetricMatrices1985}.  The
coordinates of the peaks are determined by calculating the center of mass of all
pixels belonging to each identified peak.  Notably, the entire peak finding
process is performed on GPUs, offering a cost-effective solution for achieving
scalability.

\section{Related work}

Reliable and automatic peak finding algorithms have undergone multiple
iterations of development.  An early approach involved utilizing template
matching \citep{wilkinsonIntegrationSinglecrystalReflections1988a} based on
libraries of peak shapes, but this method was found to be slow and inefficient
in runtime, especially when dealing with peaks with low signal-to-noise ratios
(SNR).  The main obstacle lies in the localization of peaks and the tuning of
user parameters for pattern matching, compounded by the difficult task of
developing a comprehensive library of peak shapes.  Another influential approach
employed region-growing techniques
\citep{bolotovskySeedSkewnessMethodIntegration1995,
bartyCheetahSoftwareHighthroughput2014} to detect pixel areas with high
skewness.  In the context of serial crystallography with XFEL sources, the
efficacy of this method was diminished due to the lack of sufficient data to
provide reliable statistics, rendering it susceptible to outliers and less adept
in analyzing weak peaks at higher scattering angles, which are essential for
achieving atomic resolution in structure determination.

While template matching and region-growing tecnhiques require users to provide
priori information like threshold values, Robust Peak Finder (RPF)
\citep{hadian-jaziPeakfindingAlgorithmBased2017,
hadian-jaziDataReductionSerial2021} has demonstrated proficient peak finding
capabilities with minimal user inputs.  This techinuqe utilizes the Modified
Selective Statistical Estimator (MSSE) method to segment between background
pixels and actual peaks.  Furthermore, the RPF method can also parallelize the
processing of diffraction patterns, making it ideal for real-time data analysis.

\psocake{} is a software specifically designed to streamline high throughput
data reduction and analysis of XFEL experiments, and is routinely used at SLAC
National Accelerator laborator (SLAC) and Pohang Accelerator Laboratory (PAL).
The built-in peak-finding algorithm \citep{shinDataAnalysisUsing2018} includes
calibrating raw analog digital units (ADUs); applying optional background
correction and bad pixel masks; identifying possible peaks; calculating their
SNR; determining Bragg spot sizes; and selecting peaks based on size, total
intensity and SNR.

In recent years, neural network models have emerged as a promising avenue for
Bragg peak finding.  BraggNet \citep{sullivanBraggNetIntegratingBragg2019} is
the first method that demonstrates proficiency of neural network models,
specifically U-Net \citep{ronnebergerUNetConvolutionalNetworks2015}, in
accurately segmenting peak pixels, including weak peaks, from background pixels
in neutron crystallography data.  Specifically, BraggNet employed simulated
peaks to create training datasets, which underwent a number of preprocessing
steps, including centering and cropping to a specfic size and adding Poisson
noise.  It should be noted that BraggNet works on a single peak at a time within
a small 32 by 32 window, which deviates significantly from conventional Bragg
peak finding tasks that require extracting peak positions from images typically
with hundreds or thousands of pixels along one dimension.  Furthermore, another
neural network method for Bragg peak analysis was detailed in the work of
BraggNN \citep{liuBraggNNFastXray2021}, emphasizing the refinement of Bragg peak
positions without the need for explicit fitting of a profile function, such as
the pseudo-Voigt profile.  Likewise, BraggNN works on a single peak at a time
within a 11 by 11 window, performing regression to two variables representing
the peak position.  To the best of our knowledge, no existing neural network
based peak-finding models have demonstrated the ability to detect multiple peaks,
which is the primary goal we strive to achieve with \peaknet{}.

\section{Methods}

The current peak finding process of \peaknet{} comprises two steps, as depicted
in Fig. \ref{fig : peak finding}.  Firstly, a segmentation map is obtained from
the input image using deep neural networks.  Subsequently, peak positions are
determined based on the generated segmentation map using connected component
analysis \citep{weaverCentrosymmetricCrossSymmetricMatrices1985}.  Importantly,
\peaknet{} has the capability to process inputs with arbitrary image sizes in a
batch manner, enabling efficient analysis.

In this section, our focus is to provide a comprehensive understanding of the
underlying deep neural network components in \peaknet{}.  We will specifically
discuss the network architecture, data augmentation techniques, and the loss
function employed during the training process.  Furthermore, we will emphasize
the use of iterative data curation in addressing the outlier problem.

\begin{figure*}[!ht]
\includegraphics[width=\textwidth,keepaspectratio]
{./figures/peaknet_steps.pdf}
\caption{The peak finding process of \peaknet{} consists of two steps: (1)
obtaining a segmentation map from the input using the underlying deep neural
networks; (2) identifying peak positions based on the generated segmentation map
using connected component analysis.  It is worth noting that \peaknet{} is
capable of accommodating input with arbitrary image sizes and batch sizes.  }
\label{fig : peak finding}
\end{figure*}

\subsection{Neural network architecture}

The underlying neural network architecture of \peaknet{} is illustrated in
Figure \ref{fig : network arc} (a).  It employs a residual attention U-Net
architecture, comprising three main components: a feature extraction ``backbone",
a feature fusion ``neck", and a single prediction ``head".  The feature
extraction ``backbone" utilizes multiple residual double convolutional blocks to
extract multi-resolution features, as visualized in Figure \ref{fig : network
arc} (b).  In the feature fusion ``neck", low-resolution features are merged
with high-resolution features using gated feature fusion blocks, as depicted in
\ref{fig : network arc} (c).  Each block incorporates an attention gate that
enhances shared features within both low and high-resolution feature maps.  The
resulting combined features from each gated feature fusion block are then
rearranged by a subsequent residual double convolutional block.  Finally, to
accomplish the segmentation task, the prediction ``head" leverages fused
features from the ``neck" and generates a prediction map encompassing three
distinct labels: background, Bragg peak, and artifact scattering.  The ``head"
itself consists of a 1 $\times$ 1 convolutional layer followed by a softmax
function.

It is essential to acknowledge that our neural network architecture is primarily
based on the original ``Attention U-Net" design
\citep{oktayAttentionUNetLearning2018}.  However, we want to point out that the
three-component design, consisting of the ``backbone", ``neck" and ``head",
offers the flexibility to replace these components with different architectures.
For instance, the ``backbone" can be substituted with RegNet
\citep{radosavovicDesigningNetworkDesign2020}, while the ``neck" can be replaced
with other multi-resolution feature fusion methods like feature pyramid networks
(FPN) \citep{linFeaturePyramidNetworks2017} or bidirectional feature pyramid
networks (BiFPN) \citep{tanEfficientDetScalableEfficient2020}.  Additionally,
the ``head" can be extended to perform additional tasks, if desired, such as
predicting the likelihood of the input image being indexable.  This modular
approach provides flexibility and allows for customization based on specific
requirements.

\begin{figure*}[!ht]
\includegraphics[width=\textwidth,keepaspectratio]
{./figures/network_arc.pdf}
\caption{Neural network architecture: Attention U-Net with residual connections.
(a) Overall end-to-end network architecture.  (b) The residual double
convolutional block.  (c) The gated feature fusion block for merging
multi-resolution features.}
\label{fig : network arc}
\end{figure*}

\subsection{Focal loss as the loss function}

One main technical issue in training neural networks for Bragg peak segmentation
is the extreme peak-background class imbalance (e.g., $> 10^3 : 1$), resulting
in reduced prediction accuracy.  This may not pose as a problem in previous peak
finders like BraggNet, which operates on a much smaller area of $32 \times 32$,
whereas \peaknet{} is trained on larger detectors, such as Rayonix MX340-XFEL
detector with a dimension of 1920 $\times$ 1920, even after downsizing by a
factor of 4.  To mitigate this challenge, focal loss was introduced to address
the extreme class imbalance problem for object detectors
\citep{linFocalLossDense2018}.  More specifically, we employed a categorical
focal loss.

\begin{align}
\text{CFL} &= - \sum_{i = 1}^{N}\sum_{j = 1}^{C} 
            \alpha_j \cdot y_j^{(i)} \cdot (1-\hat{p}_j^{(i)})^\gamma 
            \cdot \log{\hat{p}_j^{(i)}} \\
\hat{p}_j^{(i)} &= f_\theta(x_j^{(i)})
\end{align}

where CFL stands for categorical focal loss, $\alpha_j$ is a balancing factor
for each class, $y_j^{(i)}$ is the grouth truth label of the $j$-th class for
the $i$-th example.  $p_j^{(i)}$ is the predicted probability of the $j$-th
class for the $i$-th example, calculated by the neural network $f$ parameterized
by $\theta$ given input $x_j^{(i)}$.  $\gamma$ is a parameter controling the
extent to which the weight of well-classified examples, such as background
pixels, is reduced.  In our neural network training, we chose $\alpha = 1.2$
across all examples and $\gamma = 2.0$.  Essentially, this means $(1-\hat{p}
_j^{(i)}) ^\gamma$ is solely responsible for down-weighting easy examples, as
$\hat{p} _j^{(i)}$ is usually large in this case.

\subsection{Data augmentation}

We applied three data augmentation techniques to each diffraction pattern in our
dataset, including random in-plane rotation, random shifting in both horizontal
and vertical directions and random masking.  Random in-plane rotation and
shifting augment the training data, reducing the model's tendency to memorize
features at specific locations.  This variability promotes more generalized
feature extraction and improved generalization performance.  Random masking
involves randomly obscuring parts of the input data, forcing the model to learn
other relevant features that enhance its predictive capabilities during
training.  The result of applying data augmentation to an arbitrary example is
shown in Fig. \ref{fig : data aug}.

\begin{figure*}[!ht]
\includegraphics[width=\textwidth,keepaspectratio]
{./figures/data_aug.pdf}
\caption{Data augmentation is utilized on an input (a) and its corresponding
labeled segmentation map (b). The zoomed-in views of (a) and (b) are represented
by (c) and (d), respectively. The segmentation label distinguishes red pixels as
peaks and blue pixels as artifact scattering, attributed to ``nozzle scattering"
in this particular scenario.}
\label{fig : data aug}
\end{figure*}

\subsection{Dataset improvement and correction}

\peaknet{} employs a data-driven approach to accurately identify Bragg peaks,
requiring dataset improvement and correction to enhance performance.  This
contrasts with model-driven approaches that primarily entail direct model
modification to improve capabilities.  Fig. \ref{fig : data engine} illustrates
a feedback loop for iterative dataset improvement and correction.

The process begins with the preparation of a source dataset, often accomplished
through a combination of algorithmic and manual data labeling.  Subsequently,
the deep neural networks within \peaknet{} are trained on this dataset to learn
how to accurately detect peaks.  Following training, the model is deployed to
predict peaks on previously unseen data, and its performance is thoroughly
evaluated.  During this evaluation, instances that notably worsen the
performance of \peaknet{} are identified.  To address these limitations, we
either correct low-quality labels predicted by the neural networks or,
alternatively, acquire additional data that closely resemble these challenging
instances and carefully annotate them.  Finally, we merge these newly labeled
instances into the training set and retrain the model, thereby improving its
overall performance.

Interestingly, during the initial pass of this iterative process, \peaknet{}
showed limited performance when dealing with images containing relatively low
levels of photons.  However, by obtaining and annotating these images, we were
able to enhance the training dataset and, as a result, significantly improve the
predictive performance of \peaknet{}.

\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth,keepaspectratio,trim={1in 0in 1in 0in}]
{./figures/data_engine.pdf}
\caption{The process of iterative dataset and model improvement.}
\label{fig : data engine}
\end{figure}

\section{Results}

The primary goal of \peaknet{} is to autonomously detect Bragg peaks in
diffraction images, devoid of any user input, such as algorithmic parameter
tuning or manual artifact masking.  We implemented a two-step approach for peak
detection, employing deep neural networks to perform semantic segmentation,
which was subsequently followed by connected component analysis to extract image
coordinates of Bragg peaks from the generated segmentation maps.  In this
section, we begin by introducing the datasets used for training, validating, and
testing \peaknet{}. Next, we present the evaluation results that demonstrate the
predictive performance of \peaknet{}. Finally, we showcase its auto-masking
capability and runtime efficiency.

\subsection{Dataset}

We obtained X-ray diffraction images from two experiments conducted at the
Macromolecular Femtosecond Crystallography (MFX) instrument within LCLS.  The
primary dataset utilized for training and evaluating \peaknet{} is ``mfx13016"
(Run number: 28,31-34, 36-38), which contains diverse biological samples, e.g.
thaumatin and proteinase, and this experiment was originally used for automated
drop dispensing research \citep{suSerialCrystallographyUsing2021}.  These
diffraction images were recorded on a Rayonix MX340-XFEL detector with a
dimension of 1920 $\times$ 1920, downsized by a factor of 4 to accommodate a
higher readout rate.

The dataset ``mfx13016" exhibits a notable characteristic of prominent nozzle
scattering rings accompanied by bright Bragg peak-like spots located on the
rings.  This characteristic presents two primary challenges for crystallography
data analysis: increased difficulty in crystal indexing and misleading
integration results caused by artifact scattering.  The current best practice
involves manual masking of these artifact scattering, enabling data analysis to
proceed as if they are absent, but this process is prone to errors and
time-consuming.  Additionally, the final outcomes often hinge on the expertise
of the individuals conducting the data processing, resulting in biases,
scalability limitations, lack of standardization, and the possibility of human
errors.  Nevertheless, the inherent challenges presented by this dataset offer
an exceptional opportunity to testify the autonomous peak finding capability of
\peaknet{}.

The neural network training dataset consists of 98 Rayonix images in run 28 of
``mfx13016", which includes thaumatin samples, and an additional 37 images
sampled from an internal LCLS experimental dataset related to therapeutics
development associated with SARS-CoV-2.  Incorporating the SARS-CoV-2 dataset
aims to educate \peaknet{} about the presence of images without artifact rings,
diversifying its understanding of different data characteristics.  Nonetheless,
all these images used for neural network training have a dimension of 1920
$\times$ 1920 and they are divided into an 80\% training set and a 20\%
validation set.  The final test dataset for evaluating the model comprises all
images in run 31-34 and run 36-38 of ``mfx13016".

\subsection{Evaluating \peaknet{}'s predictive performance}

The peak finding performance of peak finders is evaluated through two
significant indicators from a user's standpoint: the number of successfully
indexed hits and the merging statistics.  For our evaluation, we utilized the
CrystFEL software suite \citep{whiteCrystFELSoftwareSuite2012} to perform
crystal indexing, integration, and merging tasks.  We use \psocake{}'s peak
finder as a baseline in this evaluation.

\subsubsection{Indexing results}

\peaknet{} and \psocake{}, when manually fine-tuned, exhibit comparable peak
finding performance in terms of the number of hits and the number of indexed
images, as shown in Table \ref{tb : index}.  However, it is critical to
emphasize that while \peaknet{} operates entirely autonomously, \psocake{}'s
performance is contingent upon manual parameter fine-tuning and manual artifact
scattering masking.  For example, an earlier work
\citep{suSerialCrystallographyUsing2021}, which processed essentially the same
experimental data, reported significantly lower hit count and indexed image
count.  Consequently, this highlights \peaknet{}'s advantage in user-independent
data processing.

Moreover, while users might prioritize the absolute number of indexed images as
a more straightforward metric, the indexing rate provides valuable insights into
the method's efficiency.  Both metrics jointly offer a more comprehensive
evaluation of the peak finding method. In the case of \peaknet{}, both the
consistently high number of indexed images and the good indexing rate testify to
its effective and reliable autonomous peak finding process, positioning it as a
highly viable option for Bragg peak finding.

\begin{table*}

\caption{Comparison of crystal indexing results for different methods on the
test dataset.  The table shows the number of hits, number of indexed hits, and
indexing rates for \peaknet{}, \psocake{} (fine-tuned) and \psocake{} (Su 2021).
The ``Run (Samples)" column lists the specific run numbers and biological
samples (TH: thaumatin; PK: proteinase).}

\label{tb : index}

\resizebox{1.0\textwidth}{!}{
\begin{tabular}{lllllllll}
\hline
\multicolumn{1}{l}{Methods}                                                                            & \multicolumn{1}{l}{Run (Samples)}        & \multicolumn{1}{l}{31 (TH)} & \multicolumn{1}{l}{32 (TH)} & \multicolumn{1}{l}{33 (TH)} & \multicolumn{1}{l}{34 (TH)} & \multicolumn{1}{l}{36 (TH)} & \multicolumn{1}{l}{37 (PK)} & 38 (PK) \\ \hline
\multicolumn{1}{l}{\multirow{3}{*}{\peaknet{}}}                                                        & \multicolumn{1}{l}{Number of hits}       & \multicolumn{1}{l}{1205}    & \multicolumn{1}{l}{3248}    & \multicolumn{1}{l}{5797}    & \multicolumn{1}{l}{3949}    & \multicolumn{1}{l}{1184}    & \multicolumn{1}{l}{1030}    & 1223    \\ \cline{2-9}
\multicolumn{1}{l}{}                                                                                   & \multicolumn{1}{l}{Number of indexed}    & \multicolumn{1}{l}{860}     & \multicolumn{1}{l}{2856}    & \multicolumn{1}{l}{3433}    & \multicolumn{1}{l}{2401}    & \multicolumn{1}{l}{919}     & \multicolumn{1}{l}{953}     & 1169    \\ \cline{2-9}
\multicolumn{1}{l}{}                                                                                   & \multicolumn{1}{l}{Indexing rate}        & \multicolumn{1}{l}{0.71}    & \multicolumn{1}{l}{0.88}    & \multicolumn{1}{l}{0.59}    & \multicolumn{1}{l}{0.61}    & \multicolumn{1}{l}{0.78}    & \multicolumn{1}{l}{0.93}    & 0.96    \\ \hline
\multicolumn{9}{l}{}                                                                                                                                                                                                                                                                                                                                \\ \hline
\multicolumn{1}{l}{\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}\psocake{}\\ (fine-tuned)\end{tabular}}} & \multicolumn{1}{l}{Number of hits}       & \multicolumn{1}{l}{1193}    & \multicolumn{1}{l}{3087}    & \multicolumn{1}{l}{5769}    & \multicolumn{1}{l}{3926}    & \multicolumn{1}{l}{917}     & \multicolumn{1}{l}{1070}    & 1212    \\ \cline{2-9}
\multicolumn{1}{l}{}                                                                                   & \multicolumn{1}{l}{Number of indexed}    & \multicolumn{1}{l}{849}     & \multicolumn{1}{l}{2657}    & \multicolumn{1}{l}{3375}    & \multicolumn{1}{l}{2364}    & \multicolumn{1}{l}{760}     & \multicolumn{1}{l}{1005}    & 1202    \\ \cline{2-9}
\multicolumn{1}{l}{}                                                                                   & \multicolumn{1}{l}{Indexing rate}        & \multicolumn{1}{l}{0.71}    & \multicolumn{1}{l}{0.86}    & \multicolumn{1}{l}{0.59}    & \multicolumn{1}{l}{0.6}     & \multicolumn{1}{l}{0.83}    & \multicolumn{1}{l}{0.94}    & 0.99    \\ \hline
\multicolumn{9}{l}{}                                                                                                                                                                                                                                                                                                                                \\ \hline
\multicolumn{1}{l}{\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}\psocake{}\\ (Su2021) \end{tabular}}}    & \multicolumn{1}{l}{Number of hits}       & \multicolumn{1}{l}{1083}    & \multicolumn{1}{l}{2454}    & \multicolumn{1}{l}{5604}    & \multicolumn{1}{l}{3756}    & \multicolumn{1}{l}{363}     & \multicolumn{1}{l}{683}     & 771     \\ \cline{2-9}
\multicolumn{1}{l}{}                                                                                   & \multicolumn{1}{l}{Number of indexed}    & \multicolumn{1}{l}{271}     & \multicolumn{1}{l}{1094}    & \multicolumn{1}{l}{963}     & \multicolumn{1}{l}{770}     & \multicolumn{1}{l}{266}     & \multicolumn{1}{l}{569}     & 709     \\ \cline{2-9}
\multicolumn{1}{l}{}                                                                                   & \multicolumn{1}{l}{Indexing rate}        & \multicolumn{1}{l}{0.25}    & \multicolumn{1}{l}{0.45}    & \multicolumn{1}{l}{0.17}    & \multicolumn{1}{l}{0.21}    & \multicolumn{1}{l}{0.73}    & \multicolumn{1}{l}{0.83}    & 0.92    \\ \hline
\end{tabular}
}

\end{table*}

\subsubsection{Merging statistics}

Merging statistics confirms \peaknet{}'s robust performance in terms of
consistency and quality in data processing.  For the thaumatin (TH) sample,
\peaknet{} demonstrates marginally superior performance in terms of R-split
values, correlation coefficients, $I/\sigma(I)$ values, redundancy, and
completeness, achieving these results autonomously.  Notably, the R-split value
for the TH sample is slightly lower for \peaknet{} (0.2605 vs. 0.2732),
suggesting slightly better internal consistency. Similarly, correlation
coefficients for \peaknet{} are marginally higher (CC$_1/2$: 0.9434 vs.  0.9368;
CC*: 0.9853 vs. 0.9835), indicating a minor advantage in the precision of
measurements.

However, for the proteinase (PK) sample, the performance comparision is mixed.
Although \peaknet{} lags slightly behind manually fine-tuned \psocake{} in terms
of R-split and redundancy, it outperforms in CC$_1/2$, CC*, $I/\sigma(I)$, and
completeness values.  This reinforces the effectiveness of \peaknet{} in
achieving respectable results across varied sample types, without any manual
intervention or parameter fine-tuning.

Overall, \peaknet{} demonstrates comparable performance to a manually fine-tuned
\psocake{} for two distinct samples, showcasing its potential for autonomous
peak finding with consistent results.  By reducing dependence on the expertise
of individuals, which can have considerable variation, \peaknet{} offers a
promising user-indepenent solution.  Notably, despite primarily being trained on
PK samples, \peaknet{} maintains robust and versatile performance, indicating
its broad applicability and effectiveness in handling diverse datasets.

\begin{table*}
\caption{Merging statistics (TH: thaumatin; PK: proteinase).  TH results were
merged from run 31, 32, 33, 34 and 36, whereas PK results were merged from run
37 and 38.}
\label{tb : merge}
\centering
\resizebox{1.0\textwidth}{!}{
\begin{tabular}{lllllllll}
\hline
Sample              & Methods & R-split & CC$_{1/2}$     & CC*       & $I/\sigma(I)$   & Resolution range (Å) & Redundancy & Completeness \\ \hline
\multirow{2}{*}{TH} & \peaknet{} & 0.2605  & 0.9434 & 0.9853 & 2.0590 & 1.45-27.93           & 76.05      & 0.9594       \\ \cline{2-9} 
                    & \psocake{} & 0.2732  & 0.9368 & 0.9835 & 2.0277 & 1.01-31.32           & 72.20      & 0.9367       \\ \hline
                    &         &         &           &           &          &                      &            &              \\ \hline
Sample              & Methods & R-split & CC$_{1/2}$     & CC*       & $I/\sigma(I)$   & Resolution range (Å) & Redundancy & Completeness \\ \hline
\multirow{2}{*}{PK} & \peaknet{} & 0.7711  & 0.2234    & 0.6043    & 1.135    & 1.45-26.98           & 16.36      & 0.8668       \\ \cline{2-9} 
                    & \psocake{} & 0.7589  & 0.1900    & 0.5650    & 0.974    & 1.45-30.04           & 17.83      & 0.8365       \\ \hline
\end{tabular}
}
\end{table*}

\subsection{Auto-masking: predicting artifact scattering patterns}

The integration of the ``auto-masking" functionality in \peaknet{} represents a
notable advancement in the automated processing of diffraction images.  The
underlying neural network architecture enables \peaknet{} to autonomously
discern and segregate pixel regions affected by artifact scattering, such as
these appearing as distinct ring-like structures induced by liquid jet nozzle
scattering.  This capability circumvents the need for manual masking in the peak
finding process, thereby optimizing the efficiency of crystallographic data
processing.

Fig. \ref{fig : automask 1} provides a comparative visualization of \peaknet{}'s
effectiveness in accurately segmenting regions with bright pixels induced by
artifact scattering under various conditions.  Images without artifact ring
structures are also included in the visualization, reassuring that \peaknet{}
does not generate or ``hallucinate" artifact rings where they do not exist.  This
visual representation serves as tangible evidence of \peaknet{} 's adeptness in
discriminating and processing pertinent features, regardless of the contextual
complexities.

Furthermore, while evaluating \peaknet{}'s ``auto-masking" feature on intended
input images, we explored its behavior on unintended inputs, providing insights
into its robustness and generalizability.  Fig. \ref{fig : automask 2} depicts
illustrative examples of \peaknet{} predicting artifact scattering patterns in
Ag Behenate scattering captured on various detectors.  Surprisingly, \peaknet{}
reliably identifies the characteristic scattering ring structures present in Ag
Behenate images.  This observation provides compelling evidence once again,
further demonstrating the robust predictive capability of \peaknet{} in
accurately recognizing artifact scattering patterns.  As a result, it reinforces
that effectiveness of \peaknet{}'s ``auto-masking" feature.

\begin{figure*}[!ht]
\includegraphics[width=\textwidth,keepaspectratio]
{./figures/automask.pdf} 
\caption{Examples of auto-masking using \peaknet{}.  Each panel contains three
images: the original image, the segmentation map used for masking, and the
resulting mask after thresholding.  Panels (a), (c) and (e) show three different
scenarios with artifact scattering rings.  Panels (b), (d) and (f) visualize the
response of \peaknet{} on images without any artifact scattering rings.}
\label{fig : automask 1} 
\end{figure*}

\begin{figure*}[!ht]
\centering
\includegraphics[width=\textwidth,keepaspectratio]
{./figures/automask.agbehnate.pdf}
\caption{Examples of identifying scattering rings in Ag Behenate images using
\peaknet{}.}
\label{fig : automask 2}
\end{figure*}

\subsection{Runtime efficiency}

Peak finding can pose significant computational demands, particularly in high
data rate experiments, highlighting the critical importance of an efficient peak
finding algorithm.  A comparative analysis of runtime performance demonstrates
the greater efficiency of \peaknet{} compared to other commonly used peak
finders like the one within \psocake{}.

When processing Rayonix images with a resolution of $1920 \times 1920$,
\peaknet{} achieved a significantly reduced processing time of 90 milliseconds
per event on an NVIDIA 1080 Ti GPU.  In contrast, \psocake{} required 176
milliseconds per event when executed on an Intel E5-2620.  Another peak finding
method, RPF (robust peak finder), operating on Intel E5-2698, is reported to
require 120.0 milliseconds but on smaller AGIPD 1M images with the size of $1024
\times 1024$ \citep{hadian-jaziDataReductionSerial2021}.  This result clearly
demonstrates that \peaknet{} not only delivers robust Bragg peak finding results
in an autonomous fashion, but also exhibits remarkable runtime efficiency.  This
establishes it as a highly competent tool for real-time autonomous Bragg peak
finding.

\begin{table}[t]
\caption{
    The runtime performance of diffraction image analysis algorithms measured on
    Rayonix images containing 3.7 megapixels.  We measured runtime performance
    of \psocake{} and \peaknet{} directly using Rayonix images.  For reference
    purposes, we also included another peak finding method RPF
    \citep{hadian-jaziPeakfindingAlgorithmBased2017,
    hadian-jaziDataReductionSerial2021} and two classification methods for X-ray
    diffraction data reduction. RPF runtime performance was originally measured
    on AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019}.  
}
\label{tb : runtime}
\centering
\resizebox{\columnwidth}{!}{
\begin{tabular}{llcc}
\hline
Methods             & Hardware       & Image size         & Time (ms/event) \\ \hline
\peaknet{}          & NVIDIA 1080 Ti & 1920 $\times$ 1920 & 90.0            \\ \hline
\psocake{}          & Intel E5-2620  & 1920 $\times$ 1920 & 175.5           \\ \hline
RPF                 & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
%CNN hit finder      & Hit Finding  & NVIDIA 1080 Ti & 720 $\times$ 720   & 0.8             \\ \hline
%ORB+MLP             & Hit Finding  & Intel Core i5  & 720 $\times$ 720   & 50.0            \\ \hline
\end{tabular}
}
\end{table}

\section{Conclusions}

\peaknet{} exhibits exceptional capabilities in autonomous detection of Bragg
peaks in diffraction images without requiring user input or intervention, such
as algorithmic parameter tuning or manual artifact scattering masking.  The
predictive performance of \peaknet{} in peak finding proves to be comparable to,
if not better than, manually fine-tuned \psocake{} with user-supplied masks.  An
integral feature of \peaknet{}, auto-masking, significantly enhances its ability
to autonomously identify and process artifact scattering patterns.  Moreover,
the efficiency of \peaknet{} is exemplified by its impressive runtime
performance, surpassesing commonly used peak finders like \psocake{} and RPF.
Parallel processing with GPU streaming can potentially improve the runtime
efficiency even further.  In conclusion, \peaknet{}  offers a robust, versatile,
and efficient solution that operates independently of user input, thereby
holding significant potential for optimizing crystallographic data processing at
high data rates.

% Bibliography
\bibliographystyle{plainnat}
\bibliography{bibliography}

\end{document}

### 2023-06-16 ieee_main.tex
Updates from Overleaf

@@
 
-\title{\peaknet{}: Bragg peak finding in X-ray crystallography experiments with
-U-Net}
+\title{\peaknet{}: Bragg peak finding in X-ray crystallography experiments with a U-Net}
 
@@
 While this development offers potential to enable novel scientific
-investigations, such as imaging molecular events at logarithmic timescales, it also poses
-challenges in regards to real-time data analysis, which involves some
-degree of data reduction to only save those features or images pertaining to the science on
-disks.  If data reduction is not effective, it could directly result in a
-substantial increase in facility budgetary requirements, or even hinder the
-utilization of ultra-high repetition imaging techniques making data analysis unwieldy.  Furthermore, an
-additional challenge involves providing real-time feedback to users derived from
-real-time data analysis.  In the context of serial crystallography, the
-initial and critical step in real-time data analysis is finding X-ray Bragg
-peaks from diffraction images.  To tackle this challenge, we present \peaknet{},
-a Bragg peak finder that utilizes neural networks and runs about four times
-faster than \psocake{} peak finder, while delivering significantly better
-indexing rates and comparable number of indexed events.  We formulated the task
-of peak finding into a semantic segmentation problem, which is implemented as a classical U-Net architecture.  A key advantage of \peaknet{} is its
-ability to scale linearly with respect to data volume, making it well-suited for
-real-time serial crystallography data analysis at high data rates.
+investigations, such as imaging molecular events at logarithmic timescales, it
+also poses challenges in regards to real-time data analysis, which involves some
+degree of data reduction to only save those features or images pertaining to the
+science on disks.  If data reduction is not effective, it could directly result
+in a substantial increase in facility budgetary requirements, or even hinder the
+utilization of ultra-high repetition imaging techniques making data analysis
+unwieldy.  Furthermore, an additional challenge involves providing real-time
+feedback to users derived from real-time data analysis.  In the context of
+serial crystallography, the initial and critical step in real-time data analysis
+is finding X-ray Bragg peaks from diffraction images.  To tackle this challenge,
+we present \peaknet{}, a Bragg peak finder that utilizes neural networks and
+runs about four times faster than \psocake{} peak finder, while delivering
+significantly better indexing rates and comparable number of indexed events.  We
+formulated the task of peak finding into a semantic segmentation problem, which
+is implemented as a classical U-Net architecture.  A key advantage of \peaknet{}
+is its ability to scale linearly with respect to data volume, making it
+well-suited for real-time serial crystallography data analysis at high data
+rates.
 \end{abstract}
@@
 
-Serial femtosecond crystallography (SFX) with X-ray free electron lasers (XFEL) has enabled structural determination of macromolecules by outrunning radiation
+Serial femtosecond crystallography (SFX) with X-ray free electron lasers (XFEL)
+has enabled structural determination of macromolecules by outrunning radiation
 damage at room temperature, an approach commonly known as
@@
 chapmanFemtosecondDiffractiveImaging2006,chapmanFemtosecondXrayProtein2011}.
-Time-resolved serial femtosecond crystallography (TR-SFX) at XFEL facilities, like the Linac Coherent
-Light Source (LCLS), allows the investigation of biochemical reactions with
-picosecond time resolution which has led to many significant
-structural studies \citep{kupitzSerialTimeresolvedCrystallography2014,
+Time-resolved serial femtosecond crystallography (TR-SFX) at XFEL facilities,
+like the Linac Coherent Light Source (LCLS), allows the investigation of
+biochemical reactions with picosecond time resolution which has led to many
+significant structural studies
+\citep{kupitzSerialTimeresolvedCrystallography2014,
 nangoThreedimensionalMovieStructural2016,pandeFemtosecondStructuralDynamics2016a,
@@
 tackle two major challenges that arise in SFX experiments, namely data reduction
-and real time feedback.  Firstly, data reduction aims to veto, extract and compress scientific data by identifying important events, commonly
-referred to as ``hits", and vetoing irrelevant ones from terabyte per second data streams.  One typical approach for SFX hit finding utilizes existing Bragg
-peak finders, such as the Cheetah peak finder
-\citep{bartyCheetahSoftwareHighthroughput2014}, the robust peak finder
-\citep{hadian-jaziPeakfindingAlgorithmBased2017}, DIALS peak finder \citep{Winter2018} or the \psocake{} peak finder
-\citep{shinDataAnalysisUsing2018}.  Additionally, a neural network-based SFX
-hit finder was reported to achieved a processing rate of 1.3 kHz on a single GPU
-\citep{keConvolutionalNeuralNetworkbased2018}.
-ORB feature extractor combined with a multilayer perceptron (MLP) hit classifier showed promising results for SFX data \citep{rahmaniDataReductionXray2023}.
-Secondly, real-time feedback in
+and real time feedback.  Firstly, data reduction aims to veto, extract and
+compress scientific data by identifying important events, commonly referred to
+as ``hits", and vetoing irrelevant ones from terabyte per second data streams.
+One typical approach for SFX hit finding utilizes existing Bragg peak finders,
+such as the Cheetah peak finder \citep{bartyCheetahSoftwareHighthroughput2014},
+the robust peak finder \citep{hadian-jaziPeakfindingAlgorithmBased2017}, DIALS
+peak finder \citep{Winter2018} or the \psocake{} peak finder
+\citep{shinDataAnalysisUsing2018}.  Additionally, a neural network-based SFX hit
+finder was reported to achieved a processing rate of 1.3 kHz on a single GPU
+\citep{keConvolutionalNeuralNetworkbased2018}. ORB feature extractor combined
+with a multilayer perceptron (MLP) hit classifier showed promising results for
+SFX data \citep{rahmaniDataReductionXray2023}.  Secondly, real-time feedback in
 SFX experiments provides users with information on the experimental conditions
@@
 networks.  To accomplish this goal, we propose to train a neural network model
-to classify each individual pixel as either belonging to a peak or not belonging to a peak.
-This is followed by converting a connected area of pixels as a single peak, a
-task that can be readily accomplished through connected component analysis
-\citep{weaverCentrosymmetricCrossSymmetricMatrices1985}.  Subsequently, the peak
-coordinates will be determined by computing the center of mass of all the pixels
-that belong to the identified peak.  It is worth noting that the entire peak
-finding process takes place on GPUs, offering a fully parallelizable approach for
-achieving scalability.  Concretely, our contributions can be summarized as
-follows:
+to classify each individual pixel as either belonging to a peak or not belonging
+to a peak.  This is followed by converting a connected area of pixels as a
+single peak, a task that can be readily accomplished through connected component
+analysis \citep{weaverCentrosymmetricCrossSymmetricMatrices1985}.  Subsequently,
+the peak coordinates will be determined by computing the center of mass of all
+the pixels that belong to the identified peak.  It is worth noting that the
+entire peak finding process takes place on GPUs, offering a fully parallelizable
+approach for achieving scalability.  Concretely, our contributions can be
+summarized as follows:
 
@@
     thousands of Bragg peaks with various peak profiles in detector images of
-    any dimension.  Despite being trained on peaks labeled by an existing peak finder,
-    we highlight that \peaknet{}'s capability is not limited by the peak finder
-    used in labeling.
+    any dimension.  Despite being trained on peaks labeled by an existing peak
+    finder, we highlight that \peaknet{}'s capability is not limited by the peak
+    finder used in labeling.
 
@@
     \peaknet{} to strike an optimal balance between model efficacy and runtime
-    performance, leading to a four times out-of-the-box processing speed improvement over \psocake{} peak finder.
+    performance, leading to a four times out-of-the-box processing speed
+    improvement over \psocake{} peak finder.
 
@@
 libraries of peak shapes, but this method was found to be slow and inefficient
-during runtime, especially when dealing with peaks with low signal-to-noise ratios
-(SNR).  The main obstacle lies in the localization of peaks and the tuning of
-user parameters for pattern matching, compounded by the difficult task of
-developing a comprehensive library of peak shapes.  Another influential approach
-employed region-growing techniques
+during runtime, especially when dealing with peaks with low signal-to-noise
+ratios (SNR).  The main obstacle lies in the localization of peaks and the
+tuning of user parameters for pattern matching, compounded by the difficult task
+of developing a comprehensive library of peak shapes.  Another influential
+approach employed region-growing techniques
 \citep{bolotovskySeedSkewnessMethodIntegration1995,
@@
 pixels and actual peaks.  Furthermore, the RPF method can also parallelize the
-processing of diffraction patterns, making it suitable for real-time data analysis.
+processing of diffraction patterns, making it suitable for real-time data
+analysis.
 
@@
 the peak position.  To the best of our knowledge, no existing neural network
-based peak-finding models have demonstrated the ability to detect multiple peaks with high precision without manual tuning of peak finding parameters,
-which is the primary goal we strive to achieve with \peaknet{}.
+based peak-finding models have demonstrated the ability to detect multiple peaks
+with high precision without manual tuning of peak finding parameters, which is
+the primary goal we strive to achieve with \peaknet{}.
 
@@
 like BraggNet, which operates on a much smaller area of $32 \times 32$, whereas
-\peaknet{} is trained on larger multi-panel detectors, such as the
-Cornell-SLAC pixel array detector (CSPAD) \citep{hartCornellSLACPixelArray2012}
-with a dimension of $194 \times 185$ for one of its panels.  Focal loss was
-introduced to address the extreme class imbalance problem for object detectors
+\peaknet{} is trained on larger multi-panel detectors, such as the Cornell-SLAC
+pixel array detector (CSPAD) \citep{hartCornellSLACPixelArray2012} with a
+dimension of $194 \times 185$ for one of its panels.  Focal loss was introduced
+to address the extreme class imbalance problem for object detectors
 \citep{linFocalLossDense2018}.  It is defined as:
@@
 
-Here, $p$ is the probabilities of a
-pixel $x$ being a peak.  $\gamma$ controls a modulating factor
-$(1-p)$ and $\alpha$ is an additional modulating factor.  We used $\gamma = 2.0$ and $\alpha = 1.2$ in \peaknet{}.  In
-practice, numerical instability will often emerge in the calculation of
-$p = e^{-\text{logit}}$, where $\text{logit} = \log{(1 + e^{-x})}$.  To bypass this issue,
-logit needs to be rewritten as $\text{logit} = a + \log{(e^{-a} + e^{-x-a})}$,
-where $a = max(0, -x)$.  As a result, if we denote the label of a pixel $x$ as $y$, the focal loss becomes
+Here, $p$ is the probabilities of a pixel $x$ being a peak.  $\gamma$ controls a
+modulating factor $(1-p)$ and $\alpha$ is an additional modulating factor.  We
+used $\gamma = 2.0$ and $\alpha = 1.2$ in \peaknet{}.  In practice, numerical
+instability will often emerge in the calculation of $p = e^{-\text{logit}}$,
+where $\text{logit} = \log{(1 + e^{-x})}$.  To bypass this issue, logit needs to
+be rewritten as $\text{logit} = a + \log{(e^{-a} + e^{-x-a})}$, where $a = max(0,
+-x)$.  As a result, if we denote the label of a pixel $x$ as $y$, the focal loss
+becomes
 
 \begin{equation}
-    \text{FL}(p) = \alpha \cdot y \cdot (1-p)^\gamma + \text{logit} + (1 - y) \cdot p^\gamma \cdot x + p^\gamma \cdot (1 - y) \cdot \text{logit}
+    \text{FL}(p) = \alpha \cdot y \cdot (1-p)^\gamma + \text{logit} + (1 - y)
+    \cdot p^\gamma \cdot x + p^\gamma \cdot (1 - y) \cdot \text{logit}
 \end{equation}
@@
 which is widely used in serial crystallography experiments at LCLS.
-Specifically, we used crystallographic data of streptavidin crystals from LCLS experiment
-\textit{cxic0415} run \textit{101} at the Coherent X-ray Imaging (CXI)
+Specifically, we used crystallographic data of streptavidin crystals from LCLS
+experiment \textit{cxic0415} run \textit{101} at the Coherent X-ray Imaging (CXI)
 instrument, where the CSPAD deployed consists of 32 panels.  An individual
@@
 peak finder. This works well when diffraction spots have consistent sizes.
-However, detectors such as the Rayonix have a large point spread function for intense peaks, which may
-result in large peaks being ignored by the \psocake{} peak finder.  Consequently,
-there is a concern about whether \peaknet{} will inherit the same limitations
-since it is trained on \psocake{} peak labels.
+However, detectors such as the Rayonix have a large point spread function for
+intense peaks, which may result in large peaks being ignored by the \psocake{}
+peak finder.  Consequently, there is a concern about whether \peaknet{} will
+inherit the same limitations since it is trained on \psocake{} peak labels.
 
@@
 a Rayonix image, with the \peaknet{} results displayed on the left and the
-\psocake{} results on the right.
-The diffraction data were collected from crystals of SARS-CoV-2 proteases using the Macromolecular Femtosecond Crystallography (MFX) instrument \citep{sierraMacromolecularFemtosecondCrystallography2019} at LCLS.
-Upon visual inspection of Fig.
-\ref{fig :
-rayonix} (c) and (d), both \peaknet{} and \psocake{} were observed to detect a
-considerable number of peaks, suggesting a potentially comparable performance
-between the two methods.  However, upon closer inspection of the view near the
-area slightly below the beamstop position, one obvious, reasonably sized Bragg
-peak was observed but not detected by the \psocake{} peak finder, whereas
-\peaknet{} successfully located this peak.  This finding provides direct
-evidence that \peaknet{}'s peak finding capability is not strictly limited by
-the peak finder used in the data labeling process.  In fact, \peaknet{} appears
-to possess its own understanding of Bragg peaks, as evidenced by the exclusion
-of a weak single Bragg peak-like spot near the upper edge of the image, as shown
-in Fig. \ref{fig : rayonix} (a) and (b).  Therefore, it is important to note that
-\peaknet{} is not merely a neural network-based replica of the \psocake{} peak finder
-despite being trained on labels supplied by it.
+\psocake{} results on the right.  The diffraction data were collected from
+crystals of SARS-CoV-2 proteases using the Macromolecular Femtosecond
+Crystallography (MFX) instrument
+\citep{sierraMacromolecularFemtosecondCrystallography2019} at LCLS.  Upon visual
+inspection of Fig. \ref{fig : rayonix} (c) and (d), both \peaknet{} and
+\psocake{} were observed to detect a considerable number of peaks, suggesting a
+potentially comparable performance between the two methods.  However, upon
+closer inspection of the view near the area slightly below the beamstop position,
+one obvious, reasonably sized Bragg peak was observed but not detected by the
+\psocake{} peak finder, whereas \peaknet{} successfully located this peak.  This
+finding provides direct evidence that \peaknet{}'s peak finding capability is
+not strictly limited by the peak finder used in the data labeling process.  In
+fact, \peaknet{} appears to possess its own understanding of Bragg peaks, as
+evidenced by the exclusion of a weak single Bragg peak-like spot near the upper
+edge of the image, as shown in Fig. \ref{fig : rayonix} (a) and (b).  Therefore,
+it is important to note that \peaknet{} is not merely a neural network-based
+replica of the \psocake{} peak finder despite being trained on labels supplied
+by it.
 
@@
 events in the CXI dataset and 465 in the MFX dataset, yielding indexing rates of
-71.2\% and 84.5\%, respectively.  In contrast, \peaknet{} discovered 1991
-events in the CXI dataset and 430 in the MFX dataset, exhibiting superior
-indexing rates of 78.6\% and 90.2\%, respectively.  Although both peak finders
-exhibit varying levels of effectiveness, our evaluation has revealed that
-\peaknet{} achieves superior indexing rates across both datasets,
-while also yielding comparable numbers of indexed events.  These results suggest
-that \peaknet{} may represent a more reliable and efficient solution for the
-analysis of such data.
+71.2\% and 84.5\%, respectively.  In contrast, \peaknet{} discovered 1991 events
+in the CXI dataset and 430 in the MFX dataset, exhibiting superior indexing
+rates of 78.6\% and 90.2\%, respectively.  Although both peak finders exhibit
+varying levels of effectiveness, our evaluation has revealed that \peaknet{}
+achieves superior indexing rates across both datasets, while also yielding
+comparable numbers of indexed events.  These results suggest that \peaknet{} may
+represent a more reliable and efficient solution for the analysis of such data.
 
@@
 alternative measures of model performance and reliability, such as the indexing
-rate and the number of indexed events.  However, 
-conventional metrics may remain a viable option when applied to synthetic data
-generated by a simulator.
-For clarification purposes, we used the \textit{indexamajig} tool within the \textit{CrystFEL} data analysis software \citep{whiteCrystFELSoftwareSuite2012} to perform indexing.
-We employed multiple indexing methods, including \textit{mosflm}, \textit{xds} and \textit{xgandalf}, with an additional setting of \textit{-int-radius=4,5,6}.
+rate and the number of indexed events.  However, conventional metrics may remain
+a viable option when applied to synthetic data generated by a simulator.   For
+clarification purposes, we used the \textit{indexamajig} tool within the
+\textit{CrystFEL} data analysis software \citep{whiteCrystFELSoftwareSuite2012}
+to perform indexing.  We employed multiple indexing methods, including
+\textit{mosflm}, \textit{xds} and \textit{xgandalf}, with an additional setting
+of \textit{-int-radius=4,5,6}.
 
@@
 runtime}, there is a caveat to consider.  Although \peaknet{} is designed as a
-nearly end-to-end solution, with its neural networks returning a segmentation map
-that represents the pixel-wise probability of being a peak from input
+nearly end-to-end solution, with its neural networks returning a segmentation
+map that represents the pixel-wise probability of being a peak from input
 diffraction images, we must employ connected component analysis to convert the
@@
 
-Earlier versions of the U-Net
-models were built and tested by P.L under the supervision of C.H.Y.  The experiments were
-designed by C.W with inputs from J.B.T and C.H.Y.  C.W prepared the datasets, labeled
-experimental data, and trained and evaluated the refined neural network model.
-The manuscript was written by C.W and C.H.Y with input from all authors.  This
-material is based upon work supported by the U.S.  Department of Energy, Office
-of Science, Office of Basic Energy Sciences under Award Number FWP-100643.  Use
-of the Linac Coherent Light Source (LCLS), SLAC National Accelerator Laboratory,
-is supported by the U.S. Department of Energy, Office of Science, Office of
-Basic Energy Sciences under Contract No.  DE-AC02-76SF00515.
+Earlier versions of the U-Net models were built and tested by P.L under the
+supervision of C.H.Y.  The experiments were designed by C.W with inputs from
+J.B.T and C.H.Y.  C.W prepared the datasets, labeled experimental data, and
+trained and evaluated the refined neural network model.  The manuscript was
+written by C.W and C.H.Y with input from all authors.  This material is based
+upon work supported by the U.S.  Department of Energy, Office of Science, Office
+of Basic Energy Sciences under Award Number FWP-100643.  Use of the Linac
+Coherent Light Source (LCLS), SLAC National Accelerator Laboratory, is supported
+by the U.S. Department of Energy, Office of Science, Office of Basic Energy
+Sciences under Contract No.  DE-AC02-76SF00515.
 

### 2023-06-16 manuscript.tex
Add more discussion on alpha in focal loss.

@@
 extent to which the weight of well-classified examples, such as background
-pixels, is reduced.  In our neural network training, we chose $\alpha = 1.2$
-across all examples and $\gamma = 2.0$.  Essentially, this means $(1-\hat{p}
-_j^{(i)}) ^\gamma$ is solely responsible for down-weighting easy examples, as
-$\hat{p} _j^{(i)}$ is usually large in this case.
+pixels, is reduced.  In our neural network training, we chose $\gamma = 2.0$,
+essentially, this means $(1-\hat{p} _j^{(i)}) ^\gamma$ is solely responsible for
+down-weighting easy examples, as $\hat{p} _j^{(i)}$ is usually large in this
+case.  Finding the ideal values for $\alpha$ can be a delicate process with only
+marginal returns, as highlighted in the original focal loss study
+\citep{linFocalLossDense2018}.  In order to fully utilize focal loss, we decided
+to use a fixed trivial value of $\alpha = 1.2$ for all examples, primarily for
+the sake of completeness.  This choice essentially treats $\alpha$ as a simple
+scaling factor without significant impact.  It is worth noting that in most
+cases, the sum of all $\alpha_j$ values, denoted as $\sum_{j = 1}^{C} \alpha_j$,
+is expected to equal 1.
 

### 2023-06-16 manuscript.tex
Modify manuscript.

@@
 
-\peaknet{} exhibits exceptional capabilities in autonomous detection of Bragg
-peaks in diffraction images without requiring user input or intervention, such
-as algorithmic parameter tuning or manual artifact scattering masking.  The
-predictive performance of \peaknet{} in peak finding proves to be comparable to,
-if not better than, manually fine-tuned \psocake{} with user-supplied masks.  An
-integral feature of \peaknet{}, auto-masking, significantly enhances its ability
-to autonomously identify and process artifact scattering patterns.  Moreover,
-the efficiency of \peaknet{} is exemplified by its impressive runtime
-performance, surpassesing commonly used peak finders like \psocake{} and RPF.
-Parallel processing with GPU streaming can potentially improve the runtime
-efficiency even further.  In conclusion, \peaknet{}  offers a robust, versatile,
-and efficient solution that operates independently of user input, thereby
-holding significant potential for optimizing crystallographic data processing at
-high data rates.
+\peaknet{} exhibits exceptional capabilities in autonomous Bragg peaks finding
+without requiring user input or intervention, such as algorithmic parameter
+tuning or manual artifact scattering masking.  The predictive performance of
+\peaknet{} in peak finding proves to be comparable to, if not better than,
+manually fine-tuned \psocake{} with user-supplied masks.  An integral feature of
+\peaknet{}, auto-masking, significantly enhances its ability to autonomously
+identify and process artifact scattering patterns.  Moreover, the efficiency of
+\peaknet{} is exemplified by its impressive runtime performance, surpassesing
+commonly used peak finders like \psocake{} and RPF.  Parallel processing with
+GPU streaming can potentially improve the runtime efficiency even further.  In
+conclusion, \peaknet{}  offers a robust, versatile, and efficient solution that
+operates independently of user input, thereby holding significant potential for
+optimizing crystallographic data processing at high data rates.
 

### 2023-06-16 manuscript.tex
Make paragraph in one line.

--- 2023-06-16 manuscript.tex
@@
 
-Serial crystallography at X-ray free electron laser (XFEL) sources has
-experienced tremendous progresses in achieving high data rate in recent times,
-offering potential to enable novel scientific investigations, such as imaging
-faster molecular events.  However, this approach also generates a significant
-amount volume of data with sparsely distributed scientific signals, posing
-challenges in data reduction and real-time feedback.  To address these concerns,
-a rapid and efficient Bragg peak finding process serves as the pivotal initial
-step, effectively addressing both data storage concerns and real-time feedback
-requirements simultaneously.  Here, we present \peaknet{}, a autonomous Bragg
-peak finder that utilizes deep neural networks, eliminating the need for manual
-parameter tuning common in conventional peak finders and the laborious task of
-manually masking pixels affected by artifact scattering, such as nozzle
-scattering rings.  \peaknet{} also exhibits exceptional runtime efficiency,
-processing a $1920 \times 1920$ image around 90 ms on an NVIDIA 1080 Ti GPU,
-with the potential for further enhancements through parallelized analysis or GPU
-stream processing.  With its ability to scale linearly with respect to data
-volume, \peaknet{} is well-suited for real-time serial crystallography data
-analysis at high data rates.
+Serial crystallography at X-ray free electron laser (XFEL) sources has experienced tremendous progresses in achieving high data rate in recent times, offering potential to enable novel scientific investigations, such as imaging faster molecular events.
+However, this approach also generates a significant amount volume of data with sparsely distributed scientific signals, posing challenges in data reduction and real-time feedback.
+To address these concerns, a rapid and efficient Bragg peak finding process serves as the pivotal initial step, effectively addressing both data storage concerns and real-time feedback requirements simultaneously.
+Here, we present \peaknet{}, a autonomous Bragg peak finder that utilizes deep neural networks, eliminating the need for manual parameter tuning common in conventional peak finders and the laborious task of manually masking pixels affected by artifact scattering, such as nozzle scattering rings.
+\peaknet{} also exhibits exceptional runtime efficiency, processing a $1920 \times 1920$ image around 90 ms on an NVIDIA 1080 Ti GPU, with the potential for further enhancements through parallelized analysis or GPU stream processing.
+With its ability to scale linearly with respect to data volume, \peaknet{} is well-suited for real-time serial crystallography data analysis at high data rates.
 
@@
 
-Serial crystallography with X-ray free electron lasers (XFEL) has enabled the
-structural determination of three-dimensional macromolecules from radiation
-damage-free samples at room temperature, an approach commonly known as
-\textit{diffraction-before-destruction}
-\citep{neutzePotentialBiomolecularImaging2000,
-chapmanFemtosecondDiffractiveImaging2006,chapmanFemtosecondXrayProtein2011}.
-Time-resolved serial crystallography at XFEL facilities, like the Linac Coherent
-Light Source (LCLS), allows the investigation of biochemical reactions with
-femtosecond-scale time resolutions.  This technique is typically referred to as
-serial femtosecond crystallography (SFX), which has led to many signficiant
-structural studies \citep{kupitzSerialTimeresolvedCrystallography2014,
-nangoThreedimensionalMovieStructural2016,pandeFemtosecondStructuralDynamics2016a,
-youngStructurePhotosystemII2016,sugaLightinducedStructuralChanges2017,
-kernStructuresIntermediatesKok2018,ibrahimUntanglingSequenceEvents2020,
-sugaTimeresolvedStudiesMetalloproteins2020} since the first published work at
-LCLS \citep{aquilaTimeresolvedProteinNanocrystallography2012}.  In the meantime,
-the data rate at XFEL facilities have also gradually increased from hundreds of
-Hz to the MHz range, with the European X-ray Free Electron Laser (EuXFEL) being
-the first MHz facility available to users and LCLS-II set to launch in 2023.
+Serial crystallography with X-ray free electron lasers (XFEL) has enabled the structural determination of three-dimensional macromolecules from radiation damage-free samples at room temperature, an approach commonly known as \textit{diffraction-before-destruction} \citep{neutzePotentialBiomolecularImaging2000, chapmanFemtosecondDiffractiveImaging2006,chapmanFemtosecondXrayProtein2011}.
+Time-resolved serial crystallography at XFEL facilities, like the Linac Coherent Light Source (LCLS), allows the investigation of biochemical reactions with femtosecond-scale time resolutions.
+This technique is typically referred to as serial femtosecond crystallography (SFX), which has led to many signficiant structural studies \citep{kupitzSerialTimeresolvedCrystallography2014, nangoThreedimensionalMovieStructural2016,pandeFemtosecondStructuralDynamics2016a, youngStructurePhotosystemII2016,sugaLightinducedStructuralChanges2017, kernStructuresIntermediatesKok2018,ibrahimUntanglingSequenceEvents2020, sugaTimeresolvedStudiesMetalloproteins2020} since the first published work at LCLS \citep{aquilaTimeresolvedProteinNanocrystallography2012}.
+In the meantime, the data rate at XFEL facilities have also gradually increased from hundreds of Hz to the MHz range, with the European X-ray Free Electron Laser (EuXFEL) being the first MHz facility available to users and LCLS-II set to launch in 2023.
 
-At the MHz data rate, novel real-time data analysis approaches are needed to
-tackle two major challenges that arise in SFX experiments, namely data reduction
-and real time feedback.  One common approach for finding hits in serial
-crystallography data is to utilize existing Bragg peak finders like the Cheetah
-peak finder \citep{bartyCheetahSoftwareHighthroughput2014}, the Robust Peak
-Finder (RPF) \citep{hadian-jaziPeakfindingAlgorithmBased2017}, or the \psocake{}
-\citep{yoonPsocakeGUIMaking2020} peak finder.  Additionally, a deep neural
-network-based hit finder for serial crystallography has been reported to achieve
-a processing rate of 1.3 kHz by analyzing downsized 180 $\times$ 180 images
-using a single GPU \citep{keConvolutionalNeuralNetworkbased2018}.  Secondly,
-real-time feedback in serial crystallography experiments plays a crucial role by
-providing users with important information about the experimental conditions.
-This enables them to make timely decisions that optimize the data acquisition
-process. For instance, it is essential to fine-tune the hit rate to maximize the
-utilization of samples. Additionally, it is important to monitor factors such as
-the current diffraction limit, crystalline mosaicity, reciprocal space coverage,
-and other relevant parameters over time. Therefore, relying solely on hit
-finding is insufficient to gain the necessary insights, making real-time Bragg
-peak finding vital for delivering prompt and comprehensive feedback. However,
-the peak finder mentioned earlier in \psocake{} operates at a rate of
-approximately 5 Hz on a data center CPU, which could lead to significant costs
-when scaling up the process.
+At the MHz data rate, novel real-time data analysis approaches are needed to tackle two major challenges that arise in SFX experiments, namely data reduction and real time feedback.
+One common approach for finding hits in serial crystallography data is to utilize existing Bragg peak finders like the Cheetah peak finder \citep{bartyCheetahSoftwareHighthroughput2014}, the Robust Peak Finder (RPF) \citep{hadian-jaziPeakfindingAlgorithmBased2017}, or the \psocake{} \citep{yoonPsocakeGUIMaking2020} peak finder.
+Additionally, a deep neural network-based hit finder for serial crystallography has been reported to achieve a processing rate of 1.3 kHz by analyzing downsized 180 $\times$ 180 images using a single GPU \citep{keConvolutionalNeuralNetworkbased2018}.
+Secondly, real-time feedback in serial crystallography experiments plays a crucial role by providing users with important information about the experimental conditions.
+This enables them to make timely decisions that optimize the data acquisition process.
+For instance, it is essential to fine-tune the hit rate to maximize the utilization of samples.
+Additionally, it is important to monitor factors such as the current diffraction limit, crystalline mosaicity, reciprocal space coverage, and other relevant parameters over time.
+Therefore, relying solely on hit finding is insufficient to gain the necessary insights, making real-time Bragg peak finding vital for delivering prompt and comprehensive feedback.
+However, the peak finder mentioned earlier in \psocake{} operates at a rate of approximately 5 Hz on a data center CPU, which could lead to significant costs when scaling up the process.
 
-In this work, we introduce \peaknet{}, a solution that effectively addresses the
-challenge of autonomously and efficiently identifying Bragg peaks in high data
-rate scenarios.  Our approach involves transforming the peak finding problem into
-semantic segmentation tasks, where different regions within diffraction images
-are classified and segmented using deep learning networks.  By leveraging this
-process, \peaknet{} autonomously detects Bragg peaks while effectively
-identifying strong artifact scattering, eliminating the need for human
-intervention.  Subsequently, connected areas of pixels are examined and treated
-as individual peaks, a task easily accomplished through connected component
-analysis \citep{weaverCentrosymmetricCrossSymmetricMatrices1985}.  The
-coordinates of the peaks are determined by calculating the center of mass of all
-pixels belonging to each identified peak.  Notably, the entire peak finding
-process is performed on GPUs, offering a cost-effective solution for achieving
-scalability.
+In this work, we introduce \peaknet{}, a solution that effectively addresses the challenge of autonomously and efficiently identifying Bragg peaks in high data rate scenarios.
+Our approach involves transforming the peak finding problem into semantic segmentation tasks, where different regions within diffraction images are classified and segmented using deep learning networks.
+By leveraging this process, \peaknet{} autonomously detects Bragg peaks while effectively identifying strong artifact scattering, eliminating the need for human intervention.
+Subsequently, connected areas of pixels are examined and treated as individual peaks, a task easily accomplished through connected component analysis \citep{weaverCentrosymmetricCrossSymmetricMatrices1985}.
+The coordinates of the peaks are determined by calculating the center of mass of all pixels belonging to each identified peak.
+Notably, the entire peak finding process is performed on GPUs, offering a cost-effective solution for achieving scalability.
 
@@
 
-Reliable and automatic peak finding algorithms have undergone multiple
-iterations of development.  An early approach involved utilizing template
-matching \citep{wilkinsonIntegrationSinglecrystalReflections1988a} based on
-libraries of peak shapes, but this method was found to be slow and inefficient
-in runtime, especially when dealing with peaks with low signal-to-noise ratios
-(SNR).  The main obstacle lies in the localization of peaks and the tuning of
-user parameters for pattern matching, compounded by the difficult task of
-developing a comprehensive library of peak shapes.  Another influential approach
-employed region-growing techniques
-\citep{bolotovskySeedSkewnessMethodIntegration1995,
-bartyCheetahSoftwareHighthroughput2014} to detect pixel areas with high
-skewness.  In the context of serial crystallography with XFEL sources, the
-efficacy of this method was diminished due to the lack of sufficient data to
-provide reliable statistics, rendering it susceptible to outliers and less adept
-in analyzing weak peaks at higher scattering angles, which are essential for
-achieving atomic resolution in structure determination.
+Reliable and automatic peak finding algorithms have undergone multiple iterations of development.
+An early approach involved utilizing template matching \citep{wilkinsonIntegrationSinglecrystalReflections1988a} based on libraries of peak shapes, but this method was found to be slow and inefficient in runtime, especially when dealing with peaks with low signal-to-noise ratios (SNR).
+The main obstacle lies in the localization of peaks and the tuning of user parameters for pattern matching, compounded by the difficult task of developing a comprehensive library of peak shapes.
+Another influential approach employed region-growing techniques \citep{bolotovskySeedSkewnessMethodIntegration1995, bartyCheetahSoftwareHighthroughput2014} to detect pixel areas with high skewness.
+In the context of serial crystallography with XFEL sources, the efficacy of this method was diminished due to the lack of sufficient data to provide reliable statistics, rendering it susceptible to outliers and less adept in analyzing weak peaks at higher scattering angles, which are essential for achieving atomic resolution in structure determination.
 
-While template matching and region-growing tecnhiques require users to provide
-priori information like threshold values, Robust Peak Finder (RPF)
-\citep{hadian-jaziPeakfindingAlgorithmBased2017,
-hadian-jaziDataReductionSerial2021} has demonstrated proficient peak finding
-capabilities with minimal user inputs.  This techinuqe utilizes the Modified
-Selective Statistical Estimator (MSSE) method to segment between background
-pixels and actual peaks.  Furthermore, the RPF method can also parallelize the
-processing of diffraction patterns, making it ideal for real-time data analysis.
+While template matching and region-growing tecnhiques require users to provide priori information like threshold values, Robust Peak Finder (RPF) \citep{hadian-jaziPeakfindingAlgorithmBased2017, hadian-jaziDataReductionSerial2021} has demonstrated proficient peak finding capabilities with minimal user inputs.
+This techinuqe utilizes the Modified Selective Statistical Estimator (MSSE) method to segment between background pixels and actual peaks.
+Furthermore, the RPF method can also parallelize the processing of diffraction patterns, making it ideal for real-time data analysis.
 
-\psocake{} is a software specifically designed to streamline high throughput
-data reduction and analysis of XFEL experiments, and is routinely used at SLAC
-National Accelerator laborator (SLAC) and Pohang Accelerator Laboratory (PAL).
-The built-in peak-finding algorithm \citep{shinDataAnalysisUsing2018} includes
-calibrating raw analog digital units (ADUs); applying optional background
-correction and bad pixel masks; identifying possible peaks; calculating their
-SNR; determining Bragg spot sizes; and selecting peaks based on size, total
-intensity and SNR.
+\psocake{} is a software specifically designed to streamline high throughput data reduction and analysis of XFEL experiments, and is routinely used at SLAC National Accelerator laborator (SLAC) and Pohang Accelerator Laboratory (PAL).
+The built-in peak-finding algorithm \citep{shinDataAnalysisUsing2018} includes calibrating raw analog digital units (ADUs); applying optional background correction and bad pixel masks; identifying possible peaks; calculating their SNR; determining Bragg spot sizes; and selecting peaks based on size, total intensity and SNR.
 
-In recent years, neural network models have emerged as a promising avenue for
-Bragg peak finding.  BraggNet \citep{sullivanBraggNetIntegratingBragg2019} is
-the first method that demonstrates proficiency of neural network models,
-specifically U-Net \citep{ronnebergerUNetConvolutionalNetworks2015}, in
-accurately segmenting peak pixels, including weak peaks, from background pixels
-in neutron crystallography data.  Specifically, BraggNet employed simulated
-peaks to create training datasets, which underwent a number of preprocessing
-steps, including centering and cropping to a specfic size and adding Poisson
-noise.  It should be noted that BraggNet works on a single peak at a time within
-a small 32 by 32 window, which deviates significantly from conventional Bragg
-peak finding tasks that require extracting peak positions from images typically
-with hundreds or thousands of pixels along one dimension.  Furthermore, another
-neural network method for Bragg peak analysis was detailed in the work of
-BraggNN \citep{liuBraggNNFastXray2021}, emphasizing the refinement of Bragg peak
-positions without the need for explicit fitting of a profile function, such as
-the pseudo-Voigt profile.  Likewise, BraggNN works on a single peak at a time
-within a 11 by 11 window, performing regression to two variables representing
-the peak position.  To the best of our knowledge, no existing neural network
-based peak-finding models have demonstrated the ability to detect multiple peaks,
-which is the primary goal we strive to achieve with \peaknet{}.
+In recent years, neural network models have emerged as a promising avenue for Bragg peak finding.
+BraggNet \citep{sullivanBraggNetIntegratingBragg2019} is the first method that demonstrates proficiency of neural network models, specifically U-Net \citep{ronnebergerUNetConvolutionalNetworks2015}, in accurately segmenting peak pixels, including weak peaks, from background pixels in neutron crystallography data.
+Specifically, BraggNet employed simulated peaks to create training datasets, which underwent a number of preprocessing steps, including centering and cropping to a specfic size and adding Poisson noise.
+It should be noted that BraggNet works on a single peak at a time within a small 32 by 32 window, which deviates significantly from conventional Bragg peak finding tasks that require extracting peak positions from images typically with hundreds or thousands of pixels along one dimension.
+Furthermore, another neural network method for Bragg peak analysis was detailed in the work of BraggNN \citep{liuBraggNNFastXray2021}, emphasizing the refinement of Bragg peak positions without the need for explicit fitting of a profile function, such as the pseudo-Voigt profile.
+Likewise, BraggNN works on a single peak at a time within a 11 by 11 window, performing regression to two variables representing the peak position.
+To the best of our knowledge, no existing neural network based peak-finding models have demonstrated the ability to detect multiple peaks, which is the primary goal we strive to achieve with \peaknet{}.
 
@@
 
-The current peak finding process of \peaknet{} comprises two steps, as depicted
-in Fig. \ref{fig : peak finding}.  Firstly, a segmentation map is obtained from
-the input image using deep neural networks.  Subsequently, peak positions are
-determined based on the generated segmentation map using connected component
-analysis \citep{weaverCentrosymmetricCrossSymmetricMatrices1985}.  Importantly,
-\peaknet{} has the capability to process inputs with arbitrary image sizes in a
-batch manner, enabling efficient analysis.
+The current peak finding process of \peaknet{} comprises two steps, as depicted in Fig.
+\ref{fig : peak finding}.
+Firstly, a segmentation map is obtained from the input image using deep neural networks.
+Subsequently, peak positions are determined based on the generated segmentation map using connected component analysis \citep{weaverCentrosymmetricCrossSymmetricMatrices1985}.
+Importantly, \peaknet{} has the capability to process inputs with arbitrary image sizes in a batch manner, enabling efficient analysis.
 
-In this section, our focus is to provide a comprehensive understanding of the
-underlying deep neural network components in \peaknet{}.  We will specifically
-discuss the network architecture, data augmentation techniques, and the loss
-function employed during the training process.  Furthermore, we will emphasize
-the use of iterative data curation in addressing the outlier problem.
+In this section, our focus is to provide a comprehensive understanding of the underlying deep neural network components in \peaknet{}.
+We will specifically discuss the network architecture, data augmentation techniques, and the loss function employed during the training process.
+Furthermore, we will emphasize the use of iterative data curation in addressing the outlier problem.
 
@@
 
-The underlying neural network architecture of \peaknet{} is illustrated in
-Figure \ref{fig : network arc} (a).  It employs a residual attention U-Net
-architecture, comprising three main components: a feature extraction ``backbone",
-a feature fusion ``neck", and a single prediction ``head".  The feature
-extraction ``backbone" utilizes multiple residual double convolutional blocks to
-extract multi-resolution features, as visualized in Figure \ref{fig : network
-arc} (b).  In the feature fusion ``neck", low-resolution features are merged
-with high-resolution features using gated feature fusion blocks, as depicted in
-\ref{fig : network arc} (c).  Each block incorporates an attention gate that
-enhances shared features within both low and high-resolution feature maps.  The
-resulting combined features from each gated feature fusion block are then
-rearranged by a subsequent residual double convolutional block.  Finally, to
-accomplish the segmentation task, the prediction ``head" leverages fused
-features from the ``neck" and generates a prediction map encompassing three
-distinct labels: background, Bragg peak, and artifact scattering.  The ``head"
-itself consists of a 1 $\times$ 1 convolutional layer followed by a softmax
-function.
+The underlying neural network architecture of \peaknet{} is illustrated in Figure \ref{fig : network arc} (a).
+It employs a residual attention U-Net architecture, comprising three main components: a feature extraction ``backbone", a feature fusion ``neck", and a single prediction ``head".
+The feature extraction ``backbone" utilizes multiple residual double convolutional blocks to extract multi-resolution features, as visualized in Figure \ref{fig : network arc} (b).
+In the feature fusion ``neck", low-resolution features are merged with high-resolution features using gated feature fusion blocks, as depicted in \ref{fig : network arc} (c).
+Each block incorporates an attention gate that enhances shared features within both low and high-resolution feature maps.
+The resulting combined features from each gated feature fusion block are then rearranged by a subsequent residual double convolutional block.
+Finally, to accomplish the segmentation task, the prediction ``head" leverages fused features from the ``neck" and generates a prediction map encompassing three distinct labels: background, Bragg peak, and artifact scattering.
+The ``head" itself consists of a 1 $\times$ 1 convolutional layer followed by a softmax function.
 
-It is essential to acknowledge that our neural network architecture is primarily
-based on the original ``Attention U-Net" design
-\citep{oktayAttentionUNetLearning2018}.  However, we want to point out that the
-three-component design, consisting of the ``backbone", ``neck" and ``head",
-offers the flexibility to replace these components with different architectures.
-For instance, the ``backbone" can be substituted with RegNet
-\citep{radosavovicDesigningNetworkDesign2020}, while the ``neck" can be replaced
-with other multi-resolution feature fusion methods like feature pyramid networks
-(FPN) \citep{linFeaturePyramidNetworks2017} or bidirectional feature pyramid
-networks (BiFPN) \citep{tanEfficientDetScalableEfficient2020}.  Additionally,
-the ``head" can be extended to perform additional tasks, if desired, such as
-predicting the likelihood of the input image being indexable.  This modular
-approach provides flexibility and allows for customization based on specific
-requirements.
+It is essential to acknowledge that our neural network architecture is primarily based on the original ``Attention U-Net" design \citep{oktayAttentionUNetLearning2018}.
+However, we want to point out that the three-component design, consisting of the ``backbone", ``neck" and ``head", offers the flexibility to replace these components with different architectures.
+For instance, the ``backbone" can be substituted with RegNet \citep{radosavovicDesigningNetworkDesign2020}, while the ``neck" can be replaced with other multi-resolution feature fusion methods like feature pyramid networks (FPN) \citep{linFeaturePyramidNetworks2017} or bidirectional feature pyramid networks (BiFPN) \citep{tanEfficientDetScalableEfficient2020}.
+Additionally, the ``head" can be extended to perform additional tasks, if desired, such as predicting the likelihood of the input image being indexable.
+This modular approach provides flexibility and allows for customization based on specific requirements.
 
@@
 
-One main technical issue in training neural networks for Bragg peak segmentation
-is the extreme peak-background class imbalance (e.g., $> 10^3 : 1$), resulting
-in reduced prediction accuracy.  This may not pose as a problem in previous peak
-finders like BraggNet, which operates on a much smaller area of $32 \times 32$,
-whereas \peaknet{} is trained on larger detectors, such as Rayonix MX340-XFEL
-detector with a dimension of 1920 $\times$ 1920, even after downsizing by a
-factor of 4.  To mitigate this challenge, focal loss was introduced to address
-the extreme class imbalance problem for object detectors
-\citep{linFocalLossDense2018}.  More specifically, we employed a categorical
-focal loss.
+One main technical issue in training neural networks for Bragg peak segmentation is the extreme peak-background class imbalance (e.g., $> 10^3 : 1$), resulting in reduced prediction accuracy.
+This may not pose as a problem in previous peak finders like BraggNet, which operates on a much smaller area of $32 \times 32$, whereas \peaknet{} is trained on larger detectors, such as Rayonix MX340-XFEL detector with a dimension of 1920 $\times$ 1920, even after downsizing by a factor of 4.
+To mitigate this challenge, focal loss was introduced to address the extreme class imbalance problem for object detectors \citep{linFocalLossDense2018}.
+More specifically, we employed a categorical focal loss.
 
@@
 
-where CFL stands for categorical focal loss, $\alpha_j$ is a balancing factor
-for each class, $y_j^{(i)}$ is the grouth truth label of the $j$-th class for
-the $i$-th example.  $p_j^{(i)}$ is the predicted probability of the $j$-th
-class for the $i$-th example, calculated by the neural network $f$ parameterized
-by $\theta$ given input $x_j^{(i)}$.  $\gamma$ is a parameter controling the
-extent to which the weight of well-classified examples, such as background
-pixels, is reduced.  In our neural network training, we chose $\gamma = 2.0$,
-essentially, this means $(1-\hat{p} _j^{(i)}) ^\gamma$ is solely responsible for
-down-weighting easy examples, as $\hat{p} _j^{(i)}$ is usually large in this
-case.  Finding the ideal values for $\alpha$ can be a delicate process with only
-marginal returns, as highlighted in the original focal loss study
-\citep{linFocalLossDense2018}.  In order to fully utilize focal loss, we decided
-to use a fixed trivial value of $\alpha = 1.2$ for all examples, primarily for
-the sake of completeness.  This choice essentially treats $\alpha$ as a simple
-scaling factor without significant impact.  It is worth noting that in most
-cases, the sum of all $\alpha_j$ values, denoted as $\sum_{j = 1}^{C} \alpha_j$,
-is expected to equal 1.
+where CFL stands for categorical focal loss, $\alpha_j$ is a balancing factor for each class, $y_j^{(i)}$ is the grouth truth label of the $j$-th class for the $i$-th example.
+$p_j^{(i)}$ is the predicted probability of the $j$-th class for the $i$-th example, calculated by the neural network $f$ parameterized by $\theta$ given input $x_j^{(i)}$.
+$\gamma$ is a parameter controling the extent to which the weight of well-classified examples, such as background pixels, is reduced.
+In our neural network training, we chose $\gamma = 2.0$, essentially, this means $(1-\hat{p} _j^{(i)}) ^\gamma$ is solely responsible for down-weighting easy examples, as $\hat{p} _j^{(i)}$ is usually large in this case.
+Finding the ideal values for $\alpha$ can be a delicate process with only marginal returns, as highlighted in the original focal loss study \citep{linFocalLossDense2018}.
+In order to fully utilize focal loss, we decided to use a fixed trivial value of $\alpha = 1.2$ for all examples, primarily for the sake of completeness.
+This choice essentially treats $\alpha$ as a simple scaling factor without significant impact.
+It is worth noting that in most cases, the sum of all $\alpha_j$ values, denoted as $\sum_{j = 1}^{C} \alpha_j$, is expected to equal 1.
 
@@
 
-We applied three data augmentation techniques to each diffraction pattern in our
-dataset, including random in-plane rotation, random shifting in both horizontal
-and vertical directions and random masking.  Random in-plane rotation and
-shifting augment the training data, reducing the model's tendency to memorize
-features at specific locations.  This variability promotes more generalized
-feature extraction and improved generalization performance.  Random masking
-involves randomly obscuring parts of the input data, forcing the model to learn
-other relevant features that enhance its predictive capabilities during
-training.  The result of applying data augmentation to an arbitrary example is
-shown in Fig. \ref{fig : data aug}.
+We applied three data augmentation techniques to each diffraction pattern in our dataset, including random in-plane rotation, random shifting in both horizontal and vertical directions and random masking.
+Random in-plane rotation and shifting augment the training data, reducing the model's tendency to memorize features at specific locations.
+This variability promotes more generalized feature extraction and improved generalization performance.
+Random masking involves randomly obscuring parts of the input data, forcing the model to learn other relevant features that enhance its predictive capabilities during training.
+The result of applying data augmentation to an arbitrary example is shown in Fig.
+\ref{fig : data aug}.
 
@@
 
-\peaknet{} employs a data-driven approach to accurately identify Bragg peaks,
-requiring dataset improvement and correction to enhance performance.  This
-contrasts with model-driven approaches that primarily entail direct model
-modification to improve capabilities.  Fig. \ref{fig : data engine} illustrates
-a feedback loop for iterative dataset improvement and correction.
+\peaknet{} employs a data-driven approach to accurately identify Bragg peaks, requiring dataset improvement and correction to enhance performance.
+This contrasts with model-driven approaches that primarily entail direct model modification to improve capabilities.
+Fig.
+\ref{fig : data engine} illustrates a feedback loop for iterative dataset improvement and correction.
 
-The process begins with the preparation of a source dataset, often accomplished
-through a combination of algorithmic and manual data labeling.  Subsequently,
-the deep neural networks within \peaknet{} are trained on this dataset to learn
-how to accurately detect peaks.  Following training, the model is deployed to
-predict peaks on previously unseen data, and its performance is thoroughly
-evaluated.  During this evaluation, instances that notably worsen the
-performance of \peaknet{} are identified.  To address these limitations, we
-either correct low-quality labels predicted by the neural networks or,
-alternatively, acquire additional data that closely resemble these challenging
-instances and carefully annotate them.  Finally, we merge these newly labeled
-instances into the training set and retrain the model, thereby improving its
-overall performance.
+The process begins with the preparation of a source dataset, often accomplished through a combination of algorithmic and manual data labeling.
+Subsequently, the deep neural networks within \peaknet{} are trained on this dataset to learn how to accurately detect peaks.
+Following training, the model is deployed to predict peaks on previously unseen data, and its performance is thoroughly evaluated.
+During this evaluation, instances that notably worsen the performance of \peaknet{} are identified.
+To address these limitations, we either correct low-quality labels predicted by the neural networks or, alternatively, acquire additional data that closely resemble these challenging instances and carefully annotate them.
+Finally, we merge these newly labeled instances into the training set and retrain the model, thereby improving its overall performance.
 
-Interestingly, during the initial pass of this iterative process, \peaknet{}
-showed limited performance when dealing with images containing relatively low
-levels of photons.  However, by obtaining and annotating these images, we were
-able to enhance the training dataset and, as a result, significantly improve the
-predictive performance of \peaknet{}.
+Interestingly, during the initial pass of this iterative process, \peaknet{} showed limited performance when dealing with images containing relatively low levels of photons.
+However, by obtaining and annotating these images, we were able to enhance the training dataset and, as a result, significantly improve the predictive performance of \peaknet{}.
 
@@
 
-The primary goal of \peaknet{} is to autonomously detect Bragg peaks in
-diffraction images, devoid of any user input, such as algorithmic parameter
-tuning or manual artifact masking.  We implemented a two-step approach for peak
-detection, employing deep neural networks to perform semantic segmentation,
-which was subsequently followed by connected component analysis to extract image
-coordinates of Bragg peaks from the generated segmentation maps.  In this
-section, we begin by introducing the datasets used for training, validating, and
-testing \peaknet{}. Next, we present the evaluation results that demonstrate the
-predictive performance of \peaknet{}. Finally, we showcase its auto-masking
-capability and runtime efficiency.
+The primary goal of \peaknet{} is to autonomously detect Bragg peaks in diffraction images, devoid of any user input, such as algorithmic parameter tuning or manual artifact masking.
+We implemented a two-step approach for peak detection, employing deep neural networks to perform semantic segmentation, which was subsequently followed by connected component analysis to extract image coordinates of Bragg peaks from the generated segmentation maps.
+In this section, we begin by introducing the datasets used for training, validating, and testing \peaknet{}.
+Next, we present the evaluation results that demonstrate the predictive performance of \peaknet{}.
+Finally, we showcase its auto-masking capability and runtime efficiency.
 
@@
 
-We obtained X-ray diffraction images from two experiments conducted at the
-Macromolecular Femtosecond Crystallography (MFX) instrument within LCLS.  The
-primary dataset utilized for training and evaluating \peaknet{} is ``mfx13016"
-(Run number: 28,31-34, 36-38), which contains diverse biological samples, e.g.
-thaumatin and proteinase, and this experiment was originally used for automated
-drop dispensing research \citep{suSerialCrystallographyUsing2021}.  These
-diffraction images were recorded on a Rayonix MX340-XFEL detector with a
-dimension of 1920 $\times$ 1920, downsized by a factor of 4 to accommodate a
-higher readout rate.
+We obtained X-ray diffraction images from two experiments conducted at the Macromolecular Femtosecond Crystallography (MFX) instrument within LCLS.
+The primary dataset utilized for training and evaluating \peaknet{} is ``mfx13016" (Run number: 28,31-34, 36-38), which contains diverse biological samples, e.g.
+thaumatin and proteinase, and this experiment was originally used for automated drop dispensing research \citep{suSerialCrystallographyUsing2021}.
+These diffraction images were recorded on a Rayonix MX340-XFEL detector with a dimension of 1920 $\times$ 1920, downsized by a factor of 4 to accommodate a higher readout rate.
 
-The dataset ``mfx13016" exhibits a notable characteristic of prominent nozzle
-scattering rings accompanied by bright Bragg peak-like spots located on the
-rings.  This characteristic presents two primary challenges for crystallography
-data analysis: increased difficulty in crystal indexing and misleading
-integration results caused by artifact scattering.  The current best practice
-involves manual masking of these artifact scattering, enabling data analysis to
-proceed as if they are absent, but this process is prone to errors and
-time-consuming.  Additionally, the final outcomes often hinge on the expertise
-of the individuals conducting the data processing, resulting in biases,
-scalability limitations, lack of standardization, and the possibility of human
-errors.  Nevertheless, the inherent challenges presented by this dataset offer
-an exceptional opportunity to testify the autonomous peak finding capability of
-\peaknet{}.
+The dataset ``mfx13016" exhibits a notable characteristic of prominent nozzle scattering rings accompanied by bright Bragg peak-like spots located on the rings.
+This characteristic presents two primary challenges for crystallography data analysis: increased difficulty in crystal indexing and misleading integration results caused by artifact scattering.
+The current best practice involves manual masking of these artifact scattering, enabling data analysis to proceed as if they are absent, but this process is prone to errors and time-consuming.
+Additionally, the final outcomes often hinge on the expertise of the individuals conducting the data processing, resulting in biases, scalability limitations, lack of standardization, and the possibility of human errors.
+Nevertheless, the inherent challenges presented by this dataset offer an exceptional opportunity to testify the autonomous peak finding capability of \peaknet{}.
 
-The neural network training dataset consists of 98 Rayonix images in run 28 of
-``mfx13016", which includes thaumatin samples, and an additional 37 images
-sampled from an internal LCLS experimental dataset related to therapeutics
-development associated with SARS-CoV-2.  Incorporating the SARS-CoV-2 dataset
-aims to educate \peaknet{} about the presence of images without artifact rings,
-diversifying its understanding of different data characteristics.  Nonetheless,
-all these images used for neural network training have a dimension of 1920
-$\times$ 1920 and they are divided into an 80\% training set and a 20\%
-validation set.  The final test dataset for evaluating the model comprises all
-images in run 31-34 and run 36-38 of ``mfx13016".
+The neural network training dataset consists of 98 Rayonix images in run 28 of ``mfx13016", which includes thaumatin samples, and an additional 37 images sampled from an internal LCLS experimental dataset related to therapeutics development associated with SARS-CoV-2.
+Incorporating the SARS-CoV-2 dataset aims to educate \peaknet{} about the presence of images without artifact rings, diversifying its understanding of different data characteristics.
+Nonetheless, all these images used for neural network training have a dimension of 1920 $\times$ 1920 and they are divided into an 80\% training set and a 20\% validation set.
+The final test dataset for evaluating the model comprises all images in run 31-34 and run 36-38 of ``mfx13016".
 
@@
 
-The peak finding performance of peak finders is evaluated through two
-significant indicators from a user's standpoint: the number of successfully
-indexed hits and the merging statistics.  For our evaluation, we utilized the
-CrystFEL software suite \citep{whiteCrystFELSoftwareSuite2012} to perform
-crystal indexing, integration, and merging tasks.  We use \psocake{}'s peak
-finder as a baseline in this evaluation.
+The peak finding performance of peak finders is evaluated through two significant indicators from a user's standpoint: the number of successfully indexed hits and the merging statistics.
+For our evaluation, we utilized the CrystFEL software suite \citep{whiteCrystFELSoftwareSuite2012} to perform crystal indexing, integration, and merging tasks.
+We use \psocake{}'s peak finder as a baseline in this evaluation.
 
@@
 
-\peaknet{} and \psocake{}, when manually fine-tuned, exhibit comparable peak
-finding performance in terms of the number of hits and the number of indexed
-images, as shown in Table \ref{tb : index}.  However, it is critical to
-emphasize that while \peaknet{} operates entirely autonomously, \psocake{}'s
-performance is contingent upon manual parameter fine-tuning and manual artifact
-scattering masking.  For example, an earlier work
-\citep{suSerialCrystallographyUsing2021}, which processed essentially the same
-experimental data, reported significantly lower hit count and indexed image
-count.  Consequently, this highlights \peaknet{}'s advantage in user-independent
-data processing.
+\peaknet{} and \psocake{}, when manually fine-tuned, exhibit comparable peak finding performance in terms of the number of hits and the number of indexed images, as shown in Table \ref{tb : index}.
+However, it is critical to emphasize that while \peaknet{} operates entirely autonomously, \psocake{}'s performance is contingent upon manual parameter fine-tuning and manual artifact scattering masking.
+For example, an earlier work \citep{suSerialCrystallographyUsing2021}, which processed essentially the same experimental data, reported significantly lower hit count and indexed image count.
+Consequently, this highlights \peaknet{}'s advantage in user-independent data processing.
 
-Moreover, while users might prioritize the absolute number of indexed images as
-a more straightforward metric, the indexing rate provides valuable insights into
-the method's efficiency.  Both metrics jointly offer a more comprehensive
-evaluation of the peak finding method. In the case of \peaknet{}, both the
-consistently high number of indexed images and the good indexing rate testify to
-its effective and reliable autonomous peak finding process, positioning it as a
-highly viable option for Bragg peak finding.
+Moreover, while users might prioritize the absolute number of indexed images as a more straightforward metric, the indexing rate provides valuable insights into the method's efficiency.
+Both metrics jointly offer a more comprehensive evaluation of the peak finding method.
+In the case of \peaknet{}, both the consistently high number of indexed images and the good indexing rate testify to its effective and reliable autonomous peak finding process, positioning it as a highly viable option for Bragg peak finding.
 
@@
 
-Merging statistics confirms \peaknet{}'s robust performance in terms of
-consistency and quality in data processing.  For the thaumatin (TH) sample,
-\peaknet{} demonstrates marginally superior performance in terms of R-split
-values, correlation coefficients, $I/\sigma(I)$ values, redundancy, and
-completeness, achieving these results autonomously.  Notably, the R-split value
-for the TH sample is slightly lower for \peaknet{} (0.2605 vs. 0.2732),
-suggesting slightly better internal consistency. Similarly, correlation
-coefficients for \peaknet{} are marginally higher (CC$_1/2$: 0.9434 vs.  0.9368;
-CC*: 0.9853 vs. 0.9835), indicating a minor advantage in the precision of
-measurements.
+Merging statistics confirms \peaknet{}'s robust performance in terms of consistency and quality in data processing.
+For the thaumatin (TH) sample, \peaknet{} demonstrates marginally superior performance in terms of R-split values, correlation coefficients, $I/\sigma(I)$ values, redundancy, and completeness, achieving these results autonomously.
+Notably, the R-split value for the TH sample is slightly lower for \peaknet{} (0.2605 vs.
+0.2732), suggesting slightly better internal consistency.
+Similarly, correlation coefficients for \peaknet{} are marginally higher (CC$_1/2$: 0.9434 vs.
+0.9368; CC*: 0.9853 vs.
+0.9835), indicating a minor advantage in the precision of measurements.
 
 However, for the proteinase (PK) sample, the performance comparision is mixed.
-Although \peaknet{} lags slightly behind manually fine-tuned \psocake{} in terms
-of R-split and redundancy, it outperforms in CC$_1/2$, CC*, $I/\sigma(I)$, and
-completeness values.  This reinforces the effectiveness of \peaknet{} in
-achieving respectable results across varied sample types, without any manual
-intervention or parameter fine-tuning.
+Although \peaknet{} lags slightly behind manually fine-tuned \psocake{} in terms of R-split and redundancy, it outperforms in CC$_1/2$, CC*, $I/\sigma(I)$, and completeness values.
+This reinforces the effectiveness of \peaknet{} in achieving respectable results across varied sample types, without any manual intervention or parameter fine-tuning.
 
-Overall, \peaknet{} demonstrates comparable performance to a manually fine-tuned
-\psocake{} for two distinct samples, showcasing its potential for autonomous
-peak finding with consistent results.  By reducing dependence on the expertise
-of individuals, which can have considerable variation, \peaknet{} offers a
-promising user-indepenent solution.  Notably, despite primarily being trained on
-PK samples, \peaknet{} maintains robust and versatile performance, indicating
-its broad applicability and effectiveness in handling diverse datasets.
+Overall, \peaknet{} demonstrates comparable performance to a manually fine-tuned \psocake{} for two distinct samples, showcasing its potential for autonomous peak finding with consistent results.
+By reducing dependence on the expertise of individuals, which can have considerable variation, \peaknet{} offers a promising user-indepenent solution.
+Notably, despite primarily being trained on PK samples, \peaknet{} maintains robust and versatile performance, indicating its broad applicability and effectiveness in handling diverse datasets.
 
@@
 
-The integration of the ``auto-masking" functionality in \peaknet{} represents a
-notable advancement in the automated processing of diffraction images.  The
-underlying neural network architecture enables \peaknet{} to autonomously
-discern and segregate pixel regions affected by artifact scattering, such as
-these appearing as distinct ring-like structures induced by liquid jet nozzle
-scattering.  This capability circumvents the need for manual masking in the peak
-finding process, thereby optimizing the efficiency of crystallographic data
-processing.
+The integration of the ``auto-masking" functionality in \peaknet{} represents a notable advancement in the automated processing of diffraction images.
+The underlying neural network architecture enables \peaknet{} to autonomously discern and segregate pixel regions affected by artifact scattering, such as these appearing as distinct ring-like structures induced by liquid jet nozzle scattering.
+This capability circumvents the need for manual masking in the peak finding process, thereby optimizing the efficiency of crystallographic data processing.
 
-Fig. \ref{fig : automask 1} provides a comparative visualization of \peaknet{}'s
-effectiveness in accurately segmenting regions with bright pixels induced by
-artifact scattering under various conditions.  Images without artifact ring
-structures are also included in the visualization, reassuring that \peaknet{}
-does not generate or ``hallucinate" artifact rings where they do not exist.  This
-visual representation serves as tangible evidence of \peaknet{} 's adeptness in
-discriminating and processing pertinent features, regardless of the contextual
-complexities.
+Fig.
+\ref{fig : automask 1} provides a comparative visualization of \peaknet{}'s effectiveness in accurately segmenting regions with bright pixels induced by artifact scattering under various conditions.
+Images without artifact ring structures are also included in the visualization, reassuring that \peaknet{} does not generate or ``hallucinate" artifact rings where they do not exist.
+This visual representation serves as tangible evidence of \peaknet{} 's adeptness in discriminating and processing pertinent features, regardless of the contextual complexities.
 
-Furthermore, while evaluating \peaknet{}'s ``auto-masking" feature on intended
-input images, we explored its behavior on unintended inputs, providing insights
-into its robustness and generalizability.  Fig. \ref{fig : automask 2} depicts
-illustrative examples of \peaknet{} predicting artifact scattering patterns in
-Ag Behenate scattering captured on various detectors.  Surprisingly, \peaknet{}
-reliably identifies the characteristic scattering ring structures present in Ag
-Behenate images.  This observation provides compelling evidence once again,
-further demonstrating the robust predictive capability of \peaknet{} in
-accurately recognizing artifact scattering patterns.  As a result, it reinforces
-that effectiveness of \peaknet{}'s ``auto-masking" feature.
+Furthermore, while evaluating \peaknet{}'s ``auto-masking" feature on intended input images, we explored its behavior on unintended inputs, providing insights into its robustness and generalizability.
+Fig.
+\ref{fig : automask 2} depicts illustrative examples of \peaknet{} predicting artifact scattering patterns in Ag Behenate scattering captured on various detectors.
+Surprisingly, \peaknet{} reliably identifies the characteristic scattering ring structures present in Ag Behenate images.
+This observation provides compelling evidence once again, further demonstrating the robust predictive capability of \peaknet{} in accurately recognizing artifact scattering patterns.
+As a result, it reinforces that effectiveness of \peaknet{}'s ``auto-masking" feature.
 
@@
 
-Peak finding can pose significant computational demands, particularly in high
-data rate experiments, highlighting the critical importance of an efficient peak
-finding algorithm.  A comparative analysis of runtime performance demonstrates
-the greater efficiency of \peaknet{} compared to other commonly used peak
-finders like the one within \psocake{}.
+Peak finding can pose significant computational demands, particularly in high data rate experiments, highlighting the critical importance of an efficient peak finding algorithm.
+A comparative analysis of runtime performance demonstrates the greater efficiency of \peaknet{} compared to other commonly used peak finders like the one within \psocake{}.
 
-When processing Rayonix images with a resolution of $1920 \times 1920$,
-\peaknet{} achieved a significantly reduced processing time of 90 milliseconds
-per event on an NVIDIA 1080 Ti GPU.  In contrast, \psocake{} required 176
-milliseconds per event when executed on an Intel E5-2620.  Another peak finding
-method, RPF (robust peak finder), operating on Intel E5-2698, is reported to
-require 120.0 milliseconds but on smaller AGIPD 1M images with the size of $1024
-\times 1024$ \citep{hadian-jaziDataReductionSerial2021}.  This result clearly
-demonstrates that \peaknet{} not only delivers robust Bragg peak finding results
-in an autonomous fashion, but also exhibits remarkable runtime efficiency.  This
-establishes it as a highly competent tool for real-time autonomous Bragg peak
-finding.
+When processing Rayonix images with a resolution of $1920 \times 1920$, \peaknet{} achieved a significantly reduced processing time of 90 milliseconds per event on an NVIDIA 1080 Ti GPU.
+In contrast, \psocake{} required 176 milliseconds per event when executed on an Intel E5-2620.
+Another peak finding method, RPF (robust peak finder), operating on Intel E5-2698, is reported to require 120.0 milliseconds but on smaller AGIPD 1M images with the size of $1024 \times 1024$ \citep{hadian-jaziDataReductionSerial2021}.
+This result clearly demonstrates that \peaknet{} not only delivers robust Bragg peak finding results in an autonomous fashion, but also exhibits remarkable runtime efficiency.
+This establishes it as a highly competent tool for real-time autonomous Bragg peak finding.
 
@@
 
-\peaknet{} exhibits exceptional capabilities in autonomous detection of Bragg
-peaks in diffraction images without requiring user input or intervention, such
-as algorithmic parameter tuning or manual artifact scattering masking.  The
-predictive performance of \peaknet{} in peak finding proves to be comparable to,
-if not better than, manually fine-tuned \psocake{} with user-supplied masks.  An
-integral feature of \peaknet{}, auto-masking, significantly enhances its ability
-to autonomously identify and process artifact scattering patterns.  Moreover,
-the efficiency of \peaknet{} is exemplified by its impressive runtime
-performance, surpassesing commonly used peak finders like \psocake{} and RPF.
-Parallel processing with GPU streaming can potentially improve the runtime
-efficiency even further.  In conclusion, \peaknet{}  offers a robust, versatile,
-and efficient solution that operates independently of user input, thereby
-holding significant potential for optimizing crystallographic data processing at
-high data rates.
+\peaknet{} exhibits exceptional capabilities in autonomous Bragg peaks finding without requiring user input or intervention, such as algorithmic parameter tuning or manual artifact scattering masking.
+The predictive performance of \peaknet{} in peak finding proves to be comparable to, if not better than, manually fine-tuned \psocake{} with user-supplied masks.
+An integral feature of \peaknet{}, auto-masking, significantly enhances its ability to autonomously identify and process artifact scattering patterns.
+Moreover, the efficiency of \peaknet{} is exemplified by its impressive runtime performance, surpassesing commonly used peak finders like \psocake{} and RPF.
+Parallel processing with GPU streaming can potentially improve the runtime efficiency even further.
+In conclusion, \peaknet{}  offers a robust, versatile, and efficient solution that operates independently of user input, thereby holding significant potential for optimizing crystallographic data processing at high data rates.
 

### 2023-06-16 manuscript.tex
Correct typos.

@@
 Time-resolved serial crystallography at XFEL facilities, like the Linac Coherent Light Source (LCLS), allows the investigation of biochemical reactions with femtosecond-scale time resolutions.
-This technique is typically referred to as serial femtosecond crystallography (SFX), which has led to many signficiant structural studies \citep{kupitzSerialTimeresolvedCrystallography2014, nangoThreedimensionalMovieStructural2016,pandeFemtosecondStructuralDynamics2016a, youngStructurePhotosystemII2016,sugaLightinducedStructuralChanges2017, kernStructuresIntermediatesKok2018,ibrahimUntanglingSequenceEvents2020, sugaTimeresolvedStudiesMetalloproteins2020} since the first published work at LCLS \citep{aquilaTimeresolvedProteinNanocrystallography2012}.
+This technique is typically referred to as serial femtosecond crystallography (SFX), which has led to many significant structural studies \citep{kupitzSerialTimeresolvedCrystallography2014, nangoThreedimensionalMovieStructural2016,pandeFemtosecondStructuralDynamics2016a, youngStructurePhotosystemII2016,sugaLightinducedStructuralChanges2017, kernStructuresIntermediatesKok2018,ibrahimUntanglingSequenceEvents2020, sugaTimeresolvedStudiesMetalloproteins2020} since the first published work at LCLS \citep{aquilaTimeresolvedProteinNanocrystallography2012}.
 In the meantime, the data rate at XFEL facilities have also gradually increased from hundreds of Hz to the MHz range, with the European X-ray Free Electron Laser (EuXFEL) being the first MHz facility available to users and LCLS-II set to launch in 2023.
@@
 
-While template matching and region-growing tecnhiques require users to provide priori information like threshold values, Robust Peak Finder (RPF) \citep{hadian-jaziPeakfindingAlgorithmBased2017, hadian-jaziDataReductionSerial2021} has demonstrated proficient peak finding capabilities with minimal user inputs.
-This techinuqe utilizes the Modified Selective Statistical Estimator (MSSE) method to segment between background pixels and actual peaks.
+While template matching and region-growing techniques require users to provide priori information like threshold values, Robust Peak Finder (RPF) \citep{hadian-jaziPeakfindingAlgorithmBased2017, hadian-jaziDataReductionSerial2021} has demonstrated proficient peak finding capabilities with minimal user inputs.
+This technique utilizes the Modified Selective Statistical Estimator (MSSE) method to segment between background pixels and actual peaks.
 Furthermore, the RPF method can also parallelize the processing of diffraction patterns, making it ideal for real-time data analysis.
 
-\psocake{} is a software specifically designed to streamline high throughput data reduction and analysis of XFEL experiments, and is routinely used at SLAC National Accelerator laborator (SLAC) and Pohang Accelerator Laboratory (PAL).
+\psocake{} is a software specifically designed to streamline high throughput data reduction and analysis of XFEL experiments, and is routinely used at SLAC National Accelerator laboratory (SLAC) and Pohang Accelerator Laboratory (PAL).
 The built-in peak-finding algorithm \citep{shinDataAnalysisUsing2018} includes calibrating raw analog digital units (ADUs); applying optional background correction and bad pixel masks; identifying possible peaks; calculating their SNR; determining Bragg spot sizes; and selecting peaks based on size, total intensity and SNR.
@@
 $p_j^{(i)}$ is the predicted probability of the $j$-th class for the $i$-th example, calculated by the neural network $f$ parameterized by $\theta$ given input $x_j^{(i)}$.
-$\gamma$ is a parameter controling the extent to which the weight of well-classified examples, such as background pixels, is reduced.
+$\gamma$ is a parameter controlling the extent to which the weight of well-classified examples, such as background pixels, is reduced.
 In our neural network training, we chose $\gamma = 2.0$, essentially, this means $(1-\hat{p} _j^{(i)}) ^\gamma$ is solely responsible for down-weighting easy examples, as $\hat{p} _j^{(i)}$ is usually large in this case.
@@
 
-However, for the proteinase (PK) sample, the performance comparision is mixed.
+However, for the proteinase (PK) sample, the performance comparison is mixed.
 Although \peaknet{} lags slightly behind manually fine-tuned \psocake{} in terms of R-split and redundancy, it outperforms in CC$_1/2$, CC*, $I/\sigma(I)$, and completeness values.
@@
 Overall, \peaknet{} demonstrates comparable performance to a manually fine-tuned \psocake{} for two distinct samples, showcasing its potential for autonomous peak finding with consistent results.
-By reducing dependence on the expertise of individuals, which can have considerable variation, \peaknet{} offers a promising user-indepenent solution.
+By reducing dependence on the expertise of individuals, which can have considerable variation, \peaknet{} offers a promising user-independent solution.
 Notably, despite primarily being trained on PK samples, \peaknet{} maintains robust and versatile performance, indicating its broad applicability and effectiveness in handling diverse datasets.
@@
 An integral feature of \peaknet{}, auto-masking, significantly enhances its ability to autonomously identify and process artifact scattering patterns.
-Moreover, the efficiency of \peaknet{} is exemplified by its impressive runtime performance, surpassesing commonly used peak finders like \psocake{} and RPF.
+Moreover, the efficiency of \peaknet{} is exemplified by its impressive runtime performance, surpassing commonly used peak finders like \psocake{} and RPF.
 Parallel processing with GPU streaming can potentially improve the runtime efficiency even further.

### 2023-06-16 manuscript.tex
Resize the runtime performance table.
Add acknowledgement

@@
 
-\begin{table}[t]
+\begin{table*}[t]
 \caption{
@@
 \centering
-\resizebox{\columnwidth}{!}{
+\resizebox{!}{!}{
 \begin{tabular}{llcc}
@@
 }
-\end{table}
+\end{table*}
 
@@
 
+\section*{Acknowledgment}
+
+Earlier versions utilizing the original U-Net model were built and tested by P.L under the supervision of C.H.Y.
+The experiments were designed by C.W with inputs from J.B.T and C.H.Y.
+C.W implemented the residual attention U-Net, prepared the datasets, labeled experimental data, and trained and evaluated the refined neural network model.
+The manuscript was written by C.W and C.H.Y with input from all authors.
+This material is based upon work supported by the U.S.
+Department of Energy, Office of Science, Office of Basic Energy Sciences under Award Number FWP-100643.
+Use of the Linac Coherent Light Source (LCLS), SLAC National Accelerator Laboratory, is supported by the U.S.
+Department of Energy, Office of Science, Office of Basic Energy Sciences under Contract No.
+DE-AC02-76SF00515.
+
 % Bibliography

### 2023-06-28 manuscript.tex
Correct format for arxiv submission.

@@
 
-Serial crystallography at X-ray free electron laser (XFEL) sources has experienced tremendous progresses in achieving high data rate in recent times, offering potential to enable novel scientific investigations, such as imaging faster molecular events.
-However, this approach also generates a significant amount volume of data with sparsely distributed scientific signals, posing challenges in data reduction and real-time feedback.
-To address these concerns, a rapid and efficient Bragg peak finding process serves as the pivotal initial step, effectively addressing both data storage concerns and real-time feedback requirements simultaneously.
-Here, we present \peaknet{}, a autonomous Bragg peak finder that utilizes deep neural networks, eliminating the need for manual parameter tuning common in conventional peak finders and the laborious task of manually masking pixels affected by artifact scattering, such as nozzle scattering rings.
-\peaknet{} also exhibits exceptional runtime efficiency, processing a $1920 \times 1920$ image around 90 ms on an NVIDIA 1080 Ti GPU, with the potential for further enhancements through parallelized analysis or GPU stream processing.
-With its ability to scale linearly with respect to data volume, \peaknet{} is well-suited for real-time serial crystallography data analysis at high data rates.
+Serial crystallography at X-ray free electron laser (XFEL) and synchrotron facilities has experienced tremendous progress in recent times enabling novel scientific investigations into macromolecular structures and molecular processes.
+However, these experiments generate a significant amount of data posing computational challenges in data reduction and real-time feedback.
+Bragg peak finding algorithm is used to identify useful images and also provide real-time feedback about hit-rate and resolution.
+Shot-to-shot intensity fluctuations and strong background scattering from buffer solution, injection nozzle and other shielding materials make this a time-consuming optimization problem.
+Here, we present \peaknet{}, an autonomous Bragg peak finder that utilizes deep neural networks.
+The development of this system 1) eliminates the need for manual algorithm parameter tuning, 2) reduces false-positive peaks by adjusting to shot-to-shot variations in strong background scattering in real-time, 3) eliminates the laborious task of manually creating bad pixel masks and the need to store these masks per event since these can be regenerated on demand.
+\peaknet{} also exhibits exceptional runtime efficiency, processing a $1920 \times 1920$ pixel image around 90 ms on an NVIDIA 1080 Ti GPU, with the potential for further enhancements through parallelized analysis or GPU stream processing.
+\peaknet{} is well-suited for expert-level real-time serial crystallography data analysis at high data rates.
 
@@
 
-Serial crystallography with X-ray free electron lasers (XFEL) has enabled the structural determination of three-dimensional macromolecules from radiation damage-free samples at room temperature, an approach commonly known as \textit{diffraction-before-destruction} \citep{neutzePotentialBiomolecularImaging2000, chapmanFemtosecondDiffractiveImaging2006,chapmanFemtosecondXrayProtein2011}.
-Time-resolved serial crystallography at XFEL facilities, like the Linac Coherent Light Source (LCLS), allows the investigation of biochemical reactions with femtosecond-scale time resolutions.
-This technique is typically referred to as serial femtosecond crystallography (SFX), which has led to many significant structural studies \citep{kupitzSerialTimeresolvedCrystallography2014, nangoThreedimensionalMovieStructural2016,pandeFemtosecondStructuralDynamics2016a, youngStructurePhotosystemII2016,sugaLightinducedStructuralChanges2017, kernStructuresIntermediatesKok2018,ibrahimUntanglingSequenceEvents2020, sugaTimeresolvedStudiesMetalloproteins2020} since the first published work at LCLS \citep{aquilaTimeresolvedProteinNanocrystallography2012}.
+Serial crystallography with X-ray free electron lasers (XFEL) has enabled radiation damage-free structural determination of macromolecules at room temperature, an approach commonly known as \textit{diffraction-before-destruction} \citep{neutzePotentialBiomolecularImaging2000, chapmanFemtosecondDiffractiveImaging2006,chapmanFemtosecondXrayProtein2011}.
+Time-resolved serial femtosecond crystallography at XFEL facilities, like the Linac Coherent Light Source (LCLS), allows the investigation of biochemical reactions with femtosecond-scale time resolution which has led to many significant structural studies \citep{kupitzSerialTimeresolvedCrystallography2014, nangoThreedimensionalMovieStructural2016,pandeFemtosecondStructuralDynamics2016a, youngStructurePhotosystemII2016,sugaLightinducedStructuralChanges2017, kernStructuresIntermediatesKok2018,ibrahimUntanglingSequenceEvents2020, sugaTimeresolvedStudiesMetalloproteins2020} since the first published work at LCLS \citep{aquilaTimeresolvedProteinNanocrystallography2012}.
 In the meantime, the data rate at XFEL facilities have also gradually increased from hundreds of Hz to the MHz range, with the European X-ray Free Electron Laser (EuXFEL) being the first MHz facility available to users and LCLS-II set to launch in 2023.
@@
 At the MHz data rate, novel real-time data analysis approaches are needed to tackle two major challenges that arise in SFX experiments, namely data reduction and real time feedback.
-One common approach for finding hits in serial crystallography data is to utilize existing Bragg peak finders like the Cheetah peak finder \citep{bartyCheetahSoftwareHighthroughput2014}, the Robust Peak Finder (RPF) \citep{hadian-jaziPeakfindingAlgorithmBased2017}, or the \psocake{} \citep{yoonPsocakeGUIMaking2020} peak finder.
-Additionally, a deep neural network-based hit finder for serial crystallography has been reported to achieve a processing rate of 1.3 kHz by analyzing downsized 180 $\times$ 180 images using a single GPU \citep{keConvolutionalNeuralNetworkbased2018}.
-Secondly, real-time feedback in serial crystallography experiments plays a crucial role by providing users with important information about the experimental conditions.
-This enables them to make timely decisions that optimize the data acquisition process.
+The standard approach for data reduction is vetoing events where the x-ray pulse did not ``hit'' the sample.
+Typically, hit finding in serial crystallography utilizes Bragg peak finding algorithms implemented in such programs as Cheetah  \citep{bartyCheetahSoftwareHighthroughput2014}, DIALS \citep{winterDIALSImplementationEvaluation2018}, and \psocake{} \citep{yoonPsocakeGUIMaking2020}.
+Additionally, a deep neural network-based hit finder for serial crystallography has been reported to achieve a processing rate of 1.3 kHz by analyzing downsized 180 $\times$ 180 images on a single GPU \citep{keConvolutionalNeuralNetworkbased2018}.
+Real-time feedback in serial crystallography experiments plays a crucial role by providing users with important information about the experimental conditions.
+This enables them to make timely decisions that optimize the data collection process.
 For instance, it is essential to fine-tune the hit rate to maximize the utilization of samples.
@@
 Therefore, relying solely on hit finding is insufficient to gain the necessary insights, making real-time Bragg peak finding vital for delivering prompt and comprehensive feedback.
-However, the peak finder mentioned earlier in \psocake{} operates at a rate of approximately 5 Hz on a data center CPU, which could lead to significant costs when scaling up the process.
 
 In this work, we introduce \peaknet{}, a solution that effectively addresses the challenge of autonomously and efficiently identifying Bragg peaks in high data rate scenarios.
-Our approach involves transforming the peak finding problem into semantic segmentation tasks, where different regions within diffraction images are classified and segmented using deep learning networks.
-By leveraging this process, \peaknet{} autonomously detects Bragg peaks while effectively identifying strong artifact scattering, eliminating the need for human intervention.
+Our approach involves transforming the peak finding problem into a semantic segmentation task, where different regions within diffraction images are classified and segmented using a deep neural network.
+\peaknet{} autonomously detects Bragg peaks while effectively identifying shot-to-shot variations of strong non-Bragg scattering artifacts, eliminating the need for human intervention.
 Subsequently, connected areas of pixels are examined and treated as individual peaks, a task easily accomplished through connected component analysis \citep{weaverCentrosymmetricCrossSymmetricMatrices1985}.
 The coordinates of the peaks are determined by calculating the center of mass of all pixels belonging to each identified peak.
-Notably, the entire peak finding process is performed on GPUs, offering a cost-effective solution for achieving scalability.
+Notably, the entire peak finding process is performed on GPUs, offering a cost-effective solution for achieving low latency.
 
@@
 
-While template matching and region-growing techniques require users to provide priori information like threshold values, Robust Peak Finder (RPF) \citep{hadian-jaziPeakfindingAlgorithmBased2017, hadian-jaziDataReductionSerial2021} has demonstrated proficient peak finding capabilities with minimal user inputs.
-This technique utilizes the Modified Selective Statistical Estimator (MSSE) method to segment between background pixels and actual peaks.
+While template matching and region-growing techniques require users to provide prior information like threshold values, Robust Peak Finder (RPF) \citep{hadian-jaziPeakfindingAlgorithmBased2017, hadian-jaziDataReductionSerial2021} has demonstrated proficient peak finding capabilities with minimal user input.
+This technique utilizes the Modified Selective Statistical Estimator (MSSE) method to segment background pixels and actual peaks.
 Furthermore, the RPF method can also parallelize the processing of diffraction patterns, making it ideal for real-time data analysis.
 
-\psocake{} is a software specifically designed to streamline high throughput data reduction and analysis of XFEL experiments, and is routinely used at SLAC National Accelerator laboratory (SLAC) and Pohang Accelerator Laboratory (PAL).
+\psocake{} is a software program specifically designed to streamline high throughput data reduction and analysis of XFEL experiments, and is routinely used at SLAC National Accelerator laboratory (SLAC).
 The built-in peak-finding algorithm \citep{shinDataAnalysisUsing2018} includes calibrating raw analog digital units (ADUs); applying optional background correction and bad pixel masks; identifying possible peaks; calculating their SNR; determining Bragg spot sizes; and selecting peaks based on size, total intensity and SNR.
@@
 
-The current peak finding process of \peaknet{} comprises two steps, as depicted in Fig.
+The current peak finding process of \peaknet{} comprises of two steps, as depicted in Fig.
 \ref{fig : peak finding}.
-Firstly, a segmentation map is obtained from the input image using deep neural networks.
+First, a segmentation map is obtained from the input image using a deep neural network.
 Subsequently, peak positions are determined based on the generated segmentation map using connected component analysis \citep{weaverCentrosymmetricCrossSymmetricMatrices1985}.
-Importantly, \peaknet{} has the capability to process inputs with arbitrary image sizes in a batch manner, enabling efficient analysis.
+Importantly, \peaknet{} has the capability to process inputs with arbitrary image sizes in batches, enabling efficient analysis.
 
-In this section, our focus is to provide a comprehensive understanding of the underlying deep neural network components in \peaknet{}.
+In this section, our focus is to provide a comprehensive description of the underlying deep neural network components in \peaknet{}.
 We will specifically discuss the network architecture, data augmentation techniques, and the loss function employed during the training process.
@@
 obtaining a segmentation map from the input using the underlying deep neural
-networks; (2) identifying peak positions based on the generated segmentation map
+network; (2) identifying peak positions based on the generated segmentation map
 using connected component analysis.  It is worth noting that \peaknet{} is
@@
 
-It is essential to acknowledge that our neural network architecture is primarily based on the original ``Attention U-Net" design \citep{oktayAttentionUNetLearning2018}.
+Our neural network architecture is primarily based on the original ``Attention U-Net" design \citep{oktayAttentionUNetLearning2018}.
 However, we want to point out that the three-component design, consisting of the ``backbone", ``neck" and ``head", offers the flexibility to replace these components with different architectures.
-For instance, the ``backbone" can be substituted with RegNet \citep{radosavovicDesigningNetworkDesign2020}, while the ``neck" can be replaced with other multi-resolution feature fusion methods like feature pyramid networks (FPN) \citep{linFeaturePyramidNetworks2017} or bidirectional feature pyramid networks (BiFPN) \citep{tanEfficientDetScalableEfficient2020}.
+For instance, the ``backbone" can be substituted with a ResNet \citep{heDeepResidualLearning2016}, while the ``neck" can be replaced with other multi-resolution feature fusion methods like feature pyramid networks (FPN) \citep{linFeaturePyramidNetworks2017} or bidirectional feature pyramid networks (BiFPN) \citep{tanEfficientDetScalableEfficient2020}.
 Additionally, the ``head" can be extended to perform additional tasks, if desired, such as predicting the likelihood of the input image being indexable.
@@
 \caption{Neural network architecture: Attention U-Net with residual connections.
-(a) Overall end-to-end network architecture.  (b) The residual double
-convolutional block.  (c) The gated feature fusion block for merging
+(a) Overall end-to-end network architecture.  (b) Residual double
+convolutional block.  (c) Gated feature fusion block for merging
 multi-resolution features.}
@@
 
-One main technical issue in training neural networks for Bragg peak segmentation is the extreme peak-background class imbalance (e.g., $> 10^3 : 1$), resulting in reduced prediction accuracy.
-This may not pose as a problem in previous peak finders like BraggNet, which operates on a much smaller area of $32 \times 32$, whereas \peaknet{} is trained on larger detectors, such as Rayonix MX340-XFEL detector with a dimension of 1920 $\times$ 1920, even after downsizing by a factor of 4.
-To mitigate this challenge, focal loss was introduced to address the extreme class imbalance problem for object detectors \citep{linFocalLossDense2018}.
-More specifically, we employed a categorical focal loss.
+One main technical issue in training neural networks for Bragg peak segmentation is the extreme peak-background class imbalance (e.g., less than $1 : 10^3$), resulting in reduced prediction accuracy.
+This may not pose as a problem in previous peak finders like BraggNet, which operates on a much smaller area of $32 \times 32$, \peaknet{} is trained on larger detectors, such as the Rayonix MX340-XFEL detector with a dimension of 1920 $\times$ 1920 pixels even after $4 \times 4$ pixel binning.
+To mitigate the label imbalance, we employ a categorical focal loss to address the problem \citep{linFocalLossDense2018}.
 
@@
             \alpha_j \cdot y_j^{(i)} \cdot (1-\hat{p}_j^{(i)})^\gamma 
-            \cdot \log{\hat{p}_j^{(i)}} \\
+            \cdot \log{\hat{p}_j^{(i)}}, \\
 \hat{p}_j^{(i)} &= f_\theta(x_j^{(i)})
@@
 
-where CFL stands for categorical focal loss, $\alpha_j$ is a balancing factor for each class, $y_j^{(i)}$ is the grouth truth label of the $j$-th class for the $i$-th example.
-$p_j^{(i)}$ is the predicted probability of the $j$-th class for the $i$-th example, calculated by the neural network $f$ parameterized by $\theta$ given input $x_j^{(i)}$.
+where CFL stands for categorical focal loss, $\alpha_j$ is a balancing factor for each class, $y_j^{(i)}$ is the ground truth label of the $j$-th class for the $i$-th pixel.
+$p_j^{(i)}$ is the predicted probability of the $j$-th class for the $i$-th pixel, calculated by the neural network $f$ parameterized by $\theta$ given input image $x_j^{(i)}$ with $N$ number of pixels and $C$ categories.
 $\gamma$ is a parameter controlling the extent to which the weight of well-classified examples, such as background pixels, is reduced.
@@
 This choice essentially treats $\alpha$ as a simple scaling factor without significant impact.
-It is worth noting that in most cases, the sum of all $\alpha_j$ values, denoted as $\sum_{j = 1}^{C} \alpha_j$, is expected to equal 1.
+In most cases, the sum of all $\alpha_j$ values, denoted as $\sum_{j = 1}^{C} \alpha_j$, sums to 1.
 
@@
 Random masking involves randomly obscuring parts of the input data, forcing the model to learn other relevant features that enhance its predictive capabilities during training.
+50 rectangular masks with random sizes between 80 and 120 were positioned randomly.
 The result of applying data augmentation to an arbitrary example is shown in Fig.
@@
 {./figures/data_aug.pdf}
-\caption{Data augmentation is utilized on an input (a) and its corresponding
-labeled segmentation map (b). The zoomed-in views of (a) and (b) are represented
-by (c) and (d), respectively. The segmentation label distinguishes red pixels as
-peaks and blue pixels as artifact scattering, attributed to ``nozzle scattering"
-in this particular scenario.}
+\caption{Illustration of data augmentation on an input image. (a) Augmented
+image with random in-plane rotation, shift, and masking. (b) its corresponding
+labeled segmentation map. (c, d) Zoomed-in views of (a) and (b), respectively.
+The segmentation label distinguishes red pixels as peaks and blue pixels as
+artifact scattering, attributed to scattering from metal shielding and injection
+nozzle.}
 \label{fig : data aug}
@@
 {./figures/data_engine.pdf}
-\caption{The process of iterative dataset and model improvement.}
+\caption{The three step process of iterative dataset and model improvement.
+(1) Model learns from training data.
+(2) Model predictions reveal potential areas of improvement.
+(3) Correct low-quality training labels or acquire additional examples of challenging instances.}
 \label{fig : data engine}
@@
 The primary goal of \peaknet{} is to autonomously detect Bragg peaks in diffraction images, devoid of any user input, such as algorithmic parameter tuning or manual artifact masking.
-We implemented a two-step approach for peak detection, employing deep neural networks to perform semantic segmentation, which was subsequently followed by connected component analysis to extract image coordinates of Bragg peaks from the generated segmentation maps.
+We implemented a two-step approach for peak detection, employing deep neural networks to perform semantic segmentation, which was subsequently followed by connected component analysis to extract image coordinates of Bragg peaks.
 In this section, we begin by introducing the datasets used for training, validating, and testing \peaknet{}.
@@
 
-The dataset ``mfx13016" exhibits a notable characteristic of prominent nozzle scattering rings accompanied by bright Bragg peak-like spots located on the rings.
-This characteristic presents two primary challenges for crystallography data analysis: increased difficulty in crystal indexing and misleading integration results caused by artifact scattering.
-The current best practice involves manual masking of these artifact scattering, enabling data analysis to proceed as if they are absent, but this process is prone to errors and time-consuming.
+The dataset ``mfx13016" exhibits a notable ring-like background scattering accompanied by bright Bragg peak-like spots located on the rings.
+This characteristic presents two primary challenges for crystallography data analysis: increased difficulty in crystal indexing due to false-positive peaks and inaccurate integration results caused by artifact scattering.
+The current best practice involves manual masking of these artifact scattering, enabling data analysis to proceed as if they are absent, but this process is time-consuming and can not adjust to shot-to-shot variations in the artifacts in real-time.
 Additionally, the final outcomes often hinge on the expertise of the individuals conducting the data processing, resulting in biases, scalability limitations, lack of standardization, and the possibility of human errors.
-Nevertheless, the inherent challenges presented by this dataset offer an exceptional opportunity to testify the autonomous peak finding capability of \peaknet{}.
+Nevertheless, the inherent challenges presented by this dataset offer an exceptional opportunity to showcase the autonomous peak finding capability of \peaknet{}.
 
@@
 
-The peak finding performance of peak finders is evaluated through two significant indicators from a user's standpoint: the number of successfully indexed hits and the merging statistics.
+The peak finding performance of peak finders is evaluated through three key indicators from a user's standpoint: the number of successfully indexed hits, the indexing rate, and the merging statistics.
 For our evaluation, we utilized the CrystFEL software suite \citep{whiteCrystFELSoftwareSuite2012} to perform crystal indexing, integration, and merging tasks.
@@
 
-\peaknet{} and \psocake{}, when manually fine-tuned, exhibit comparable peak finding performance in terms of the number of hits and the number of indexed images, as shown in Table \ref{tb : index}.
-However, it is critical to emphasize that while \peaknet{} operates entirely autonomously, \psocake{}'s performance is contingent upon manual parameter fine-tuning and manual artifact scattering masking.
-For example, an earlier work \citep{suSerialCrystallographyUsing2021}, which processed essentially the same experimental data, reported significantly lower hit count and indexed image count.
-Consequently, this highlights \peaknet{}'s advantage in user-independent data processing.
+\peaknet{} and manually fine-tuned \psocake{} exhibit comparable peak finding performance in terms of the number of hits and the number of indexed images, as shown in Table \ref{tb : index}.
+However, we emphasize that while \peaknet{} operates entirely autonomously, \psocake{}'s performance is contingent upon manual parameter fine-tuning and manual artifact scattering masking.
+For example, an earlier work \citep{suSerialCrystallographyUsing2021}, which processed the same experimental data, reported significantly lower hit count and indexed image count.
+Consequently, this highlights \peaknet{}'s advantage in user-independent expert-level data processing.
 
@@
 Both metrics jointly offer a more comprehensive evaluation of the peak finding method.
-In the case of \peaknet{}, both the consistently high number of indexed images and the good indexing rate testify to its effective and reliable autonomous peak finding process, positioning it as a highly viable option for Bragg peak finding.
+In the case of \peaknet{}, both consistently high number of indexed images and high indexing rate testify to its effective and reliable autonomous peak finding process.
 
@@
 \multicolumn{1}{l}{Methods}                                                                            & \multicolumn{1}{l}{Run (Samples)}        & \multicolumn{1}{l}{31 (TH)} & \multicolumn{1}{l}{32 (TH)} & \multicolumn{1}{l}{33 (TH)} & \multicolumn{1}{l}{34 (TH)} & \multicolumn{1}{l}{36 (TH)} & \multicolumn{1}{l}{37 (PK)} & 38 (PK) \\ \hline
-\multicolumn{1}{l}{\multirow{3}{*}{\peaknet{}}}                                                        & \multicolumn{1}{l}{Number of hits}       & \multicolumn{1}{l}{1205}    & \multicolumn{1}{l}{3248}    & \multicolumn{1}{l}{5797}    & \multicolumn{1}{l}{3949}    & \multicolumn{1}{l}{1184}    & \multicolumn{1}{l}{1030}    & 1223    \\ \cline{2-9}
-\multicolumn{1}{l}{}                                                                                   & \multicolumn{1}{l}{Number of indexed}    & \multicolumn{1}{l}{860}     & \multicolumn{1}{l}{2856}    & \multicolumn{1}{l}{3433}    & \multicolumn{1}{l}{2401}    & \multicolumn{1}{l}{919}     & \multicolumn{1}{l}{953}     & 1169    \\ \cline{2-9}
-\multicolumn{1}{l}{}                                                                                   & \multicolumn{1}{l}{Indexing rate}        & \multicolumn{1}{l}{0.71}    & \multicolumn{1}{l}{0.88}    & \multicolumn{1}{l}{0.59}    & \multicolumn{1}{l}{0.61}    & \multicolumn{1}{l}{0.78}    & \multicolumn{1}{l}{0.93}    & 0.96    \\ \hline
+\multicolumn{1}{l}{\multirow{3}{*}{\peaknet{}}}                                                        & \multicolumn{1}{l}{Number of hits}       & \multicolumn{1}{l}{\textbf{1205}}    & \multicolumn{1}{l}{\textbf{3248}}    & \multicolumn{1}{l}{\textbf{5797}}    & \multicolumn{1}{l}{\textbf{3949}}    & \multicolumn{1}{l}{\textbf{1184}}    & \multicolumn{1}{l}{1030}    & \textbf{1223}    \\ \cline{2-9}
+\multicolumn{1}{l}{}                                                                                   & \multicolumn{1}{l}{Number of indexed}    & \multicolumn{1}{l}{\textbf{860}}     & \multicolumn{1}{l}{\textbf{2856}}    & \multicolumn{1}{l}{\textbf{3433}}    & \multicolumn{1}{l}{\textbf{2401}}    & \multicolumn{1}{l}{\textbf{919}}     & \multicolumn{1}{l}{953}     & 1169    \\ \cline{2-9}
+\multicolumn{1}{l}{}                                                                                   & \multicolumn{1}{l}{Indexing rate}        & \multicolumn{1}{l}{\textbf{0.71}}    & \multicolumn{1}{l}{\textbf{0.88}}    & \multicolumn{1}{l}{\textbf{0.59}}    & \multicolumn{1}{l}{\textbf{0.61}}    & \multicolumn{1}{l}{0.78}    & \multicolumn{1}{l}{0.93}    & 0.96    \\ \hline
 \multicolumn{9}{l}{}                                                                                                                                                                                                                                                                                                                                \\ \hline
-\multicolumn{1}{l}{\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}\psocake{}\\ (fine-tuned)\end{tabular}}} & \multicolumn{1}{l}{Number of hits}       & \multicolumn{1}{l}{1193}    & \multicolumn{1}{l}{3087}    & \multicolumn{1}{l}{5769}    & \multicolumn{1}{l}{3926}    & \multicolumn{1}{l}{917}     & \multicolumn{1}{l}{1070}    & 1212    \\ \cline{2-9}
-\multicolumn{1}{l}{}                                                                                   & \multicolumn{1}{l}{Number of indexed}    & \multicolumn{1}{l}{849}     & \multicolumn{1}{l}{2657}    & \multicolumn{1}{l}{3375}    & \multicolumn{1}{l}{2364}    & \multicolumn{1}{l}{760}     & \multicolumn{1}{l}{1005}    & 1202    \\ \cline{2-9}
-\multicolumn{1}{l}{}                                                                                   & \multicolumn{1}{l}{Indexing rate}        & \multicolumn{1}{l}{0.71}    & \multicolumn{1}{l}{0.86}    & \multicolumn{1}{l}{0.59}    & \multicolumn{1}{l}{0.6}     & \multicolumn{1}{l}{0.83}    & \multicolumn{1}{l}{0.94}    & 0.99    \\ \hline
+\multicolumn{1}{l}{\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}\psocake{}\\ (fine-tuned)\end{tabular}}} & \multicolumn{1}{l}{Number of hits}       & \multicolumn{1}{l}{1193}    & \multicolumn{1}{l}{3087}    & \multicolumn{1}{l}{5769}    & \multicolumn{1}{l}{3926}    & \multicolumn{1}{l}{917}     & \multicolumn{1}{l}{\textbf{1070}}    & 1212    \\ \cline{2-9}
+\multicolumn{1}{l}{}                                                                                   & \multicolumn{1}{l}{Number of indexed}    & \multicolumn{1}{l}{849}     & \multicolumn{1}{l}{2657}    & \multicolumn{1}{l}{3375}    & \multicolumn{1}{l}{2364}    & \multicolumn{1}{l}{760}     & \multicolumn{1}{l}{\textbf{1005}}    & \textbf{1202}    \\ \cline{2-9}
+\multicolumn{1}{l}{}                                                                                   & \multicolumn{1}{l}{Indexing rate}        & \multicolumn{1}{l}{\textbf{0.71}}    & \multicolumn{1}{l}{0.86}    & \multicolumn{1}{l}{\textbf{0.59}}    & \multicolumn{1}{l}{0.60}     & \multicolumn{1}{l}{\textbf{0.83}}    & \multicolumn{1}{l}{\textbf{0.94}}    & \textbf{0.99}    \\ \hline
 \multicolumn{9}{l}{}                                                                                                                                                                                                                                                                                                                                \\ \hline
@@
 For the thaumatin (TH) sample, \peaknet{} demonstrates marginally superior performance in terms of R-split values, correlation coefficients, $I/\sigma(I)$ values, redundancy, and completeness, achieving these results autonomously.
-Notably, the R-split value for the TH sample is slightly lower for \peaknet{} (0.2605 vs.
+Notably, the R-split value for thaumatin is slightly lower for \peaknet{} (0.2605 vs.
 0.2732), suggesting slightly better internal consistency.
@@
 \begin{table*}
-\caption{Merging statistics (TH: thaumatin; PK: proteinase).  TH results were
-merged from run 31, 32, 33, 34 and 36, whereas PK results were merged from run
+\caption{Comparison of merging statistics between \peaknet{} and fine-tuned \psocake{}.  Thaumatin (TH) results were
+merged from run 31, 32, 33, 34 and 36. Proteinase (PK) results were merged from run
 37 and 38.}
@@
 Sample              & Methods & R-split & CC$_{1/2}$     & CC*       & $I/\sigma(I)$   & Resolution range (Å) & Redundancy & Completeness \\ \hline
-\multirow{2}{*}{TH} & \peaknet{} & 0.2605  & 0.9434 & 0.9853 & 2.0590 & 1.45-27.93           & 76.05      & 0.9594       \\ \cline{2-9} 
-                    & \psocake{} & 0.2732  & 0.9368 & 0.9835 & 2.0277 & 1.01-31.32           & 72.20      & 0.9367       \\ \hline
+\multirow{2}{*}{TH} & \peaknet{} & \textbf{0.2605}  & \textbf{0.9434} & \textbf{0.9853} & \textbf{2.0590} & 1.45-27.93           & \textbf{76.05}      & \textbf{0.9594}       \\ \cline{2-9} 
+                    & \psocake{} & 0.2732  & 0.9368 & 0.9835 & 2.0277 & \textbf{1.01-31.32}           & 72.20      & 0.9367       \\ \hline
                     &         &         &           &           &          &                      &            &              \\ \hline
 Sample              & Methods & R-split & CC$_{1/2}$     & CC*       & $I/\sigma(I)$   & Resolution range (Å) & Redundancy & Completeness \\ \hline
-\multirow{2}{*}{PK} & \peaknet{} & 0.7711  & 0.2234    & 0.6043    & 1.135    & 1.45-26.98           & 16.36      & 0.8668       \\ \cline{2-9} 
-                    & \psocake{} & 0.7589  & 0.1900    & 0.5650    & 0.974    & 1.45-30.04           & 17.83      & 0.8365       \\ \hline
+\multirow{2}{*}{PK} & \peaknet{} & 0.7711  & \textbf{0.2234}    & \textbf{0.6043}    & \textbf{1.135}    & 1.45-26.98           & 16.36      & \textbf{0.8668}       \\ \cline{2-9} 
+                    & \psocake{} & \textbf{0.7589}  & 0.1900    & 0.5650    & 0.974    & \textbf{1.45-30.04}           & \textbf{17.83}      & 0.8365       \\ \hline
 \end{tabular}
@@
 
-\subsection{Auto-masking: predicting artifact scattering patterns}
+\subsection{Auto-masking: predicting scattering artifacts}
 
-The integration of the ``auto-masking" functionality in \peaknet{} represents a notable advancement in the automated processing of diffraction images.
-The underlying neural network architecture enables \peaknet{} to autonomously discern and segregate pixel regions affected by artifact scattering, such as these appearing as distinct ring-like structures induced by liquid jet nozzle scattering.
-This capability circumvents the need for manual masking in the peak finding process, thereby optimizing the efficiency of crystallographic data processing.
+Auto-masking functionality in \peaknet{} represents a significant advancement in the automated processing of diffraction images.
+The underlying neural network architecture enables \peaknet{} to autonomously discern and segregate pixel regions affected by scattering artifacts, such as distinct ring-like structures produced by metal shielding used to reduce air scatter and/or liquid jet nozzle scattering.
+This capability circumvents the need for manual masking in the peak finding process and the need to store a binary mask used for each event which is needed for crystal indexing/integration, thereby optimizing the efficiency of crystallographic data processing.
 
 Fig.
-\ref{fig : automask 1} provides a comparative visualization of \peaknet{}'s effectiveness in accurately segmenting regions with bright pixels induced by artifact scattering under various conditions.
-Images without artifact ring structures are also included in the visualization, reassuring that \peaknet{} does not generate or ``hallucinate" artifact rings where they do not exist.
+\ref{fig : automask 1} provides a comparative visualization of \peaknet{}'s effectiveness in accurately segmenting regions with bright pixels induced by scattering artifacts under various conditions.
+Images without ring artifacts are also included in the visualization, reassuring that \peaknet{} does not generate or ``hallucinate" ring artifacts where they do not exist.
 This visual representation serves as tangible evidence of \peaknet{} 's adeptness in discriminating and processing pertinent features, regardless of the contextual complexities.
 
-Furthermore, while evaluating \peaknet{}'s ``auto-masking" feature on intended input images, we explored its behavior on unintended inputs, providing insights into its robustness and generalizability.
+Furthermore, while evaluating \peaknet{}'s auto-masking feature on intended input images, we explored its behavior on unintended inputs, providing insights into its robustness and generalizability.
 Fig.
-\ref{fig : automask 2} depicts illustrative examples of \peaknet{} predicting artifact scattering patterns in Ag Behenate scattering captured on various detectors.
-Surprisingly, \peaknet{} reliably identifies the characteristic scattering ring structures present in Ag Behenate images.
+\ref{fig : automask 2} depicts illustrative examples of \peaknet{} predicting artifact scattering patterns in silver behenate scattering captured on various detectors.
+Silver behenate is a popular calibrant used to determine the detector position relative to the beam based on the known ring spacing.
+Surprisingly, \peaknet{} reliably identifies the characteristic scattering ring structures present in silver behenate images.
 This observation provides compelling evidence once again, further demonstrating the robust predictive capability of \peaknet{} in accurately recognizing artifact scattering patterns.
-As a result, it reinforces that effectiveness of \peaknet{}'s ``auto-masking" feature.
+As a result, it reinforces that effectiveness of \peaknet{}'s auto-masking feature and the potential to automatically optimize the diffraction geometry.
 
@@
 {./figures/automask.agbehnate.pdf}
-\caption{Examples of identifying scattering rings in Ag Behenate images using
+\caption{Examples of identifying scattering rings in silver behenate images using
 \peaknet{}.}
@@
 
-Peak finding can pose significant computational demands, particularly in high data rate experiments, highlighting the critical importance of an efficient peak finding algorithm.
-A comparative analysis of runtime performance demonstrates the greater efficiency of \peaknet{} compared to other commonly used peak finders like the one within \psocake{}.
+Peak finding can pose a significant computational demand, particularly in high data rate experiments, highlighting the critical importance of an efficient peak finding algorithm.
+A comparative analysis of runtime performance demonstrates the greater efficiency of \peaknet{} compared to other commonly used \psocake{} peak finder.
 
-When processing Rayonix images with a resolution of $1920 \times 1920$, \peaknet{} achieved a significantly reduced processing time of 90 milliseconds per event on an NVIDIA 1080 Ti GPU.
-In contrast, \psocake{} required 176 milliseconds per event when executed on an Intel E5-2620.
-Another peak finding method, RPF (robust peak finder), operating on Intel E5-2698, is reported to require 120.0 milliseconds but on smaller AGIPD 1M images with the size of $1024 \times 1024$ \citep{hadian-jaziDataReductionSerial2021}.
+When processing Rayonix images with $1920 \times 1920$ pixels, \peaknet{} achieved a significantly reduced processing time of 90 milliseconds per event on an NVIDIA 1080 Ti GPU.
+In contrast, \psocake{} required 176 milliseconds per event when executed on an Intel E5-2620 CPU.
+Another peak finding method, RPF (robust peak finder), operating on Intel E5-2698, is reported to require 120 milliseconds but on a smaller AGIPD 1M images \citep{hadian-jaziDataReductionSerial2021}.
 This result clearly demonstrates that \peaknet{} not only delivers robust Bragg peak finding results in an autonomous fashion, but also exhibits remarkable runtime efficiency.
-This establishes it as a highly competent tool for real-time autonomous Bragg peak finding.
+%This establishes it as a highly competent tool for real-time autonomous Bragg peak finding.
 
@@
 
-\peaknet{} exhibits exceptional capabilities in autonomous Bragg peaks finding without requiring user input or intervention, such as algorithmic parameter tuning or manual artifact scattering masking.
+\peaknet{} exhibits exceptional capabilities in autonomous Bragg peaks finding without requiring user input or intervention, such as algorithmic parameter tuning or manual artifact masking.
 The predictive performance of \peaknet{} in peak finding proves to be comparable to, if not better than, manually fine-tuned \psocake{} with user-supplied masks.
@@
 
-Earlier versions utilizing the original U-Net model were built and tested by P.L under the supervision of C.H.Y.
+Earlier versions utilizing YOLO and U-Net models were built and tested by P.L and C.H.Y.
 The experiments were designed by C.W with inputs from J.B.T and C.H.Y.

### 2023-06-28 manuscript.tex
Update minor math notation.

@@
 $\gamma$ is a parameter controlling the extent to which the weight of well-classified examples, such as background pixels, is reduced.
-In our neural network training, we chose $\gamma = 2.0$, essentially, this means $(1-\hat{p} _j^{(i)}) ^\gamma$ is solely responsible for down-weighting easy examples, as $\hat{p} _j^{(i)}$ is usually large in this case.
+In our neural network training, we chose $\gamma = 2.0$, essentially, this means $(1-\hat{p}_j^{(i)}) ^\gamma$ is solely responsible for down-weighting easy examples, as $\hat{p}_j^{(i)}$ is usually large in this case.
 Finding the ideal values for $\alpha$ can be a delicate process with only marginal returns, as highlighted in the original focal loss study \citep{linFocalLossDense2018}.

### 2023-06-28 manuscript.natcomm.tex
Support natcomm submission.

--- 2023-06-28 manuscript.tex
@@
 
-\usepackage{style}      % Custom style
-\usepackage{more}
-\usepackage{constants}  % Load constants
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PREFERENCES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% set margin specifics
+\usepackage[a4paper, total={6.5in, 9in}]{geometry}
+
+% set unicode
+\usepackage[utf8]{inputenc}
+
+% set indent for paragraph
+\setlength{\parindent}{2em}
+
+% set graphics support
+\usepackage{graphicx}
+
+% setting line spaceing
+\renewcommand{\baselinestretch}{2.0}
+
+% use boldface in latex equation
+\usepackage{bm}
+
+% Extra math feature
+\usepackage{amssymb}
+\usepackage{amsmath}
+
+% Code block
+\usepackage{listings}
+\lstset{
+    basicstyle=\footnotesize\ttfamily,
+    breaklines=true,
+}
+
+% Set the font for lstinline
+\makeatletter
+\lstdefinestyle{lststyle}{
+  basicstyle=%
+    \ttfamily
+    \color{black}%
+    \lst@ifdisplaystyle\scriptsize\fi
+}
+\makeatother
+\lstset{style=lststyle}
+
+% Color
+\usepackage{xcolor}
+
+% A better enumerate tool that allows changing the label of item
+% It has compatibility issue with beamer;
+\usepackage{enumitem}
+
+% Use emojis
+\usepackage{pifont}
+\usepackage{wasysym}
+
+% No indent
+\setlength{\parindent}{0cm}
+
+% Include picture environment
+\usepackage[calc]{picture}
+
+% Include TikZ environment
+\usepackage{tikz}
+\usepackage{calc}
+
+% Include caption
+\usepackage{caption}    % !!! For new document
+%% \usepackage{caption2}   % !!! Support old document
+\usepackage{float}
+
+% Include natbib
+\usepackage{natbib}
+%% \setcitestyle{authoryear,round}    % Use authoryear format
+
+% Workaround to display bold font in math mode
+% Source: https://tex.stackexchange.com/questions/565069/beamer-bold-math-no-longer-working
+\DeclareFontShape{OT1}{cmss}{b}{n}{<->ssub * cmss/bx/n}{}
+
+%% \usepackage{setspace}
+%% \doublespacing
+
+% To make multirow tables
+\usepackage{multirow}
+
+% Use author blocks
+\usepackage{authblk}
+
+\newcommand{\PeakNet}{PeakNet}
+\newcommand{\peaknet}{PeakNet}
+\newcommand{\psocake}{Psocake}
+\newcommand{\etal}{\textit{et al}.}
+\newcommand{\beSpecific}[1]{(\colorbox{yellow!30}{#1})}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 BraggNet \citep{sullivanBraggNetIntegratingBragg2019} is the first method that demonstrates proficiency of neural network models, specifically U-Net \citep{ronnebergerUNetConvolutionalNetworks2015}, in accurately segmenting peak pixels, including weak peaks, from background pixels in neutron crystallography data.
-Specifically, BraggNet employed simulated peaks to create training datasets, which underwent a number of preprocessing steps, including centering and cropping to a specfic size and adding Poisson noise.
+BraggNet employed simulated peaks to create training datasets, which underwent a number of preprocessing steps, including centering and cropping to a specfic size and adding Poisson noise.
 It should be noted that BraggNet works on a single peak at a time within a small 32 by 32 window, which deviates significantly from conventional Bragg peak finding tasks that require extracting peak positions from images typically with hundreds or thousands of pixels along one dimension.
@@
 
-% Bibliography
-\bibliographystyle{plainnat}
-\bibliography{bibliography}
+\begin{thebibliography}{33}
+\providecommand{\natexlab}[1]{#1}
+\providecommand{\url}[1]{\texttt{#1}}
+\expandafter\ifx\csname urlstyle\endcsname\relax
+  \providecommand{\doi}[1]{doi: #1}\else
+  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi
+
+\bibitem[Allahgholi et~al.(2019)Allahgholi, Becker, Delfs, Dinapoli,
+  Goettlicher, Greiffenberg, Henrich, Hirsemann, Kuhn, Klanner, Klyuev,
+  Krueger, Lange, Laurus, Marras, Mezza, Mozzanica, Niemann, Poehlsen,
+  Schwandt, Sheviakov, Shi, Smoljanin, Steffen, {Sztuk-Dambietz}, Trunk, Xia,
+  Zeribi, Zhang, Zimmer, Schmitt, and
+  Graafsma]{allahgholiAdaptiveGainIntegrating2019}
+Aschkan Allahgholi, Julian Becker, Annette Delfs, Roberto Dinapoli, Peter
+  Goettlicher, Dominic Greiffenberg, Beat Henrich, Helmut Hirsemann, Manuela
+  Kuhn, Robert Klanner, Alexander Klyuev, Hans Krueger, Sabine Lange, Torsten
+  Laurus, Alessandro Marras, Davide Mezza, Aldo Mozzanica, Magdalena Niemann,
+  Jennifer Poehlsen, Joern Schwandt, Igor Sheviakov, Xintian Shi, Sergej
+  Smoljanin, Lothar Steffen, Jolanta {Sztuk-Dambietz}, Ulrich Trunk, Qingqing
+  Xia, Mourad Zeribi, Jiaguo Zhang, Manfred Zimmer, Bernd Schmitt, and Heinz
+  Graafsma.
+\newblock The {{Adaptive Gain Integrating Pixel Detector}} at the {{European
+  XFEL}}.
+\newblock \emph{Journal of Synchrotron Radiation}, 26\penalty0 (1):\penalty0
+  74--82, January 2019.
+\newblock ISSN 1600-5775.
+\newblock \doi{10.1107/S1600577518016077}.
+
+\bibitem[Aquila et~al.(2012)Aquila, Hunter, Doak, Kirian, Fromme, White,
+  Andreasson, Arnlund, Bajt, Barends, Barthelmess, Bogan, Bostedt, Bottin,
+  Bozek, Caleman, Coppola, Davidsson, DePonte, Elser, Epp, Erk, Fleckenstein,
+  Foucar, Frank, Fromme, Graafsma, Grotjohann, Gumprecht, Hajdu, Hampton,
+  Hartmann, Hartmann, {Hau-Riege}, Hauser, Hirsemann, Holl, Holton, H{\"o}mke,
+  Johansson, Kimmel, Kassemeyer, Krasniqi, K{\"u}hnel, Liang, Lomb, Malmerberg,
+  Marchesini, Martin, Maia, Messerschmidt, Nass, Reich, Neutze, Rolles, Rudek,
+  Rudenko, Schlichting, Schmidt, Schmidt, Schulz, Seibert, Shoeman, Sierra,
+  Soltau, Starodub, Stellato, Stern, Str{\"u}der, Timneanu, Ullrich, Wang,
+  Williams, Weidenspointner, Weierstall, Wunderer, Barty, Spence, and
+  Chapman]{aquilaTimeresolvedProteinNanocrystallography2012}
+Andrew Aquila, Mark~S. Hunter, R.~Bruce Doak, Richard~A. Kirian, Petra Fromme,
+  Thomas~A. White, Jakob Andreasson, David Arnlund, Sa{\v s}a Bajt, Thomas
+  R.~M. Barends, Miriam Barthelmess, Michael~J. Bogan, Christoph Bostedt,
+  Herv{\'e} Bottin, John~D. Bozek, Carl Caleman, Nicola Coppola, Jan Davidsson,
+  Daniel~P. DePonte, Veit Elser, Sascha~W. Epp, Benjamin Erk, Holger
+  Fleckenstein, Lutz Foucar, Matthias Frank, Raimund Fromme, Heinz Graafsma,
+  Ingo Grotjohann, Lars Gumprecht, Janos Hajdu, Christina~Y. Hampton, Andreas
+  Hartmann, Robert Hartmann, Stefan {Hau-Riege}, G{\"u}nter Hauser, Helmut
+  Hirsemann, Peter Holl, James~M. Holton, Andr{\'e} H{\"o}mke, Linda Johansson,
+  Nils Kimmel, Stephan Kassemeyer, Faton Krasniqi, Kai-Uwe K{\"u}hnel, Mengning
+  Liang, Lukas Lomb, Erik Malmerberg, Stefano Marchesini, Andrew~V. Martin,
+  Filipe~R.N.C. Maia, Marc Messerschmidt, Karol Nass, Christian Reich, Richard
+  Neutze, Daniel Rolles, Benedikt Rudek, Artem Rudenko, Ilme Schlichting, Carlo
+  Schmidt, Kevin~E. Schmidt, Joachim Schulz, M.~Marvin Seibert, Robert~L.
+  Shoeman, Raymond Sierra, Heike Soltau, Dmitri Starodub, Francesco Stellato,
+  Stephan Stern, Lothar Str{\"u}der, Nicusor Timneanu, Joachim Ullrich, Xiaoyu
+  Wang, Garth~J. Williams, Georg Weidenspointner, Uwe Weierstall, Cornelia
+  Wunderer, Anton Barty, John C.~H. Spence, and Henry~N. Chapman.
+\newblock Time-resolved protein nanocrystallography using an {{X-ray}}
+  free-electron laser.
+\newblock \emph{Optics Express}, 20\penalty0 (3):\penalty0 2706, January 2012.
+\newblock ISSN 1094-4087.
+\newblock \doi{10.1364/OE.20.002706}.
+
+\bibitem[Barty et~al.(2014)Barty, Kirian, Maia, Hantke, Yoon, White, and
+  Chapman]{bartyCheetahSoftwareHighthroughput2014}
+Anton Barty, Richard~A. Kirian, Filipe R. N.~C. Maia, Max Hantke, Chun~Hong
+  Yoon, Thomas~A. White, and Henry Chapman.
+\newblock {\emph{Cheetah}} : Software for high-throughput reduction and
+  analysis of serial femtosecond {{X-ray}} diffraction data.
+\newblock \emph{Journal of Applied Crystallography}, 47\penalty0 (3):\penalty0
+  1118--1131, June 2014.
+\newblock ISSN 1600-5767.
+\newblock \doi{10.1107/S1600576714007626}.
+
+\bibitem[Bolotovsky et~al.(1995)Bolotovsky, White, Darovsky, and
+  Coppens]{bolotovskySeedSkewnessMethodIntegration1995}
+R.~Bolotovsky, M.~A. White, A.~Darovsky, and P.~Coppens.
+\newblock The `{{Seed-Skewness}}' {{Method}} for {{Integration}} of {{Peaks}}
+  on {{Imaging Plates}}.
+\newblock \emph{Journal of Applied Crystallography}, 28\penalty0 (2):\penalty0
+  86--95, April 1995.
+\newblock ISSN 0021-8898.
+\newblock \doi{10.1107/S0021889894009696}.
+
+\bibitem[Chapman et~al.(2006)Chapman, Barty, Bogan, Boutet, Frank, {Hau-Riege},
+  Marchesini, Woods, Bajt, Benner, London, Pl{\"o}njes, Kuhlmann, Treusch,
+  D{\"u}sterer, Tschentscher, Schneider, Spiller, M{\"o}ller, Bostedt, Hoener,
+  Shapiro, Hodgson, {van der Spoel}, Burmeister, Bergh, Caleman, Huldt,
+  Seibert, Maia, Lee, Sz{\"o}ke, Timneanu, and
+  Hajdu]{chapmanFemtosecondDiffractiveImaging2006}
+Henry~N. Chapman, Anton Barty, Michael~J. Bogan, S{\'e}bastien Boutet, Matthias
+  Frank, Stefan~P. {Hau-Riege}, Stefano Marchesini, Bruce~W. Woods, Sa{\v s}a
+  Bajt, W.~Henry Benner, Richard~A. London, Elke Pl{\"o}njes, Marion Kuhlmann,
+  Rolf Treusch, Stefan D{\"u}sterer, Thomas Tschentscher, Jochen~R. Schneider,
+  Eberhard Spiller, Thomas M{\"o}ller, Christoph Bostedt, Matthias Hoener,
+  David~A. Shapiro, Keith~O. Hodgson, David {van der Spoel}, Florian
+  Burmeister, Magnus Bergh, Carl Caleman, G{\"o}sta Huldt, M.~Marvin Seibert,
+  Filipe R. N.~C. Maia, Richard~W. Lee, Abraham Sz{\"o}ke, Nicusor Timneanu,
+  and Janos Hajdu.
+\newblock Femtosecond diffractive imaging with a soft-{{X-ray}} free-electron
+  laser.
+\newblock \emph{Nature Physics}, 2\penalty0 (12):\penalty0 839--843, December
+  2006.
+\newblock ISSN 1745-2473, 1745-2481.
+\newblock \doi{10.1038/nphys461}.
+
+\bibitem[Chapman et~al.(2011)Chapman, Fromme, Barty, White, Kirian, Aquila,
+  Hunter, Schulz, DePonte, Weierstall, Doak, Maia, Martin, Schlichting, Lomb,
+  Coppola, Shoeman, Epp, Hartmann, Rolles, Rudenko, Foucar, Kimmel,
+  Weidenspointner, Holl, Liang, Barthelmess, Caleman, Boutet, Bogan,
+  Krzywinski, Bostedt, Bajt, Gumprecht, Rudek, Erk, Schmidt, H{\"o}mke, Reich,
+  Pietschner, Str{\"u}der, Hauser, Gorke, Ullrich, Herrmann, Schaller,
+  Schopper, Soltau, K{\"u}hnel, Messerschmidt, Bozek, {Hau-Riege}, Frank,
+  Hampton, Sierra, Starodub, Williams, Hajdu, Timneanu, Seibert, Andreasson,
+  Rocker, J{\"o}nsson, Svenda, Stern, Nass, Andritschke, Schr{\"o}ter,
+  Krasniqi, Bott, Schmidt, Wang, Grotjohann, Holton, Barends, Neutze,
+  Marchesini, Fromme, Schorb, Rupp, Adolph, Gorkhover, Andersson, Hirsemann,
+  Potdevin, Graafsma, Nilsson, and Spence]{chapmanFemtosecondXrayProtein2011}
+Henry~N. Chapman, Petra Fromme, Anton Barty, Thomas~A. White, Richard~A.
+  Kirian, Andrew Aquila, Mark~S. Hunter, Joachim Schulz, Daniel~P. DePonte, Uwe
+  Weierstall, R.~Bruce Doak, Filipe R. N.~C. Maia, Andrew~V. Martin, Ilme
+  Schlichting, Lukas Lomb, Nicola Coppola, Robert~L. Shoeman, Sascha~W. Epp,
+  Robert Hartmann, Daniel Rolles, Artem Rudenko, Lutz Foucar, Nils Kimmel,
+  Georg Weidenspointner, Peter Holl, Mengning Liang, Miriam Barthelmess, Carl
+  Caleman, S{\'e}bastien Boutet, Michael~J. Bogan, Jacek Krzywinski, Christoph
+  Bostedt, Sa{\v s}a Bajt, Lars Gumprecht, Benedikt Rudek, Benjamin Erk, Carlo
+  Schmidt, Andr{\'e} H{\"o}mke, Christian Reich, Daniel Pietschner, Lothar
+  Str{\"u}der, G{\"u}nter Hauser, Hubert Gorke, Joachim Ullrich, Sven Herrmann,
+  Gerhard Schaller, Florian Schopper, Heike Soltau, Kai-Uwe K{\"u}hnel, Marc
+  Messerschmidt, John~D. Bozek, Stefan~P. {Hau-Riege}, Matthias Frank,
+  Christina~Y. Hampton, Raymond~G. Sierra, Dmitri Starodub, Garth~J. Williams,
+  Janos Hajdu, Nicusor Timneanu, M.~Marvin Seibert, Jakob Andreasson, Andrea
+  Rocker, Olof J{\"o}nsson, Martin Svenda, Stephan Stern, Karol Nass, Robert
+  Andritschke, Claus-Dieter Schr{\"o}ter, Faton Krasniqi, Mario Bott, Kevin~E.
+  Schmidt, Xiaoyu Wang, Ingo Grotjohann, James~M. Holton, Thomas R.~M. Barends,
+  Richard Neutze, Stefano Marchesini, Raimund Fromme, Sebastian Schorb, Daniela
+  Rupp, Marcus Adolph, Tais Gorkhover, Inger Andersson, Helmut Hirsemann,
+  Guillaume Potdevin, Heinz Graafsma, Bj{\"o}rn Nilsson, and John C.~H. Spence.
+\newblock Femtosecond {{X-ray}} protein nanocrystallography.
+\newblock \emph{Nature}, 470\penalty0 (7332):\penalty0 73--77, February 2011.
+\newblock ISSN 0028-0836, 1476-4687.
+\newblock \doi{10.1038/nature09750}.
+
+\bibitem[{Hadian-Jazi} et~al.(2017){Hadian-Jazi}, Messerschmidt, Darmanin,
+  Giewekemeyer, Mancuso, and Abbey]{hadian-jaziPeakfindingAlgorithmBased2017}
+Marjan {Hadian-Jazi}, Marc Messerschmidt, Connie Darmanin, Klaus Giewekemeyer,
+  Adrian~P. Mancuso, and Brian Abbey.
+\newblock A peak-finding algorithm based on robust statistical analysis in
+  serial crystallography.
+\newblock \emph{Journal of Applied Crystallography}, 50\penalty0 (6):\penalty0
+  1705--1715, December 2017.
+\newblock ISSN 1600-5767.
+\newblock \doi{10.1107/S1600576717014340}.
+
+\bibitem[{Hadian-Jazi} et~al.(2021){Hadian-Jazi}, Sadri, Barty, Yefanov,
+  Galchenkova, Oberthuer, Komadina, Brehm, Kirkwood, Mills, {de Wijn}, Letrun,
+  Kloos, Vakili, Gelisio, Darmanin, Mancuso, Chapman, and
+  Abbey]{hadian-jaziDataReductionSerial2021}
+Marjan {Hadian-Jazi}, Alireza Sadri, Anton Barty, Oleksandr Yefanov, Marina
+  Galchenkova, Dominik Oberthuer, Dana Komadina, Wolfgang Brehm, Henry
+  Kirkwood, Grant Mills, Raphael {de Wijn}, Romain Letrun, Marco Kloos,
+  Mohammad Vakili, Luca Gelisio, Connie Darmanin, Adrian~P. Mancuso, Henry~N.
+  Chapman, and Brian Abbey.
+\newblock Data reduction for serial crystallography using a robust peak finder.
+\newblock \emph{Journal of Applied Crystallography}, 54\penalty0 (5):\penalty0
+  1360--1378, October 2021.
+\newblock ISSN 1600-5767.
+\newblock \doi{10.1107/S1600576721007317}.
+
+\bibitem[He et~al.(2016)He, Zhang, Ren, and Sun]{heDeepResidualLearning2016}
+Kaiming He, Xiangyu Zhang, Shaoqing Ren, and Jian Sun.
+\newblock Deep {{Residual Learning}} for {{Image Recognition}}.
+\newblock In \emph{2016 {{IEEE Conference}} on {{Computer Vision}} and
+  {{Pattern Recognition}} ({{CVPR}})}, pages 770--778, {Las Vegas, NV, USA},
+  June 2016. {IEEE}.
+\newblock ISBN 978-1-4673-8851-1.
+\newblock \doi{10.1109/CVPR.2016.90}.
+
+\bibitem[Ibrahim et~al.(2020)Ibrahim, Fransson, Chatterjee, Cheah, Hussein,
+  Lassalle, Sutherlin, Young, Fuller, Gul, Kim, Simon, {de Lichtenberg},
+  Chernev, Bogacz, Pham, Orville, Saichek, Northen, Batyuk, Carbajo,
+  {Alonso-Mori}, Tono, Owada, Bhowmick, Bolotovsky, Mendez, Moriarty, Holton,
+  Dobbek, Brewster, Adams, Sauter, Bergmann, Zouni, Messinger, Kern, Yachandra,
+  and Yano]{ibrahimUntanglingSequenceEvents2020}
+Mohamed Ibrahim, Thomas Fransson, Ruchira Chatterjee, Mun~Hon Cheah, Rana
+  Hussein, Louise Lassalle, Kyle~D. Sutherlin, Iris~D. Young, Franklin~D.
+  Fuller, Sheraz Gul, In-Sik Kim, Philipp~S. Simon, Casper {de Lichtenberg},
+  Petko Chernev, Isabel Bogacz, Cindy~C. Pham, Allen~M. Orville, Nicholas
+  Saichek, Trent Northen, Alexander Batyuk, Sergio Carbajo, Roberto
+  {Alonso-Mori}, Kensuke Tono, Shigeki Owada, Asmit Bhowmick, Robert
+  Bolotovsky, Derek Mendez, Nigel~W. Moriarty, James~M. Holton, Holger Dobbek,
+  Aaron~S. Brewster, Paul~D. Adams, Nicholas~K. Sauter, Uwe Bergmann, Athina
+  Zouni, Johannes Messinger, Jan Kern, Vittal~K. Yachandra, and Junko Yano.
+\newblock Untangling the sequence of events during the {{S}}
+  {\textsubscript{2}} \textrightarrow{} {{S}} {\textsubscript{3}} transition in
+  photosystem {{II}} and implications for the water oxidation mechanism.
+\newblock \emph{Proceedings of the National Academy of Sciences}, 117\penalty0
+  (23):\penalty0 12624--12635, June 2020.
+\newblock ISSN 0027-8424, 1091-6490.
+\newblock \doi{10.1073/pnas.2000529117}.
+
+\bibitem[Ke et~al.(2018)Ke, Brewster, Yu, Ushizima, Yang, and
+  Sauter]{keConvolutionalNeuralNetworkbased2018}
+Tsung-Wei Ke, Aaron~S. Brewster, Stella~X. Yu, Daniela Ushizima, Chao Yang, and
+  Nicholas~K. Sauter.
+\newblock A convolutional neural network-based screening tool for {{X-ray}}
+  serial crystallography.
+\newblock \emph{Journal of Synchrotron Radiation}, 25\penalty0 (3):\penalty0
+  655--670, May 2018.
+\newblock ISSN 1600-5775.
+\newblock \doi{10.1107/S1600577518004873}.
+
+\bibitem[Kern et~al.(2018)Kern, Chatterjee, Young, Fuller, Lassalle, Ibrahim,
+  Gul, Fransson, Brewster, {Alonso-Mori}, Hussein, Zhang, Douthit, {de
+  Lichtenberg}, Cheah, Shevela, Wersig, Seuffert, Sokaras, Pastor, Weninger,
+  Kroll, Sierra, Aller, Butryn, Orville, Liang, Batyuk, Koglin, Carbajo,
+  Boutet, Moriarty, Holton, Dobbek, Adams, Bergmann, Sauter, Zouni, Messinger,
+  Yano, and Yachandra]{kernStructuresIntermediatesKok2018}
+Jan Kern, Ruchira Chatterjee, Iris~D. Young, Franklin~D. Fuller, Louise
+  Lassalle, Mohamed Ibrahim, Sheraz Gul, Thomas Fransson, Aaron~S. Brewster,
+  Roberto {Alonso-Mori}, Rana Hussein, Miao Zhang, Lacey Douthit, Casper {de
+  Lichtenberg}, Mun~Hon Cheah, Dmitry Shevela, Julia Wersig, Ina Seuffert,
+  Dimosthenis Sokaras, Ernest Pastor, Clemens Weninger, Thomas Kroll,
+  Raymond~G. Sierra, Pierre Aller, Agata Butryn, Allen~M. Orville, Mengning
+  Liang, Alexander Batyuk, Jason~E. Koglin, Sergio Carbajo, S{\'e}bastien
+  Boutet, Nigel~W. Moriarty, James~M. Holton, Holger Dobbek, Paul~D. Adams, Uwe
+  Bergmann, Nicholas~K. Sauter, Athina Zouni, Johannes Messinger, Junko Yano,
+  and Vittal~K. Yachandra.
+\newblock Structures of the intermediates of {{Kok}}'s photosynthetic water
+  oxidation clock.
+\newblock \emph{Nature}, 563\penalty0 (7731):\penalty0 421--425, November 2018.
+\newblock ISSN 0028-0836, 1476-4687.
+\newblock \doi{10.1038/s41586-018-0681-2}.
+
+\bibitem[Kupitz et~al.(2014)Kupitz, Basu, Grotjohann, Fromme, Zatsepin, Rendek,
+  Hunter, Shoeman, White, Wang, James, Yang, Cobb, Reeder, Sierra, Liu, Barty,
+  Aquila, Deponte, Kirian, Bari, Bergkamp, Beyerlein, Bogan, Caleman, Chao,
+  Conrad, Davis, Fleckenstein, Galli, {Hau-Riege}, Kassemeyer, Laksmono, Liang,
+  Lomb, Marchesini, Martin, Messerschmidt, Milathianaki, Nass, Ros,
+  {Roy-Chowdhury}, Schmidt, Seibert, Steinbrener, Stellato, Yan, Yoon, Moore,
+  Moore, Pushkar, Williams, Boutet, Doak, Weierstall, Frank, Chapman, Spence,
+  and Fromme]{kupitzSerialTimeresolvedCrystallography2014}
+Christopher Kupitz, Shibom Basu, Ingo Grotjohann, Raimund Fromme, Nadia~A.
+  Zatsepin, Kimberly~N. Rendek, Mark~S. Hunter, Robert~L. Shoeman, Thomas~A.
+  White, Dingjie Wang, Daniel James, Jay-How Yang, Danielle~E. Cobb, Brenda
+  Reeder, Raymond~G. Sierra, Haiguang Liu, Anton Barty, Andrew~L. Aquila,
+  Daniel Deponte, Richard~A. Kirian, Sadia Bari, Jesse~J. Bergkamp, Kenneth~R.
+  Beyerlein, Michael~J. Bogan, Carl Caleman, Tzu-Chiao Chao, Chelsie~E. Conrad,
+  Katherine~M. Davis, Holger Fleckenstein, Lorenzo Galli, Stefan~P.
+  {Hau-Riege}, Stephan Kassemeyer, Hartawan Laksmono, Mengning Liang, Lukas
+  Lomb, Stefano Marchesini, Andrew~V. Martin, Marc Messerschmidt, Despina
+  Milathianaki, Karol Nass, Alexandra Ros, Shatabdi {Roy-Chowdhury}, Kevin
+  Schmidt, Marvin Seibert, Jan Steinbrener, Francesco Stellato, Lifen Yan,
+  Chunhong Yoon, Thomas~A. Moore, Ana~L. Moore, Yulia Pushkar, Garth~J.
+  Williams, S{\'e}bastien Boutet, R.~Bruce Doak, Uwe Weierstall, Matthias
+  Frank, Henry~N. Chapman, John C.~H. Spence, and Petra Fromme.
+\newblock Serial time-resolved crystallography of photosystem {{II}} using a
+  femtosecond {{X-ray}} laser.
+\newblock \emph{Nature}, 513\penalty0 (7517):\penalty0 261--265, September
+  2014.
+\newblock ISSN 0028-0836, 1476-4687.
+\newblock \doi{10.1038/nature13453}.
+
+\bibitem[Lin et~al.(2017)Lin, Doll{\'a}r, Girshick, He, Hariharan, and
+  Belongie]{linFeaturePyramidNetworks2017}
+Tsung-Yi Lin, Piotr Doll{\'a}r, Ross Girshick, Kaiming He, Bharath Hariharan,
+  and Serge Belongie.
+\newblock Feature {{Pyramid Networks}} for {{Object Detection}}, April 2017.
+
+\bibitem[Lin et~al.(2018)Lin, Goyal, Girshick, He, and
+  Doll{\'a}r]{linFocalLossDense2018}
+Tsung-Yi Lin, Priya Goyal, Ross Girshick, Kaiming He, and Piotr Doll{\'a}r.
+\newblock Focal {{Loss}} for {{Dense Object Detection}}, February 2018.
+
+\bibitem[Liu et~al.(2021)Liu, Sharma, Park, Kenesei, Miceli, Almer, Kettimuthu,
+  and Foster]{liuBraggNNFastXray2021}
+Zhengchun Liu, Hemant Sharma, Jun-Sang Park, Peter Kenesei, Antonino Miceli,
+  Jonathan Almer, Rajkumar Kettimuthu, and Ian Foster.
+\newblock {{BraggNN}}: {{Fast X-ray Bragg Peak Analysis Using Deep Learning}}.
+\newblock \emph{arXiv:2008.08198 [cs, eess]}, June 2021.
+
+\bibitem[Nango et~al.(2016)Nango, Royant, Kubo, Nakane, Wickstrand, Kimura,
+  Tanaka, Tono, Song, Tanaka, Arima, Yamashita, Kobayashi, Hosaka, Mizohata,
+  Nogly, Sugahara, Nam, Nomura, Shimamura, Im, Fujiwara, Yamanaka, Jeon,
+  Nishizawa, Oda, Fukuda, Andersson, B{\aa}th, Dods, Davidsson, Matsuoka,
+  Kawatake, Murata, Nureki, Owada, Kameshima, Hatsui, Joti, Schertler, Yabashi,
+  Bondar, Standfuss, Neutze, and
+  Iwata]{nangoThreedimensionalMovieStructural2016}
+Eriko Nango, Antoine Royant, Minoru Kubo, Takanori Nakane, Cecilia Wickstrand,
+  Tetsunari Kimura, Tomoyuki Tanaka, Kensuke Tono, Changyong Song, Rie Tanaka,
+  Toshi Arima, Ayumi Yamashita, Jun Kobayashi, Toshiaki Hosaka, Eiichi
+  Mizohata, Przemyslaw Nogly, Michihiro Sugahara, Daewoong Nam, Takashi Nomura,
+  Tatsuro Shimamura, Dohyun Im, Takaaki Fujiwara, Yasuaki Yamanaka, Byeonghyun
+  Jeon, Tomohiro Nishizawa, Kazumasa Oda, Masahiro Fukuda, Rebecka Andersson,
+  Petra B{\aa}th, Robert Dods, Jan Davidsson, Shigeru Matsuoka, Satoshi
+  Kawatake, Michio Murata, Osamu Nureki, Shigeki Owada, Takashi Kameshima,
+  Takaki Hatsui, Yasumasa Joti, Gebhard Schertler, Makina Yabashi, Ana-Nicoleta
+  Bondar, J{\"o}rg Standfuss, Richard Neutze, and So~Iwata.
+\newblock A three-dimensional movie of structural changes in bacteriorhodopsin.
+\newblock \emph{Science}, 354\penalty0 (6319):\penalty0 1552--1557, December
+  2016.
+\newblock ISSN 0036-8075, 1095-9203.
+\newblock \doi{10.1126/science.aah3497}.
+
+\bibitem[Neutze et~al.(2000)Neutze, Wouts, {van der Spoel}, Weckert, and
+  Hajdu]{neutzePotentialBiomolecularImaging2000}
+Richard Neutze, Remco Wouts, David {van der Spoel}, Edgar Weckert, and Janos
+  Hajdu.
+\newblock Potential for biomolecular imaging with femtosecond {{X-ray}} pulses.
+\newblock \emph{Nature}, 406\penalty0 (6797):\penalty0 752--757, August 2000.
+\newblock ISSN 0028-0836, 1476-4687.
+\newblock \doi{10.1038/35021099}.
+
+\bibitem[Oktay et~al.(2018)Oktay, Schlemper, Folgoc, Lee, Heinrich, Misawa,
+  Mori, McDonagh, Hammerla, Kainz, Glocker, and
+  Rueckert]{oktayAttentionUNetLearning2018}
+Ozan Oktay, Jo~Schlemper, Loic~Le Folgoc, Matthew Lee, Mattias Heinrich,
+  Kazunari Misawa, Kensaku Mori, Steven McDonagh, Nils~Y. Hammerla, Bernhard
+  Kainz, Ben Glocker, and Daniel Rueckert.
+\newblock Attention {{U-Net}}: {{Learning Where}} to {{Look}} for the
+  {{Pancreas}}, May 2018.
+
+\bibitem[Pande et~al.(2016)Pande, Hutchison, Groenhof, Aquila, Robinson,
+  Tenboer, Basu, Boutet, DePonte, Liang, White, Zatsepin, Yefanov, Morozov,
+  Oberthuer, Gati, Subramanian, James, Zhao, Koralek, Brayshaw, Kupitz, Conrad,
+  {Roy-Chowdhury}, Coe, Metz, Xavier, Grant, Koglin, Ketawala, Fromme, {\v
+  S}rajer, Henning, Spence, Ourmazd, Schwander, Weierstall, Frank, Fromme,
+  Barty, Chapman, Moffat, {van Thor}, and
+  Schmidt]{pandeFemtosecondStructuralDynamics2016a}
+Kanupriya Pande, Christopher D.~M. Hutchison, Gerrit Groenhof, Andy Aquila,
+  Josef~S. Robinson, Jason Tenboer, Shibom Basu, S{\'e}bastien Boutet,
+  Daniel~P. DePonte, Mengning Liang, Thomas~A. White, Nadia~A. Zatsepin,
+  Oleksandr Yefanov, Dmitry Morozov, Dominik Oberthuer, Cornelius Gati, Ganesh
+  Subramanian, Daniel James, Yun Zhao, Jake Koralek, Jennifer Brayshaw,
+  Christopher Kupitz, Chelsie Conrad, Shatabdi {Roy-Chowdhury}, Jesse~D. Coe,
+  Markus Metz, Paulraj~Lourdu Xavier, Thomas~D. Grant, Jason~E. Koglin, Gihan
+  Ketawala, Raimund Fromme, Vukica {\v S}rajer, Robert Henning, John C.~H.
+  Spence, Abbas Ourmazd, Peter Schwander, Uwe Weierstall, Matthias Frank, Petra
+  Fromme, Anton Barty, Henry~N. Chapman, Keith Moffat, Jasper~J. {van Thor},
+  and Marius Schmidt.
+\newblock Femtosecond structural dynamics drives the trans/cis isomerization in
+  photoactive yellow protein.
+\newblock \emph{Science}, 352\penalty0 (6286):\penalty0 725--729, May 2016.
+\newblock ISSN 0036-8075, 1095-9203.
+\newblock \doi{10.1126/science.aad5081}.
+
+\bibitem[Ronneberger et~al.(2015)Ronneberger, Fischer, and
+  Brox]{ronnebergerUNetConvolutionalNetworks2015}
+Olaf Ronneberger, Philipp Fischer, and Thomas Brox.
+\newblock U-{{Net}}: {{Convolutional Networks}} for {{Biomedical Image
+  Segmentation}}.
+\newblock \emph{arXiv:1505.04597 [cs]}, May 2015.
+
+\bibitem[Shin et~al.(2018)Shin, Kim, and Yoon]{shinDataAnalysisUsing2018}
+Hocheol Shin, Seungnam Kim, and Chun~Hong Yoon.
+\newblock Data {{Analysis}} using {{Psocake}} at {{PAL-XFEL}}.
+\newblock \emph{Journal of the Korean Physical Society}, 73\penalty0
+  (1):\penalty0 16--20, July 2018.
+\newblock ISSN 0374-4884, 1976-8524.
+\newblock \doi{10.3938/jkps.73.16}.
+
+\bibitem[Su et~al.(2021)Su, Cantlon, Douthit, Wiedorn, Boutet, Kern, Yoon, and
+  DePonte]{suSerialCrystallographyUsing2021}
+Zhen Su, Joshua Cantlon, Lacey Douthit, Max Wiedorn, S{\'e}bastien Boutet, Jan
+  Kern, Chun~Hong Yoon, and Daniel DePonte.
+\newblock Serial crystallography using automated drop dispensing.
+\newblock \emph{Journal of Synchrotron Radiation}, 28\penalty0 (5):\penalty0
+  1386--1392, September 2021.
+\newblock ISSN 1600-5775.
+\newblock \doi{10.1107/S1600577521006160}.
+
+\bibitem[Suga et~al.(2017)Suga, Akita, Sugahara, Kubo, Nakajima, Nakane,
+  Yamashita, Umena, Nakabayashi, Yamane, Nakano, Suzuki, Masuda, Inoue, Kimura,
+  Nomura, Yonekura, Yu, Sakamoto, Motomura, Chen, Kato, Noguchi, Tono, Joti,
+  Kameshima, Hatsui, Nango, Tanaka, Naitow, Matsuura, Yamashita, Yamamoto,
+  Nureki, Yabashi, Ishikawa, Iwata, and
+  Shen]{sugaLightinducedStructuralChanges2017}
+Michihiro Suga, Fusamichi Akita, Michihiro Sugahara, Minoru Kubo, Yoshiki
+  Nakajima, Takanori Nakane, Keitaro Yamashita, Yasufumi Umena, Makoto
+  Nakabayashi, Takahiro Yamane, Takamitsu Nakano, Mamoru Suzuki, Tetsuya
+  Masuda, Shigeyuki Inoue, Tetsunari Kimura, Takashi Nomura, Shinichiro
+  Yonekura, Long-Jiang Yu, Tomohiro Sakamoto, Taiki Motomura, Jing-Hua Chen,
+  Yuki Kato, Takumi Noguchi, Kensuke Tono, Yasumasa Joti, Takashi Kameshima,
+  Takaki Hatsui, Eriko Nango, Rie Tanaka, Hisashi Naitow, Yoshinori Matsuura,
+  Ayumi Yamashita, Masaki Yamamoto, Osamu Nureki, Makina Yabashi, Tetsuya
+  Ishikawa, So~Iwata, and Jian-Ren Shen.
+\newblock Light-induced structural changes and the site of {{O}}={{O}} bond
+  formation in {{PSII}} caught by {{XFEL}}.
+\newblock \emph{Nature}, 543\penalty0 (7643):\penalty0 131--135, March 2017.
+\newblock ISSN 0028-0836, 1476-4687.
+\newblock \doi{10.1038/nature21400}.
+
+\bibitem[Suga et~al.(2020)Suga, Shimada, Akita, Shen, Tosha, and
+  Sugimoto]{sugaTimeresolvedStudiesMetalloproteins2020}
+Michihiro Suga, Atsuhiro Shimada, Fusamichi Akita, Jian-Ren Shen, Takehiko
+  Tosha, and Hiroshi Sugimoto.
+\newblock Time-resolved studies of metalloproteins using {{X-ray}} free
+  electron laser radiation at {{SACLA}}.
+\newblock \emph{Biochimica et Biophysica Acta (BBA) - General Subjects},
+  1864\penalty0 (2):\penalty0 129466, February 2020.
+\newblock ISSN 03044165.
+\newblock \doi{10.1016/j.bbagen.2019.129466}.
+
+\bibitem[Sullivan et~al.(2019)Sullivan, Archibald, Azadmanesh, Vandavasi,
+  Langan, Coates, Lynch, and Langan]{sullivanBraggNetIntegratingBragg2019}
+Brendan Sullivan, Rick Archibald, Jahaun Azadmanesh, Venu~Gopal Vandavasi,
+  Patricia~S. Langan, Leighton Coates, Vickie Lynch, and Paul Langan.
+\newblock {{BraggNet}}: Integrating {{Bragg}} peaks using neural networks.
+\newblock \emph{Journal of Applied Crystallography}, 52\penalty0 (4):\penalty0
+  854--863, August 2019.
+\newblock ISSN 1600-5767.
+\newblock \doi{10.1107/S1600576719008665}.
+
+\bibitem[Tan et~al.(2020)Tan, Pang, and
+  Le]{tanEfficientDetScalableEfficient2020}
+Mingxing Tan, Ruoming Pang, and Quoc~V. Le.
+\newblock {{EfficientDet}}: {{Scalable}} and {{Efficient Object Detection}},
+  July 2020.
+
+\bibitem[Weaver(1985)]{weaverCentrosymmetricCrossSymmetricMatrices1985}
+James~R. Weaver.
+\newblock Centrosymmetric ({{Cross-Symmetric}}) {{Matrices}}, {{Their Basic
+  Properties}}, {{Eigenvalues}}, and {{Eigenvectors}}.
+\newblock \emph{The American Mathematical Monthly}, 92\penalty0 (10):\penalty0
+  711, December 1985.
+\newblock ISSN 00029890.
+\newblock \doi{10.2307/2323222}.
+
+\bibitem[White et~al.(2012)White, Kirian, Martin, Aquila, Nass, Barty, and
+  Chapman]{whiteCrystFELSoftwareSuite2012}
+Thomas~A. White, Richard~A. Kirian, Andrew~V. Martin, Andrew Aquila, Karol
+  Nass, Anton Barty, and Henry~N. Chapman.
+\newblock {{{\emph{CrystFEL}}}} : A software suite for snapshot serial
+  crystallography.
+\newblock \emph{Journal of Applied Crystallography}, 45\penalty0 (2):\penalty0
+  335--341, April 2012.
+\newblock ISSN 0021-8898.
+\newblock \doi{10.1107/S0021889812002312}.
+
+\bibitem[Wilkinson et~al.(1988)Wilkinson, Khamis, Stansfield, and
+  McIntyre]{wilkinsonIntegrationSinglecrystalReflections1988a}
+C.~Wilkinson, H.~W. Khamis, R.~F.~D. Stansfield, and G.~J. McIntyre.
+\newblock Integration of single-crystal reflections using area multidetectors.
+\newblock \emph{Journal of Applied Crystallography}, 21\penalty0 (5):\penalty0
+  471--478, October 1988.
+\newblock ISSN 0021-8898.
+\newblock \doi{10.1107/S0021889888005400}.
+
+\bibitem[Winter et~al.(2018)Winter, Waterman, Parkhurst, Brewster, Gildea,
+  Gerstel, {Fuentes-Montero}, Vollmar, {Michels-Clark}, Young, Sauter, and
+  Evans]{winterDIALSImplementationEvaluation2018}
+Graeme Winter, David~G. Waterman, James~M. Parkhurst, Aaron~S. Brewster,
+  Richard~J. Gildea, Markus Gerstel, Luis {Fuentes-Montero}, Melanie Vollmar,
+  Tara {Michels-Clark}, Iris~D. Young, Nicholas~K. Sauter, and Gwyndaf Evans.
+\newblock {{{\emph{DIALS}}}} : Implementation and evaluation of a new
+  integration package.
+\newblock \emph{Acta Crystallographica Section D Structural Biology},
+  74\penalty0 (2):\penalty0 85--97, February 2018.
+\newblock ISSN 2059-7983.
+\newblock \doi{10.1107/S2059798317017235}.
+
+\bibitem[Yoon(2020)]{yoonPsocakeGUIMaking2020}
+Chun~Hong Yoon.
+\newblock Psocake: {{GUI}} for {{Making Data Analysis}} a {{Piece}} of
+  {{Cake}}.
+\newblock In \emph{Handbook on {{Big Data}} and {{Machine Learning}} in the
+  {{Physical Sciences}}}, pages 169--178. {World Scientific Publishing Co Pte
+  Ltd}, May 2020.
+
+\bibitem[Young et~al.(2016)Young, Ibrahim, Chatterjee, Gul, Fuller, Koroidov,
+  Brewster, Tran, {Alonso-Mori}, Kroll, {Michels-Clark}, Laksmono, Sierra,
+  Stan, Hussein, Zhang, Douthit, Kubin, {de Lichtenberg}, Vo~Pham, Nilsson,
+  Cheah, Shevela, Saracini, Bean, Seuffert, Sokaras, Weng, Pastor, Weninger,
+  Fransson, Lassalle, Br{\"a}uer, Aller, Docker, Andi, Orville, Glownia,
+  Nelson, Sikorski, Zhu, Hunter, Lane, Aquila, Koglin, Robinson, Liang, Boutet,
+  Lyubimov, Uervirojnangkoorn, Moriarty, Liebschner, Afonine, Waterman, Evans,
+  Wernet, Dobbek, Weis, Brunger, Zwart, Adams, Zouni, Messinger, Bergmann,
+  Sauter, Kern, Yachandra, and Yano]{youngStructurePhotosystemII2016}
+Iris~D. Young, Mohamed Ibrahim, Ruchira Chatterjee, Sheraz Gul, Franklin~D.
+  Fuller, Sergey Koroidov, Aaron~S. Brewster, Rosalie Tran, Roberto
+  {Alonso-Mori}, Thomas Kroll, Tara {Michels-Clark}, Hartawan Laksmono,
+  Raymond~G. Sierra, Claudiu~A. Stan, Rana Hussein, Miao Zhang, Lacey Douthit,
+  Markus Kubin, Casper {de Lichtenberg}, Long Vo~Pham, H{\aa}kan Nilsson,
+  Mun~Hon Cheah, Dmitriy Shevela, Claudio Saracini, Mackenzie~A. Bean, Ina
+  Seuffert, Dimosthenis Sokaras, Tsu-Chien Weng, Ernest Pastor, Clemens
+  Weninger, Thomas Fransson, Louise Lassalle, Philipp Br{\"a}uer, Pierre Aller,
+  Peter~T. Docker, Babak Andi, Allen~M. Orville, James~M. Glownia, Silke
+  Nelson, Marcin Sikorski, Diling Zhu, Mark~S. Hunter, Thomas~J. Lane, Andy
+  Aquila, Jason~E. Koglin, Joseph Robinson, Mengning Liang, S{\'e}bastien
+  Boutet, Artem~Y. Lyubimov, Monarin Uervirojnangkoorn, Nigel~W. Moriarty,
+  Dorothee Liebschner, Pavel~V. Afonine, David~G. Waterman, Gwyndaf Evans,
+  Philippe Wernet, Holger Dobbek, William~I. Weis, Axel~T. Brunger, Petrus~H.
+  Zwart, Paul~D. Adams, Athina Zouni, Johannes Messinger, Uwe Bergmann,
+  Nicholas~K. Sauter, Jan Kern, Vittal~K. Yachandra, and Junko Yano.
+\newblock Structure of photosystem {{II}} and substrate binding at room
+  temperature.
+\newblock \emph{Nature}, 540\penalty0 (7633):\penalty0 453--457, December 2016.
+\newblock ISSN 0028-0836, 1476-4687.
+\newblock \doi{10.1038/nature20161}.
+
+\end{thebibliography}
 

### 2023-06-28 package.arxiv.sh
Add packaging scripts.

@@ -1,0 +1,16 @@
+#!/bin/bash
+
+tar czvf                             \
+    ./PeakNet.tar.gz                 \
+    ./bibliography.bib               \
+    ./figures/peaknet_steps.pdf      \
+    ./figures/network_arc.pdf        \
+    ./figures/data_aug.pdf           \
+    ./figures/data_engine.pdf        \
+    ./figures/automask.pdf           \
+    ./figures/automask.agbehnate.pdf \
+    ./manuscript.tex                 \
+    ./style.sty                      \
+    ./more.sty                       \
+    ./constants.sty                  \
+    ./manuscript.bbl

### 2023-06-28 package.natcomm.sh

@@ -1,0 +1,12 @@
+#!/bin/bash
+
+tar czvf                             \
+    ./PeakNet.natcomm.tar.gz         \
+    ./figures/peaknet_steps.pdf      \
+    ./figures/network_arc.pdf        \
+    ./figures/data_aug.pdf           \
+    ./figures/data_engine.pdf        \
+    ./figures/automask.pdf           \
+    ./figures/automask.agbehnate.pdf \
+    ./manuscript.natcomm.tex         \
+    ./manuscript.natcomm.pdf

### 2023-06-29 manuscript.natcomm.tex
Add acknowledgement to ChatGPT and use numerics for citaitons.
Fixed minor formatting issues.

@@
 \usepackage{natbib}
+\setcitestyle{numbers,square}
 %% \setcitestyle{authoryear,round}    % Use authoryear format
@@
 Use of the Linac Coherent Light Source (LCLS), SLAC National Accelerator Laboratory, is supported by the U.S.
-Department of Energy, Office of Science, Office of Basic Energy Sciences under Contract No.
-DE-AC02-76SF00515.
+Department of Energy, Office of Science, Office of Basic Energy Sciences under Contract No.DE-AC02-76SF00515.
+C.W acknowledges the assistance provided by ChatGPT from OpenAI in refining the language and enhancing the readability of this paper.
 

### 2023-06-30 manuscript.tex
Merged changes from Chuck.

@@
 The development of this system 1) eliminates the need for manual algorithm parameter tuning, 2) reduces false-positive peaks by adjusting to shot-to-shot variations in strong background scattering in real-time, 3) eliminates the laborious task of manually creating bad pixel masks and the need to store these masks per event since these can be regenerated on demand.
-\peaknet{} also exhibits exceptional runtime efficiency, processing a $1920 \times 1920$ pixel image around 90 ms on an NVIDIA 1080 Ti GPU, with the potential for further enhancements through parallelized analysis or GPU stream processing.
+\peaknet{} also exhibits exceptional runtime efficiency, processing a $1920 \times 1920$ pixel image around 90 milliseconds for peak finding and mask generation on an NVIDIA 1080 Ti GPU, with the potential for further enhancements through parallelized analysis or GPU stream processing.
 \peaknet{} is well-suited for expert-level real-time serial crystallography data analysis at high data rates.
@@
 
-When processing Rayonix images with $1920 \times 1920$ pixels, \peaknet{} achieved a significantly reduced processing time of 90 milliseconds per event on an NVIDIA 1080 Ti GPU.
-In contrast, \psocake{} required 176 milliseconds per event when executed on an Intel E5-2620 CPU.
-Another peak finding method, RPF (robust peak finder), operating on Intel E5-2698, is reported to require 120 milliseconds but on a smaller AGIPD 1M images \citep{hadian-jaziDataReductionSerial2021}.
+When processing Rayonix images with $1920 \times 1920$ pixels, \peaknet{} achieved a significantly reduced processing time of 90 milliseconds per event on an NVIDIA 1080 Ti GPU for peak finding and auto-mask generation.
+In contrast, \psocake{} required 176 milliseconds per event when executed on an Intel E5-2620 CPU and more than 350 milliseconds for Cheetah \citep{hadian-jaziPeakfindingAlgorithmBased2017} and 120 milliseconds for Robust Peak Finder (RBF) on 3 times smaller AGIPD 1M images \citep{hadian-jaziDataReductionSerial2021}.
+Note that computation time will be even longer if auto-masking feature is introduced to these existing peak finders.
 This result clearly demonstrates that \peaknet{} not only delivers robust Bragg peak finding results in an autonomous fashion, but also exhibits remarkable runtime efficiency.
@@
     \citep{hadian-jaziPeakfindingAlgorithmBased2017,
-    hadian-jaziDataReductionSerial2021} and two classification methods for X-ray
-    diffraction data reduction. RPF runtime performance was originally measured
+    hadian-jaziDataReductionSerial2021} and Peakfinder8 . RPF runtime performance was originally measured
     on AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019}.  
@@
 \resizebox{!}{!}{
-\begin{tabular}{llcc}
+\begin{tabular}{lllcc}
 \hline
-Methods             & Hardware       & Image size         & Time (ms/event) \\ \hline
-\peaknet{}          & NVIDIA 1080 Ti & 1920 $\times$ 1920 & 90.0            \\ \hline
-\psocake{}          & Intel E5-2620  & 1920 $\times$ 1920 & 175.5           \\ \hline
-RPF                 & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
+Methods         &  Auto-mask   & Hardware       & Image dimension    & Time (ms/event) \\ \hline
+\peaknet{}      &  Yes         & NVIDIA 1080 Ti & 1920 $\times$ 1920 & 90.0            \\ \hline
+\psocake{}      &  No          & Intel E5-2620  & 1920 $\times$ 1920 & 175.5           \\ \hline
+RPF             &  No          & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
+Peakfinder8     &  No          & Intel E5-2698  & 1024 $\times$ 1024 & $\approx$ RPF        \\ \hline
 %CNN hit finder      & Hit Finding  & NVIDIA 1080 Ti & 720 $\times$ 720   & 0.8             \\ \hline

### 2023-06-30 manuscript.tex
Incorporate Cheetah in the discussion.

@@
 When processing Rayonix images with $1920 \times 1920$ pixels, \peaknet{} achieved a significantly reduced processing time of 90 milliseconds per event on an NVIDIA 1080 Ti GPU for peak finding and auto-mask generation.
-In contrast, \psocake{} required 176 milliseconds per event when executed on an Intel E5-2620 CPU and more than 350 milliseconds for Cheetah \citep{hadian-jaziPeakfindingAlgorithmBased2017} and 120 milliseconds for Robust Peak Finder (RBF) on 3 times smaller AGIPD 1M images \citep{hadian-jaziDataReductionSerial2021}.
-Note that computation time will be even longer if auto-masking feature is introduced to these existing peak finders.
-This result clearly demonstrates that \peaknet{} not only delivers robust Bragg peak finding results in an autonomous fashion, but also exhibits remarkable runtime efficiency.
-%This establishes it as a highly competent tool for real-time autonomous Bragg peak finding.
+In contrast, \psocake{} required 176 milliseconds per event when executed on an Intel E5-2620 CPU.
+To provide a reference, an earlier study \citep{hadian-jaziDataReductionSerial2021} also reported the runtime efficiency of both the Robust Peak Finder (RBF) and Cheetah, demonstrating an average processing time of around 120 milliseconds for 3 times smaller AGPID 1M images.
+It should be noted that computation time would be even longer if the auto-masking feature is introduced to these existing peak finders.
+This result clearly demonstrates that \peaknet{} not only delivers robust Bragg peak finding results autonomously but also exhibits remarkable runtime efficiency.
 
@@
 \caption{
-    The runtime performance of diffraction image analysis algorithms measured on
-    Rayonix images containing 3.7 megapixels.  We measured runtime performance
-    of \psocake{} and \peaknet{} directly using Rayonix images.  For reference
-    purposes, we also included another peak finding method RPF
-    \citep{hadian-jaziPeakfindingAlgorithmBased2017,
-    hadian-jaziDataReductionSerial2021} and Peakfinder8 . RPF runtime performance was originally measured
-    on AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019}.  
+    The runtime performance of diffraction image analysis algorithms measured on Rayonix images containing 3.7 megapixels.
+We measured runtime performance of \psocake{} and \peaknet{} directly using Rayonix images.
+For reference purposes, we also included peak finding method RPF \citep{hadian-jaziPeakfindingAlgorithmBased2017, hadian-jaziDataReductionSerial2021} and Cheetah \citep{bartyCheetahSoftwareHighthroughput2014}, whose runtime performance were originally measured on AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019}.
 }
@@
 RPF             &  No          & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
-Peakfinder8     &  No          & Intel E5-2698  & 1024 $\times$ 1024 & $\approx$ RPF        \\ \hline
+Cheetah         &  No          & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
 %CNN hit finder      & Hit Finding  & NVIDIA 1080 Ti & 720 $\times$ 720   & 0.8             \\ \hline

### 2023-06-30 manuscript.tex
Merged new changes from overleaf.

@@
 We measured runtime performance of \psocake{} and \peaknet{} directly using Rayonix images.
-For reference purposes, we also included peak finding method RPF \citep{hadian-jaziPeakfindingAlgorithmBased2017, hadian-jaziDataReductionSerial2021} and Cheetah \citep{bartyCheetahSoftwareHighthroughput2014}, whose runtime performance were originally measured on AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019}.
+For reference purposes, we also included peak finding methods RPF and Cheetah, whose runtime performance were originally measured on AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019}.
 }

### 2023-06-30 manuscript.natcomm.tex
Handling repeated referencing.

@@
 
-When processing Rayonix images with $1920 \times 1920$ pixels, \peaknet{} achieved a significantly reduced processing time of 90 milliseconds per event on an NVIDIA 1080 Ti GPU.
+When processing Rayonix images with $1920 \times 1920$ pixels, \peaknet{} achieved a significantly reduced processing time of 90 milliseconds per event on an NVIDIA 1080 Ti GPU for peak finding and auto-mask generation.
 In contrast, \psocake{} required 176 milliseconds per event when executed on an Intel E5-2620 CPU.
-Another peak finding method, RPF (robust peak finder), operating on Intel E5-2698, is reported to require 120 milliseconds but on a smaller AGIPD 1M images \citep{hadian-jaziDataReductionSerial2021}.
-This result clearly demonstrates that \peaknet{} not only delivers robust Bragg peak finding results in an autonomous fashion, but also exhibits remarkable runtime efficiency.
-%This establishes it as a highly competent tool for real-time autonomous Bragg peak finding.
+To provide a reference, an earlier study \citep{hadian-jaziDataReductionSerial2021} also reported the runtime efficiency of both the Robust Peak Finder (RBF) and Cheetah, demonstrating an average processing time of around 120 milliseconds for 3 times smaller AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019} images.
+It should be noted that computation time would be even longer if the auto-masking feature is introduced to these existing peak finders.
+This result clearly demonstrates that \peaknet{} not only delivers robust Bragg peak finding results autonomously but also exhibits remarkable runtime efficiency.
 
@@
 \caption{
-    The runtime performance of diffraction image analysis algorithms measured on
-    Rayonix images containing 3.7 megapixels.  We measured runtime performance
-    of \psocake{} and \peaknet{} directly using Rayonix images.  For reference
-    purposes, we also included another peak finding method RPF
-    \citep{hadian-jaziPeakfindingAlgorithmBased2017,
-    hadian-jaziDataReductionSerial2021} and two classification methods for X-ray
-    diffraction data reduction. RPF runtime performance was originally measured
-    on AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019}.  
+    The runtime performance of diffraction image analysis algorithms measured on Rayonix images containing 3.7 megapixels.
+We measured runtime performance of \psocake{} and \peaknet{} directly using Rayonix images.
+For reference purposes, we also included peak finding methods RPF and Cheetah, whose runtime performance were originally measured on AGIPD 1M.
 }
@@
 \resizebox{!}{!}{
-\begin{tabular}{llcc}
+\begin{tabular}{lllcc}
 \hline
-Methods             & Hardware       & Image size         & Time (ms/event) \\ \hline
-\peaknet{}          & NVIDIA 1080 Ti & 1920 $\times$ 1920 & 90.0            \\ \hline
-\psocake{}          & Intel E5-2620  & 1920 $\times$ 1920 & 175.5           \\ \hline
-RPF                 & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
+Methods         &  Auto-mask   & Hardware       & Image dimension    & Time (ms/event) \\ \hline
+\peaknet{}      &  Yes         & NVIDIA 1080 Ti & 1920 $\times$ 1920 & 90.0            \\ \hline
+\psocake{}      &  No          & Intel E5-2620  & 1920 $\times$ 1920 & 175.5           \\ \hline
+RPF             &  No          & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
+Cheetah         &  No          & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
 %CNN hit finder      & Hit Finding  & NVIDIA 1080 Ti & 720 $\times$ 720   & 0.8             \\ \hline

### 2023-06-30 manuscript.tex
Handling repeated referencing.

@@
 In contrast, \psocake{} required 176 milliseconds per event when executed on an Intel E5-2620 CPU.
-To provide a reference, an earlier study \citep{hadian-jaziDataReductionSerial2021} also reported the runtime efficiency of both the Robust Peak Finder (RBF) and Cheetah, demonstrating an average processing time of around 120 milliseconds for 3 times smaller AGPID 1M images.
+To provide a reference, an earlier study \citep{hadian-jaziDataReductionSerial2021} also reported the runtime efficiency of both the Robust Peak Finder (RBF) and Cheetah, demonstrating an average processing time of around 120 milliseconds for 3 times smaller AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019} images.
 It should be noted that computation time would be even longer if the auto-masking feature is introduced to these existing peak finders.
@@
 We measured runtime performance of \psocake{} and \peaknet{} directly using Rayonix images.
-For reference purposes, we also included peak finding methods RPF and Cheetah, whose runtime performance were originally measured on AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019}.
+For reference purposes, we also included peak finding methods RPF and Cheetah, whose runtime performance were originally measured on AGIPD 1M.
 }

### 2023-07-01 manuscript.natcomm.tex
Improved bibliography.

@@
   and Serge Belongie.
-\newblock Feature {{Pyramid Networks}} for {{Object Detection}}, April 2017.
+\newblock Feature {{Pyramid Networks}} for {{Object Detection}}.
+\newblock \emph{arXiv:1612.03144 [cs.CV]}, April 2017.
+\newblock \doi{10.48550/arXiv.1612.03144}.
 
@@
 Tsung-Yi Lin, Priya Goyal, Ross Girshick, Kaiming He, and Piotr Doll{\'a}r.
-\newblock Focal {{Loss}} for {{Dense Object Detection}}, February 2018.
+\newblock Focal {{Loss}} for {{Dense Object Detection}}.
+\newblock \emph{arXiv:1708.02002 [cs.CV]}, February 2018.
+\newblock \doi{10.48550/arXiv.1708.02002}.
 
@@
 \newblock \emph{arXiv:2008.08198 [cs, eess]}, June 2021.
+\newblock \doi{10.48550/arXiv.2008.08198}.
 
@@
 \newblock Attention {{U-Net}}: {{Learning Where}} to {{Look}} for the
-  {{Pancreas}}, May 2018.
+  {{Pancreas}}.
+\newblock \emph{arXiv:1804.03999 [cs.CV]}, May 2018.
+\newblock \doi{10.48550/arXiv.1804.03999}.
 
@@
 \newblock \emph{arXiv:1505.04597 [cs]}, May 2015.
+\newblock \doi{10.48550/arXiv.1505.04597}.
 
@@
 Mingxing Tan, Ruoming Pang, and Quoc~V. Le.
-\newblock {{EfficientDet}}: {{Scalable}} and {{Efficient Object Detection}},
-  July 2020.
+\newblock {{EfficientDet}}: {{Scalable}} and {{Efficient Object Detection}}.
+\newblock \emph{arXiv:1911.09070 [cs.CV]}, July 2020.
+\newblock \doi{10.48550/arXiv.1911.09070}.
 
